### 2018-01-24 Manuscript_figures_2017_12_12.Rmd
Add files via upload

---
title: "Landscape heterogeneity simulation figures"
author: "Lauren White"
date: "December 12, 2017"
output: html_document
---

## Load packages
```{r}
library(doBy)
library(ggplot2)
library(viridis)
library(ggthemes)
library(scales)
library(lsr)
library(SDMTools)
```

## Load and update summary dataset

```{r}
setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
merged_data<-read.csv("IBMsummary.csv")
merged_data<-merged_data[-which(merged_data$beta2==5),] #remove saturating beta_2 values

#Create character strings for landscape structure (Hurst exponent and proportion available habitat)
merged_data$Hurst<-NA
merged_data$proportion<-NA
merged_data$Hurst[which(merged_data$H==0.1)]<-"HP"
merged_data$Hurst[which(merged_data$H==0.5)]<-"MP"
merged_data$Hurst[which(merged_data$H==0.9)]<-"LP"

merged_data$proportion[which(merged_data$p==0.25)]<-"L"
merged_data$proportion[which(merged_data$p==0.5)]<-"M"
merged_data$proportion[which(merged_data$p==0.75)]<-"H"
merged_data$lstructure<-paste(merged_data$proportion, merged_data$Hurst, sep="/")

#Order factors
merged_data$betas<- factor(merged_data$betas, levels = c("0 0 0", "0 0 -1", "0 1 -1", "0 1 -0.5", "0 2 -1", "0 2 -0.5", "3 0 0", "3 0 -1", "3 1 -1", "3 1 -0.5", "3 2 -1", "3 2 -0.5", "6 0 0", "6 0 -1", "6 1 -1", "6 1 -0.5", "6 2 -1", "6 2 -0.5"))
merged_data$lstructure<- factor(merged_data$lstructure, levels = c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))

#Set working directory of where to produce Figures
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
```

## Define multiplot function
```{r}
#' Multiplot function
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                     ncol = cols, nrow = ceiling(numPlots/cols), byrow=TRUE)
  }

  if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

```

##Figure 1
Representation of neutral landscapes
```{r}
#' Create neutral landscape maps
library(raster)

#' Use standard methods to generate fractal maps. Binary and continuous surfaces may be produced.
#' 
#' @param k integer. The extent of the map (2^k+1)^2 pixels
#' @param h numeric. Level of aggregation in the map.
#' @param p numeric (0,1). The proportion of map in habitat=1
#' @param binary logical. If TRUE, a 0/1 categorical landscape is produced.
#' @author Shannon Pittman, James Forester, modified by Lauren White
#' @export
#' @example examples/neutral.landscape_example.R
fracland_mod <- function(k, h, p, binary = TRUE) {
  ## Function for creating neutral landscapes Shannon Pittman University of Minnesota May, 2013 k = the extent of the map (2^k+1)^2 pixels h =
  ## how clumped the map should be (ranging from ?? to ??) -- weird behavior at higher values p = proportion of map in habitat 1 binary =
  ## plotflag == if TRUE will plot a filled contour version of the matrix

  ## function call: testmap=land(6,1,.5,FALSE,TRUE)
  A <- 2^k + 1  # Scalar-determines length of landscape matrix

  #Right now, as written (1-p) represents the amount of habitat listed as "1"
  B <- matrix(0, A, A)  # Creates landscape matrix

  B[1, 1] <- 0
  B[1, A] <- 0
  B[A, 1] <- 0
  B[A, A] <- 0

  iter <- 1
  for (iter in 1:k) {
    scalef <- (0.5 + (1 - h)/2)^(iter)

    d <- 2^(k - iter)

    # ALL SQUARE STEPS#
    for (i in seq(d + 1, A - d, 2 * d)) {
      for (j in seq(d + 1, A - d, 2 * d)) {
        B[i, j] <- mean(c(B[i - d, j - d], B[i - d, j + d], B[i + d, j - d], B[i + d, j + d])) + scalef * rnorm(n = 1)
      }
    }

    # OUTSIDE DIAMOND STEP#
    for (j in seq(d + 1, A - d, 2 * d)) {
      B[1, j] <- mean(c(B[1, j - d], B[1, j + d], B[1 + d, j])) + scalef * rnorm(n = 1)
      B[A, j] <- mean(c(B[A, j - d], B[A, j + d], B[A - d, j])) + scalef * rnorm(n = 1)
    }

    for (i in seq(d + 1, A - d, 2 * d)) {
      B[i, 1] <- mean(c(B[i - d, 1], B[i + d, 1], B[i, 1 + d])) + scalef * rnorm(n = 1)
      B[i, A] <- mean(c(B[i - d, A], B[i + d, A], B[i, A - d])) + scalef * rnorm(n = 1)
    }

    # INSIDE DIAMOND STEP#
    if (2 * d + 1 <= A - 2 * d) {
      for (i in seq(d + 1, A - d, 2 * d)) {
        for (j in seq(2 * d + 1, A - 2 * d, 2 * d)) {
          B[i, j] <- mean(c(B[i - d, j], B[i + d, j], B[i, j - d], B[i, j + d])) + scalef * rnorm(n = 1)
        }
      }

      for (i in seq(2 * d + 1, A - 2 * d, 2 * d)) {
        for (j in seq(d + 1, A - d, 2 * d)) {
          B[i, j] <- mean(c(B[i - d, j], B[i + d, j], B[i, j - d], B[i, j + d])) + scalef * rnorm(n = 1)
        }
      }
    }

    iter <- iter + 1
  }

  if (binary == T) {
    R <- sort(B)
    PosR <- (1 - p) * length(R)  #larger values become habitat, designated as 1
    pval <- R[PosR]
    T1 <- which(B > pval)
    T2 <- which(B <= pval)
    B[T1] <- 1  #habitat is 1
    B[T2] <- 0
  } 
  return(B)
}

landscape<-fracland_mod(k=7, h=0.1, p=0.25)
map.1 <- raster(landscape)
one<-spplot(map.1)
landscape<-fracland_mod(k=7, h=0.1, p=0.5) 
map.2 <- raster(landscape)
two<-spplot(map.2)
landscape<-fracland_mod(k=7, h=0.1, p=0.75)
map.3 <- raster(landscape)
three<-spplot(map.3)

landscape<-fracland_mod(k=7, h=0.5, p=0.25) 
map.4 <- raster(landscape)
four<-spplot(map.4)
landscape<-fracland_mod(k=7, h=0.5, p=0.5) 
map.5 <- raster(landscape)
five<-spplot(map.5)
landscape<-fracland_mod(k=7, h=0.5, p=0.75)
map.6 <- raster(landscape)
six<-spplot(map.6)

landscape<-fracland_mod(k=7, h=0.9, p=0.25)
map.7 <- raster(landscape)
seven<-spplot(map.7)
landscape<-fracland_mod(k=7, h=0.9, p=0.5)
map.8 <- raster(landscape)
eight<-spplot(map.8)
landscape<-fracland_mod(k=7, h=0.9, p=0.75)
map.9 <- raster(landscape)
# nine<-spplot(map.9)

#convert the raster to points for plotting
H<-rep(0.1, times=length(map.1))
map.1 <- rasterToPoints(map.1)
p<-rep(0.25, times=length(map.1))
df <- data.frame(map.1, H, p)

map.2 <- rasterToPoints(map.2)
p<-rep(0.5, times=length(map.1))
df2 <- data.frame(map.2, H, p)

map.3 <- rasterToPoints(map.3)
p<-rep(0.75, times=length(map.1))
df3 <- data.frame(map.3, H, p)

H<-rep(0.5, times=length(map.1))
map.4 <- rasterToPoints(map.4)
p<-rep(0.25, times=length(map.1))
df4 <- data.frame(map.4, H, p)

map.5 <- rasterToPoints(map.5)
p<-rep(0.5, times=length(map.1))
df5 <- data.frame(map.5, H, p)

map.6 <- rasterToPoints(map.6)
p<-rep(0.75, times=length(map.1))
df6 <- data.frame(map.6, H, p)

H<-rep(0.9, times=length(map.1))
map.7 <- rasterToPoints(map.7)
p<-rep(0.25, times=length(map.1))
df7 <- data.frame(map.7, H, p)

map.8 <- rasterToPoints(map.8)
p<-rep(0.5, times=length(map.1))
df8 <- data.frame(map.8, H, p)

map.9 <- rasterToPoints(map.9)
p<-rep(0.75, times=length(map.1))
df9 <- data.frame(map.9, H, p)

#Make the points a dataframe for ggplot

df <- rbind(df, df2)
df <- rbind(df, df3)
df <- rbind(df, df4)
df <- rbind(df, df5)
df <- rbind(df, df6)
df <- rbind(df, df7)
df <- rbind(df, df8)
df <- rbind(df, df9)

my_x_title <- expression(paste("Hurst exponent- habitat patchiness (", italic("H"), ")"))
my_y_title <- expression(paste("Proportion of available habitat (", italic("p"), ")"))

#Now make the map
tiff("Figure1_p_vs_H.tif", height = 8, width = 8, units = "in", compression = "lzw", res = 300)
ggplot(data=df, aes(y=y, x=x)) +
  geom_raster(aes(fill=layer)) +
    theme_bw() +
  coord_equal() +
  facet_grid(p~ H) +
  #scale_fill_viridis(name="Resource quality")+
  #scale_fill_continuous(colours=c("#0000FFFF","#FFFFFFFF"))+
  scale_fill_gradient(low="lightgrey", high="darkgreen", guide=FALSE) +
  #scale_fill_continuous(guide = FALSE) +
  labs(y=my_y_title, x=my_x_title)+
  theme(axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  theme(axis.title = element_text(face="bold", size=28)) +
  theme(strip.text = element_text(vjust=0.5, size=24))+ 
  theme(legend.text = element_text(vjust=0.5, size=24), legend.title=element_text(vjust=0.5, size=28))
dev.off()

```

##Figure 2
Random forest variable importance results
```{r}
library(randomForest)
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")

#Load importance values (not scaled by SD)
imp_logit<-read.csv("imp_logit.csv")
imp_logitprev<-read.csv("logit_imp_maxprev.csv")
imp_logitdur<-read.csv("logit_imp_dur.csv")

logitSD<-read.csv("imp_logitSD.csv")
logitprevSD<-read.csv("imp_logitprevSD.csv")
logitdurSD<-read.csv("imp_logitdurSD.csv")

imp_logit$SD<-logitSD$x
imp_logitprev$SD<-logitprevSD$x
imp_logitdur$SD<-logitdurSD$x

#Order according to increasing node purity
imp_logit<-imp_logit[order(imp_logit$IncNodePurity),]
imp_logitdur<-imp_logitdur[order(imp_logitdur$IncNodePurity),] 
imp_logitprev<-imp_logitprev[order(imp_logitprev$IncNodePurity),]

#Remove infection probability (dummy variable--not varied in factorial design)
imp_logit<- imp_logit[!(imp_logit$X=="inf_prob"),]
imp_logitdur<- imp_logitdur[!(imp_logitdur$X=="inf_prob"),]
imp_logitprev<- imp_logitprev[!(imp_logitprev$X=="inf_prob"),]

#In ggplot
imp_logit<-imp_logit[order(imp_logit$X.IncMSE),] #order according to %increase in MSE

#imp_logit$SD<-rep(0.005, times=nrow(imp_logit))
A<-ggplot(imp_logit, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "range")) +
     #ylab("Mean Decrease in Accuracy (%IncMSE)") +
    ylab(NULL)+
    ggtitle("(A)") + #" Variable Importance for Epidemic \nSuccess") +
    theme(axis.title = element_text(size=10),title=element_text(face="bold", size=10))+
    coord_flip()+
    theme_bw()
A

#imp_logitprev$SD<-rep(0.0000001, times=nrow(imp_logitprev))
B<-ggplot(imp_logitprev, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "range")) +
     #ylab("Mean Decrease in Accuracy (%IncMSE)") +
    ylab(NULL)+
    theme(axis.title = element_text(size=10),title=element_text(face="bold", size=10))+
    ggtitle("(B)") + #" Variable Importance for Maximum \nPrevalence|Success") +
    coord_flip()+
    theme_bw()
B

#imp_logitdur$SD<-rep(100, times=nrow(imp_logitdur))
C<-ggplot(imp_logitdur, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
    #               size=.3,    # Thinner lines
    #               width=.2,
    #               position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "range")) +
    ylab("Mean Decrease in Accuracy (%IncMSE)") +
    ggtitle("(C)") + #" Variable Importance for Epidemic \nDuration|Success") +
    theme(axis.title = element_text(size=10),title=element_text(face="bold", size=10))+
    coord_flip()+
    theme_bw()
C

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
tiff("Fig2_RF.tif", height =16 , width =8.7, units = "cm", compression = "lzw", res = 300)
multiplot(A, B, C, cols=1)
dev.off()

```

##Figure 3
Box plots rec rate vs. density
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks

#tiff("boxplot_prev.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
gg<- ggplot(data=sub_data, aes(y=max_prevalence, x=as.factor(rec_rate)))
#gg<- gg+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
gg<-gg+ geom_boxplot()+ facet_grid(percep ~ density, scales= "free_x", labeller=label_both)
gg<- gg+ labs(x = expression(Recovery~rate~(gamma)), y = "Maximum prevalence",title="(A)")
gg<- gg+ theme(axis.title = element_text(size=16),title=element_text(face="bold", size=16))
gg<- gg + theme(axis.text.x = element_text(vjust=0.5, size=16))
gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
gg<- gg + theme(strip.text = element_text(vjust=0.5, size=14)) 
gg
#dev.off()

#tiff("boxplot_dur.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
hh<- ggplot(data=sub_data, aes(x=as.factor(rec_rate), y=duration))
#hh<- hh+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
hh<-hh+ geom_boxplot()+ facet_grid(percep ~ density, scales= "free_x", labeller=label_both)
hh<- hh+ labs(fill= "density", x = expression(Recovery~rate~(gamma)), y = "Duration", title="(B)")
hh<- hh+ theme(axis.title = element_text(face="bold", size=16), title=element_text(face="bold", size=16))
hh<- hh + theme(axis.text.x = element_text(vjust=0.5, size=16))
hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
hh<- hh + theme(strip.text = element_text(vjust=0.5, size=14)) 
hh
#dev.off()

tiff("Figure3.tif", height = 14, width = 8.7, units = "in", compression = "lzw", res = 300)
multiplot(gg,hh, cols=1)
dev.off()

```

##Figure 4
```{r}
#percep=3, rec_rate=0.2, density=0.5
p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=max_prevalence, fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii

jj<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=duration, fill=as.factor(beta2)))
jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(B)", fill= expression(beta[2]))
jj<- jj+ theme(axis.title = element_text(face="bold", size=20))
jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
jj<- jj + theme(strip.text = element_text(vjust=0.5, size=16)) 
jj<- jj + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
jj

tiff("Fig4.tif", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(ii,jj, cols=1)
dev.off()
```

##Figure 4 (log version)
```{r}
#percep=3, rec_rate=0.2, density=0.5
p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(max_prevalence), fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Maximum prevalence)", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii

jj<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(duration), fill=as.factor(beta2)))
jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Duration)", title="(B)", fill= expression(beta[2]))
jj<- jj+ theme(axis.title = element_text(face="bold", size=20))
jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
jj<- jj + theme(strip.text = element_text(vjust=0.5, size=16)) 
jj<- jj + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
jj

tiff("Fig4_log.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(ii,jj, cols=1)
dev.off()
```

##Figure 5
```{r}
#percep=3, rec_rate=0.1, density=0.5
p3r0.1d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.1 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=max_prevalence,fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii

jj<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=duration, fill=as.factor(beta2)))
jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(B)", fill= expression(beta[2]))
jj<- jj+ theme(axis.title = element_text(face="bold", size=20))
jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
jj<- jj + theme(strip.text = element_text(vjust=0.5, size=16)) 
jj<- jj + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
jj

tiff("Fig5.tif", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(ii,jj, cols=1)
dev.off()
```

##Figure 5 (log version)
```{r}
#percep=3, rec_rate=0.1, density=0.5
p3r0.1d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.1 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=log(max_prevalence),fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Maximum prevalence)", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii

jj<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=log(duration), fill=as.factor(beta2)))
jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Duration)", title="(B)", fill= expression(beta[2]))
jj<- jj+ theme(axis.title = element_text(face="bold", size=20))
jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
jj<- jj + theme(strip.text = element_text(vjust=0.5, size=16)) 
jj<- jj + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
jj

tiff("Fig5_log.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(ii,jj, cols=1)
dev.off()
```

##Figure 6
Comparing effects on landscape structure for a single RSF(\beta_1=6, \beta_2=2, \beta_3=-0.5) for different densities, perceptual distances, and recovery rates.
```{r}
sub_data<-merged_data[which(merged_data$max_I>1),]

RSF620.5<-sub_data[which(sub_data$betas=="6 2 -0.5"),]
RSF620.5_rec0.1<-RSF620.5[which(RSF620.5$rec_rate==0.1),]
RSF620.5_rec0.2<-RSF620.5[which(RSF620.5$rec_rate==0.2),]
RSF620.5_rec0.4<-RSF620.5[which(RSF620.5$rec_rate==0.4),]

#Individual plots of RSF box plot max prevalence and duration
gg<- ggplot(data=RSF620.5_rec0.2, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
gg<- gg+ geom_boxplot(stat="boxplot", position=position_dodge())
gg<- gg + facet_grid(percep ~ density)
# gg<-gg +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
gg<- gg+ labs(title="(A)", x = "Landscape structure", y = "Mean maximum \n prevalence")
#gg<-gg +theme_grey()
#gg<-gg + theme(plot.title = element_text(hjust = 0.5))
gg<- gg+ theme(axis.title = element_text(face="bold", size=19))
gg<- gg + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=16))
gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
gg<- gg + theme(strip.text = element_text(vjust=0.5, size=16)) 
#gg <- gg+ theme(legend.position="none")
#gg<-gg+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
#gg<-gg+ theme(axis.ticks.x=element_blank())
#gg<-gg +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
gg

hh<- ggplot(data=RSF620.5_rec0.2, aes(x=lstructure, y=duration)) #, fill=covariation)
hh<- hh+ geom_boxplot(stat="boxplot", position=position_dodge())
hh<- hh + facet_grid(percep ~ density)
# hh<-hh +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
hh<- hh+ labs(title="(B)", x = "Landscape structure", y = "Duration")
#hh<-hh +theme_grey()
#hh<-hh + theme(plot.title = element_text(hjust = 0.5))
hh<- hh+ theme(axis.title = element_text(face="bold", size=19))
hh<- hh + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=16))
hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
hh<- hh + theme(strip.text = element_text(vjust=0.5, size=16)) 
#hh <- hh+ theme(legend.position="none")
#hh<-hh+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
#hh<-hh+ theme(axis.ticks.x=element_blank())
#hh<-hh +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
hh

#Individual plots of RSF box plot max prevalence and duration
ii<- ggplot(data=RSF620.5_rec0.1, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
ii<- ii+ geom_boxplot(stat="boxplot", position=position_dodge())
ii<- ii + facet_grid(percep ~ density)
# ii<-ii +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
ii<- ii+ labs(title="(C)", x = "Landscape structure", y = "Mean maximum \n prevalence")
#ii<-ii +theme_grey()
#ii<-ii + theme(plot.title = element_text(hjust = 0.5))
ii<- ii+ theme(axis.title = element_text(face="bold", size=19))
ii<- ii + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
#ii <- ii+ theme(legend.position="none")
#ii<-ii+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
#ii<-ii+ theme(axis.ticks.x=element_blank())
#ii<-ii +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
ii

jj<- ggplot(data=RSF620.5_rec0.1, aes(x=lstructure, y=duration)) #, fill=covariation)
jj<- jj+ geom_boxplot(stat="boxplot", position=position_dodge())
jj<- jj + facet_grid(percep ~ density)
# jj<-jj +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
jj<- jj+ labs(title="(D)", x = "Landscape structure", y = "Duration")
#jj<-jj +theme_grey()
#jj<-jj + theme(plot.title = element_text(hjust = 0.5))
jj<- jj+ theme(axis.title = element_text(face="bold", size=19))
jj<- jj + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=16))
jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
jj<- jj + theme(strip.text = element_text(vjust=0.5, size=16)) 
#jj <- jj+ theme(legend.position="none")
#jj<-jj+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
#jj<-jj+ theme(axis.ticks.x=element_blank())
#jj<-jj +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
jj

tiff("Figure6.tif", height = 12, width = 12, units = "in", compression = "lzw", res = 300)
multiplot(gg,hh,ii,jj, cols=2)
dev.off()

```

##Supplementary Figure 7
Box plot of percep vs. rec rate vs. density
```{r}
sub_data<-merged_data[which(merged_data$max_I>1),]

#tiff("boxplot_prev.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
gg<- ggplot(data=merged_data, aes(x=betas, y=max_prevalence, fill=as.factor(density)))
#gg<- gg+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
gg<-gg+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
gg<- gg+ labs(fill= "density", x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence",title="(A)")
gg<- gg+ theme(axis.title = element_text(face="bold", size=20))
gg<- gg + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
gg<- gg + theme(strip.text = element_text(vjust=0.5, size=14)) 
gg<- gg + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
gg
#dev.off()

#tiff("boxplot_dur.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
hh<- ggplot(data=merged_data, aes(x=betas, y=duration, fill=as.factor(density)))
#hh<- hh+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
hh<-hh+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
hh<- hh+ labs(fill= "density", x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(B)")
hh<- hh+ theme(axis.title = element_text(face="bold", size=20))
hh<- hh + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
hh<- hh + theme(strip.text = element_text(vjust=0.5, size=14)) 
hh<- hh + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
hh
#dev.off()

tiff("FigureS7.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(gg,hh, cols=1)
dev.off()

```

##Supplementary Figure 8 (Heat map)
Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing rec rates 0.1 and 0.2
```{r}
r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.5),]

sdf <- summaryBy(duration~ H + betas +p+ percep, data=r2, FUN=mean)
gg <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
gg <- gg + geom_tile(color="white", size=0.1)
gg <- gg + scale_fill_viridis(name="Duration")
gg <- gg + coord_equal()
gg <- gg + facet_grid(percep ~ betas)
gg<- gg+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title= "(B)")
gg<- gg+ theme(axis.title = element_text(face="bold", size=24))
gg<- gg + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
gg<- gg + theme(strip.text = element_text(vjust=0.5, size=18)) 
gg<- gg + theme(strip.text.x = element_text(angle = 90))
gg<- gg + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
gg

sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r2, FUN=mean)
hh <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
hh <- hh + geom_tile(color="white", size=0.1)
hh <- hh + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
hh <- hh + coord_equal()
hh <- hh + facet_grid(percep ~ betas)
hh<- hh+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(A)")
hh<- hh+ theme(axis.title = element_text(face="bold", size=24))
hh<- hh + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
hh<- hh + theme(strip.text = element_text(vjust=0.5, size=18)) 
hh<- hh + theme(strip.text.x = element_text(angle = 90))
hh<- hh + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
hh

r1<-merged_data[which(merged_data$rec_rate==0.1 & merged_data$density==0.5),]
sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r1, FUN=mean)
ii <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
ii <- ii + geom_tile(color="white", size=0.1)
ii <- ii + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
ii <- ii + coord_equal()
ii <- ii + facet_grid(percep ~ betas)
ii<- ii+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(C)")
ii<- ii+ theme(axis.title = element_text(face="bold", size=24))
ii<- ii + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=18)) 
ii<- ii + theme(strip.text.x = element_text(angle = 90))
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
ii

sdf <- summaryBy(duration~ H + betas +p+ percep, data=r1, FUN=mean)
jj <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
jj <- jj + geom_tile(color="white", size=0.1)
jj <- jj + scale_fill_viridis(name="Duration")
jj <- jj + coord_equal()
jj <- jj + facet_grid(percep ~ betas)
jj<- jj+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(D)")
jj<- jj+ theme(axis.title = element_text(face="bold", size=24))
jj<- jj + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
jj<- jj + theme(strip.text = element_text(vjust=0.5, size=18)) 
jj<- jj + theme(strip.text.x = element_text(angle = 90))
jj<- jj + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
jj

tiff("FigureS8_heatmap.tiff", height = 18, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(hh,gg, ii,jj, cols=1)
dev.off()
```

#Supplement beta2/beta3
```{r}
#Function to calculate rsf
myrsf=function(x,b1,b2) exp(x*b1+x^2*b2)   #caclulate rsf

#Function to calculate probability of selecting a given cell relative to other cells
#' @param x= \delta N
#' @param x.1= baseline population size of individuals
#' @param b2= \beta2 
#' @param b3= \beta3 (quadratic coefficient for RSF)
#' @param ncells= number of cells in neighborhood (e.g., 9, 25, 49)
myprsf=function(x,x.1,b2,b3,ncells)  #calculates rsf value for each cell; ncells= number of cells
{ lowlocs=myrsf(x.1,b2,b3)*(ncells-1)  #x = delta n
hiloc=myrsf(x+x.1,b2,b3)    
phi=hiloc/(hiloc+lowlocs)}

##beta2= 0, beta3=0
A <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
  stat_function(fun = myprsf, args = list(0, 0, 0, 9),
                aes(linetype = "N=0")) +
  stat_function(fun =  myprsf, args = list(2, 0, 0, 9),
                aes(linetype = "N=2")) +
  stat_function(fun =  myprsf, args = list(4, 0, 0, 9),
                aes(linetype = "N=4")) +
  scale_x_continuous(name = expression(paste(Delta, "N")),
                     breaks = seq(0, 6, 1),
                     limits=c(0, 6)) +
  geom_hline(yintercept = 1/9, colour="red") + 
  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
  ggtitle(expression(paste("(A) ", beta[2], "= 0 & ", beta[3], "= 0 (Random)"))) +
  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
A

##beta2= 0, beta3=-1
B <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
  stat_function(fun = myprsf, args = list(0, 0, -1, 9),
                aes(linetype = "N=0")) +
  stat_function(fun =  myprsf, args = list(2, 0, -1, 9),
                aes(linetype = "N=2")) +
  stat_function(fun =  myprsf, args = list(4, 0, -1, 9),
                aes(linetype = "N=4")) +
  scale_x_continuous(name = expression(paste(Delta, "N")),
                     breaks = seq(0, 6, 1),
                     limits=c(0, 6)) +
  geom_hline(yintercept = 1/9, colour="red") + 
  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
  ggtitle(expression(paste("(B) ", beta[2], "= 0 & ", beta[3], "= -1 (Negative)"))) +
  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
B

##beta2= 1, beta3=-1
C <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
  stat_function(fun = myprsf, args = list(0, 1, -1, 9),
                aes(linetype = "N=0")) +
  stat_function(fun =  myprsf, args = list(2, 1, -1, 9),
                aes(linetype = "N=2")) +
  stat_function(fun =  myprsf, args = list(4, 1, -1, 9),
                aes(linetype = "N=4")) +
  scale_x_continuous(name = expression(paste(Delta, "N")),
                     breaks = seq(0, 6, 1),
                     limits=c(0, 6)) +
  geom_hline(yintercept = 1/9, colour="red") + 
  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
  ggtitle(expression(paste("(C) ", beta[2], "= 1 & ", beta[3], "=-1 (Positive)"))) +
  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
C

##beta2= 0, beta3=0
D <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
  stat_function(fun = myprsf, args = list(0, 1, -0.5, 9),
                aes(linetype = "N=0")) +
  stat_function(fun =  myprsf, args = list(2, 1, -0.5, 9),
                aes(linetype = "N=2")) +
  stat_function(fun =  myprsf, args = list(4, 1, -0.5, 9),
                aes(linetype = "N=4")) +
  scale_x_continuous(name = expression(paste(Delta, "N")),
                     breaks = seq(0, 6, 1),
                     limits=c(0, 6)) +
  geom_hline(yintercept = 1/9, colour="red") + 
  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
  ggtitle(expression(paste("(D) ", beta[2], "= 1 & ", beta[3], "= -0.5 (Positive)"))) +
  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
D

##beta2= 2, beta3=-1
E <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
  stat_function(fun = myprsf, args = list(0, 2, -1, 9),
                aes(linetype = "N=0")) +
  stat_function(fun =  myprsf, args = list(2, 2, -1, 9),
                aes(linetype = "N=2")) +
  stat_function(fun =  myprsf, args = list(4, 2, -1, 9),
                aes(linetype = "N=4")) +
  scale_x_continuous(name = expression(paste(Delta, "N")),
                     breaks = seq(0, 6, 1),
                     limits=c(0, 6)) +
  geom_hline(yintercept = 1/9, colour="red") + 
  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
  ggtitle(expression(paste("(E) ", beta[2], "= 2 & ", beta[3], "=-1 (Positive)"))) +
  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
E

##beta2= 2, beta3=-0.5
F <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
  stat_function(fun = myprsf, args = list(0, 2, -0.5, 9),
                aes(linetype = "N=0")) +
  stat_function(fun =  myprsf, args = list(2, 2, -0.5, 9),
                aes(linetype = "N=2")) +
  stat_function(fun =  myprsf, args = list(4, 2, -0.5, 9),
                aes(linetype = "N=4")) +
  scale_x_continuous(name = expression(paste(Delta, "N")),
                     breaks = seq(0, 6, 1),
                     limits=c(0, 6)) +
  geom_hline(yintercept = 1/9, colour="red") + 
  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
  ggtitle(expression(paste("(F) ", beta[2], "= 2 & ", beta[3], "=-0.5 (Positive)"))) +
  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
F

tiff("RSF_conspecifics.tiff", height = 18, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(A,B,C,D,E,F, cols=2)
dev.off()
```

### 2018-01-24 RandomForestParallelLogitDur.R

@@ -1,0 +1,47 @@
+#' Running RandomForest in parallel for duration (if spreads beyond one individual, what factors
+#' determine how long infection lasts?)
+#' November 21, 2017
+#' @author Lauren White, whit1951@umn.edu
+
+#Load libraries
+library(parallel)
+library(doParallel)
+library(foreach)
+library(randomForest)
+
+#Detect cores
+ncores <- parallel::detectCores()
+doParallel::registerDoParallel(ncores)
+
+# setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
+# merged_data<-read.csv("IBMsummary.csv")
+
+#Load data
+#source('/home/forester/whit1951/IBMsummary.csv')
+merged_data<-read.csv("IBMsummary.csv")
+merged_data<-merged_data[-which(merged_data$beta2==5),] #Take out saturating beta2
+merged_data<-merged_data[which(merged_data$max_I>1),]
+
+# x <- matrix(runif(500), 100)
+# y <- gl(2, 50)
+
+x<-merged_data[,c(3:11)] #covariates
+y<-merged_data[,12] #response variable, duration
+#y<-merged_data[,14] #response variable, max_prev
+
+
+tic=Sys.time()
+rf <- foreach(ntree=rep(500, 20), .combine=combine, .multicombine=TRUE,
+              .packages='randomForest') %dopar% {
+                randomForest(x, y, ntree=ntree, importance=TRUE)
+              }
+print(difftime(Sys.time(),tic,units="mins"))
+save(rf, file = "RF_logit_dur.RData")
+
+#varImpPlot(rf, type=2, main= "Duration")
+
+imp_dur<-rf$importance
+write.csv(imp_dur, "logit_imp_dur.csv")
+
+
+rm(list=ls(all=T)) #clear workspace

### 2018-01-24 move_sim1.R

@@ -1,0 +1,42 @@
+#Run IBM_loop_function in parallel via clusters
+#August 24, 2017
+#Updated with \beta_3\ values
+
+library(parallel)
+library(foreach)
+library(doParallel)
+library(SDMTools)
+
+#load functions
+#source('C:/Users/law2y/OneDrive/R Code/IBM/May 2017/MSI Code/sim_parallel_functions.R')
+source('/home/forester/whit1951/sim_parallel_functions_2017_08_22.R')
+
+maxtime<-10000
+nsim<-100
+k<-8 #dimensions of landscape= 2^k+1
+density<-0.25
+inf_prob<-0.2
+rec_rate<-0.1
+percep<- 1
+p<-0.25 #0.5, 0.75
+H<-c(0.1, 0.5, 0.9)
+beta1<-c(0, 3, 6)
+beta2<-c(0, 5)
+beta3<-c(0, -1)
+
+params<-expand.grid(maxtime=maxtime, nsim=nsim, k=k, density=density, inf_prob=inf_prob, rec_rate=rec_rate, p=p, H=H, beta1=beta1, beta2=beta2, beta3=beta3, percep=percep)
+params<-params[-which(params$beta2==5 & params$beta3==0),]
+#summary_data<-list(NA)
+
+## Apply the declared function in parallel
+
+ncores <- parallel::detectCores()
+doParallel::registerDoParallel(ncores)
+tic=Sys.time()
+foreach(n = 1:nrow(params)) %dopar% IBM_loop_function(params[n,]$maxtime, params[n,]$nsim, params[n,]$k, params[n,]$density, params[n,]$inf_prob, params[n,]$rec_rate, params[n,]$p, params[n,]$H, params[n,]$beta1, params[n,]$beta2, params[n,]$beta3, params[n,]$percep)
+print(difftime(Sys.time(),tic,units="mins"))
+
+#save(summary_data, file="move_sim1.RData")
+#save(params, file="parameters_sim1.RData")
+
+rm(list=ls(all=T)) #clear workspace

### 2018-01-24 sim_parallel_functions_2017_08_22.R

@@ -1,0 +1,523 @@
+#sim_parallel_functions
+#Updated May 25, 2017 to reflect errors in torus wrapping found in previous version
+#Updated August 23, 2017 to scale by number of conspecfics rather than conspecific density &
+#to update the RSF to include \beta_3 for a quadratic conspecific term &
+#to record landscape stats for each landscape generated
+
+#############################################################################################
+#############################################################################################
+sampfun<-function(x){
+  ## A convenience function to use with apply when sampling values from rows within a matrix.
+  sample(1:length(x),1,prob=x) 
+}
+
+#############################################################################################
+#############################################################################################
+#' Calculate distance weight on a matrix
+#'
+#' Convert distances in x,y (row, col on a matrix) to distances and then weight according to a function.
+#'  
+#' @param celldist matrix. Should represent a two-column matrix of change in row and column ranks, respectively.
+#' @param min.dist numeric. The distance to use for celldist==0 (i.e., for the cell of origin).
+#' @param dist.weight.fun function. A function to use for calculating the distance weight (e.g., dgamma)
+#' @param ... Other parameters to pass to dist.weight.fun.
+#' @author James Forester
+#' @export
+get.dist.weight <-function(celldist, min.dist=0.5, dist.weight.fun=NULL,...){
+  ##calculate distance from central cell to others in the neighborhood
+  celldist=sqrt(rowSums(celldist^2)) #sqrt((x-0)^2+ (y-0)^2)
+  celldist[celldist==0]=min.dist
+  
+  if(is.function(dist.weight.fun)){
+    ##calculate weight, assuming a uniform bearing distribution
+    cell.dist.weight=dist.weight.fun(celldist,...)/(2*pi*celldist)
+  }else{
+    ##default to inverse distance weight
+    cell.dist.weight=1/(2*pi*celldist^2)
+  }
+  
+  return(cell.dist.weight)
+}
+
+
+#############################################################################################
+#############################################################################################
+#' Calculate coordinates of neighboring cells
[…]

### 2018-01-24 Manuscript_figures_2017_12_12.Rmd
Remove computer-specific setwd()

@@
 ```{r}
-setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
+#Set working directory to where IBMsummary.csv is located
+#setwd()
 merged_data<-read.csv("IBMsummary.csv")
@@
 #Set working directory of where to produce Figures
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
+#setwd()
 ```
@@
 
-##Figure 1
+## Figure 1
 Representation of neutral landscapes
@@
 
-##Figure 2
+## Figure 2
 Random forest variable importance results
@@
 library(randomForest)
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")
+#setwd()
 
@@
 
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
+#setwd()
 tiff("Fig2_RF.tif", height =16 , width =8.7, units = "cm", compression = "lzw", res = 300)
@@
 
-##Figure 3
+## Figure 3
 Box plots rec rate vs. density
 ```{r}
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
+#setwd()
 sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks
@@
 
-##Figure 4
+## Figure 4
 ```{r}
@@
 
-##Figure 4 (log version)
+## Figure 4 (log version)
 ```{r}
@@
 
-##Figure 5
+## Figure 5
 ```{r}
@@
 
-##Figure 5 (log version)
+## Figure 5 (log version)
 ```{r}
@@
 
-##Figure 6
+## Figure 6
 Comparing effects on landscape structure for a single RSF(\beta_1=6, \beta_2=2, \beta_3=-0.5) for different densities, perceptual distances, and recovery rates.
@@
 
-##Supplementary Figure 7
+## Supplementary Figure 2
 Box plot of percep vs. rec rate vs. density
@@
 
-tiff("FigureS7.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
+tiff("FigureS2.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
 multiplot(gg,hh, cols=1)
@@
 
-##Supplementary Figure 8 (Heat map)
+## Supplementary Figure 3 (Heat map)
 Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing rec rates 0.1 and 0.2
@@
 
-tiff("FigureS8_heatmap.tiff", height = 18, width = 14, units = "in", compression = "lzw", res = 300)
+tiff("FigureS3_heatmap.tiff", height = 18, width = 14, units = "in", compression = "lzw", res = 300)
 multiplot(hh,gg, ii,jj, cols=1)
@@
 
-#Supplement beta2/beta3
+## Supplementary Figure 1 
+Calibrate beta1/beta2/beta3
 ```{r}

### 2018-01-24 RandomForestParallelLogit.R
Delete RandomForestParallelLogit.R

@@ -1,49 +1,0 @@
-#' Running RandomForest in parallel for max prevalence (if pathogen spreads to another individual, what
-#' determines severity of outbreak?)
-#' November 21, 2017
-#' @author Lauren White, whit1951@umn.edu
-
-#Load libraries
-library(parallel)
-library(doParallel)
-library(foreach)
-library(randomForest)
-
-#TEsting
-#Detect cores
-ncores <- parallel::detectCores()
-doParallel::registerDoParallel(ncores)
-
-# setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
-# merged_data<-read.csv("IBMsummary.csv")
-
-#Load data
-#source('/home/forester/whit1951/IBMsummary.csv')
-merged_data<-read.csv("IBMsummary.csv")
-merged_data<-merged_data[-which(merged_data$beta2==5),] #Take out saturating beta2
-merged_data$outbreak<-ifelse(merged_data$max_I>1, 1,0)
-
-# x <- matrix(runif(500), 100)
-# y <- gl(2, 50)
-
-x<-merged_data[,c(3:11)] #covariates
-#y<-merged_data[,12] #response variable, duration
-y<-merged_data[,17] #response variable, outbreak (0 or 1)
-
-
-tic=Sys.time()
-set.seed(123)
-rf <- foreach(ntree=rep(500, 20), .combine=combine, .multicombine=TRUE,
-              .packages='randomForest') %dopar% {
-                randomForest(x, y, ntree=ntree, importance=TRUE)
-              }
-print(difftime(Sys.time(),tic,units="mins"))
-save(rf, file = "RF_logit.RData")
-
-#varImpPlot(rf, type=2, main= "Duration")
-
-imp_logit<-rf$importance
-write.csv(imp_logit, "imp_logit.csv")
-
-
-rm(list=ls(all=T)) #clear workspace

### 2018-01-24 RandomForestParallelLogitDur.R
Delete RandomForestParallelLogitDur.R

@@ -1,47 +1,0 @@
-#' Running RandomForest in parallel for duration (if spreads beyond one individual, what factors
-#' determine how long infection lasts?)
-#' November 21, 2017
-#' @author Lauren White, whit1951@umn.edu
-
-#Load libraries
-library(parallel)
-library(doParallel)
-library(foreach)
-library(randomForest)
-
-#Detect cores
-ncores <- parallel::detectCores()
-doParallel::registerDoParallel(ncores)
-
-# setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
-# merged_data<-read.csv("IBMsummary.csv")
-
-#Load data
-#source('/home/forester/whit1951/IBMsummary.csv')
-merged_data<-read.csv("IBMsummary.csv")
-merged_data<-merged_data[-which(merged_data$beta2==5),] #Take out saturating beta2
-merged_data<-merged_data[which(merged_data$max_I>1),]
-
-# x <- matrix(runif(500), 100)
-# y <- gl(2, 50)
-
-x<-merged_data[,c(3:11)] #covariates
-y<-merged_data[,12] #response variable, duration
-#y<-merged_data[,14] #response variable, max_prev
-
-
-tic=Sys.time()
-rf <- foreach(ntree=rep(500, 20), .combine=combine, .multicombine=TRUE,
-              .packages='randomForest') %dopar% {
-                randomForest(x, y, ntree=ntree, importance=TRUE)
-              }
-print(difftime(Sys.time(),tic,units="mins"))
-save(rf, file = "RF_logit_dur.RData")
-
-#varImpPlot(rf, type=2, main= "Duration")
-
-imp_dur<-rf$importance
-write.csv(imp_dur, "logit_imp_dur.csv")
-
-
-rm(list=ls(all=T)) #clear workspace

### 2018-01-24 RandomForestParallelLogitPrev.R
Delete RandomForestParallelLogitPrev.R

@@ -1,48 +1,0 @@
-#' Running RandomForest in parallel for max prevalence (if pathogen spreads to another individual, what
-#' determines severity of outbreak?)
-#' November 21, 2017
-#' @author Lauren White, whit1951@umn.edu
-
-#Load libraries
-library(parallel)
-library(doParallel)
-library(foreach)
-library(randomForest)
-
-#Detect cores
-ncores <- parallel::detectCores()
-doParallel::registerDoParallel(ncores)
-
-# setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
-# merged_data<-read.csv("IBMsummary.csv")
-
-#Load data
-#source('/home/forester/whit1951/IBMsummary.csv')
-merged_data<-read.csv("IBMsummary.csv")
-merged_data<-merged_data[-which(merged_data$beta2==5),] #Take out saturating beta2
-merged_data<-merged_data[which(merged_data$max_I>1),]
-
-# x <- matrix(runif(500), 100)
-# y <- gl(2, 50)
-
-x<-merged_data[,c(3:11)] #covariates
-#y<-merged_data[,12] #response variable, duration
-y<-merged_data[,14] #response variable, max_prev
-
-
-tic=Sys.time()
-set.seed(123)
-rf <- foreach(ntree=rep(500, 20), .combine=combine, .multicombine=TRUE,
-              .packages='randomForest') %dopar% {
-                randomForest(x, y, ntree=ntree, importance=TRUE)
-              }
-print(difftime(Sys.time(),tic,units="mins"))
-save(rf, file = "RF_logit_prev.RData")
-
-#varImpPlot(rf, type=2, main= "Duration")
-
-imp_maxprev<-rf$importance
-write.csv(imp_maxprev, "logit_imp_maxprev.csv")
-
-
-rm(list=ls(all=T)) #clear workspace

### 2018-01-24 RandomForestParallelLogit.R
Add files via upload

@@ -1,0 +1,49 @@
+#' Running RandomForest in parallel for max prevalence (if pathogen spreads to another individual, what
+#' determines severity of outbreak?)
+#' November 21, 2017
+#' @author Lauren White, whit1951@umn.edu
+
+#Load libraries
+library(parallel)
+library(doParallel)
+library(foreach)
+library(randomForest)
+
+#TEsting
+#Detect cores
+ncores <- parallel::detectCores()
+doParallel::registerDoParallel(ncores)
+
+# setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
+# merged_data<-read.csv("IBMsummary.csv")
+
+#Load data
+#source('/home/forester/whit1951/IBMsummary.csv')
+merged_data<-read.csv("IBMsummary.csv")
+merged_data<-merged_data[-which(merged_data$beta2==5),] #Take out saturating beta2
+merged_data$outbreak<-ifelse(merged_data$max_I>1, 1,0)
+
+# x <- matrix(runif(500), 100)
+# y <- gl(2, 50)
+
+x<-merged_data[,c(3:11)] #covariates
+#y<-merged_data[,12] #response variable, duration
+y<-merged_data[,17] #response variable, outbreak (0 or 1)
+
+
+tic=Sys.time()
+set.seed(123)
+rf <- foreach(ntree=rep(500, 20), .combine=combine, .multicombine=TRUE,
+              .packages='randomForest') %dopar% {
+                randomForest(x, y, ntree=ntree, importance=TRUE)
+              }
+print(difftime(Sys.time(),tic,units="mins"))
+save(rf, file = "RF_logit.RData")
+
+#varImpPlot(rf, type=2, main= "Duration")
+
+imp_logit<-rf$importance
+write.csv(imp_logit, "imp_logit.csv")
+
+
+rm(list=ls(all=T)) #clear workspace

### 2018-01-24 RandomForestParallelLogitPrev.R

@@ -1,0 +1,48 @@
+#' Running RandomForest in parallel for max prevalence (if pathogen spreads to another individual, what
+#' determines severity of outbreak?)
+#' November 21, 2017
+#' @author Lauren White, whit1951@umn.edu
+
+#Load libraries
+library(parallel)
+library(doParallel)
+library(foreach)
+library(randomForest)
+
+#Detect cores
+ncores <- parallel::detectCores()
+doParallel::registerDoParallel(ncores)
+
+# setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
+# merged_data<-read.csv("IBMsummary.csv")
+
+#Load data
+#source('/home/forester/whit1951/IBMsummary.csv')
+merged_data<-read.csv("IBMsummary.csv")
+merged_data<-merged_data[-which(merged_data$beta2==5),] #Take out saturating beta2
+merged_data<-merged_data[which(merged_data$max_I>1),]
+
+# x <- matrix(runif(500), 100)
+# y <- gl(2, 50)
+
+x<-merged_data[,c(3:11)] #covariates
+#y<-merged_data[,12] #response variable, duration
+y<-merged_data[,14] #response variable, max_prev
+
+
+tic=Sys.time()
+set.seed(123)
+rf <- foreach(ntree=rep(500, 20), .combine=combine, .multicombine=TRUE,
+              .packages='randomForest') %dopar% {
+                randomForest(x, y, ntree=ntree, importance=TRUE)
+              }
+print(difftime(Sys.time(),tic,units="mins"))
+save(rf, file = "RF_logit_prev.RData")
+
+#varImpPlot(rf, type=2, main= "Duration")
+
+imp_maxprev<-rf$importance
+write.csv(imp_maxprev, "logit_imp_maxprev.csv")
+
+
+rm(list=ls(all=T)) #clear workspace

### 2018-01-24 RandomForestParallelLogit.R
Update RandomForestParallelLogit.R

@@ -14,17 +14,12 @@ library(randomForest)
 ncores <- parallel::detectCores()
 doParallel::registerDoParallel(ncores)
 
-# setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
-# merged_data<-read.csv("IBMsummary.csv")
 
 #Load data
-#source('/home/forester/whit1951/IBMsummary.csv')
 merged_data<-read.csv("IBMsummary.csv")
 merged_data<-merged_data[-which(merged_data$beta2==5),] #Take out saturating beta2
 merged_data$outbreak<-ifelse(merged_data$max_I>1, 1,0)
 
-# x <- matrix(runif(500), 100)
-# y <- gl(2, 50)
 
 x<-merged_data[,c(3:11)] #covariates
 #y<-merged_data[,12] #response variable, duration

### 2018-01-24 RandomForestParallelLogitDur.R
Remove specific file pathways

@@ -13,17 +13,12 @@ library(randomForest)
 ncores <- parallel::detectCores()
 doParallel::registerDoParallel(ncores)
 
-# setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
-# merged_data<-read.csv("IBMsummary.csv")
 
 #Load data
-#source('/home/forester/whit1951/IBMsummary.csv')
 merged_data<-read.csv("IBMsummary.csv")
 merged_data<-merged_data[-which(merged_data$beta2==5),] #Take out saturating beta2
 merged_data<-merged_data[which(merged_data$max_I>1),]
 
-# x <- matrix(runif(500), 100)
-# y <- gl(2, 50)
 
 x<-merged_data[,c(3:11)] #covariates
 y<-merged_data[,12] #response variable, duration

### 2018-01-24 RandomForestParallelLogitPrev.R
Remove specific file pathways

@@ -13,17 +13,12 @@ library(randomForest)
 ncores <- parallel::detectCores()
 doParallel::registerDoParallel(ncores)
 
-# setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
-# merged_data<-read.csv("IBMsummary.csv")
 
 #Load data
-#source('/home/forester/whit1951/IBMsummary.csv')
 merged_data<-read.csv("IBMsummary.csv")
 merged_data<-merged_data[-which(merged_data$beta2==5),] #Take out saturating beta2
 merged_data<-merged_data[which(merged_data$max_I>1),]
 
-# x <- matrix(runif(500), 100)
-# y <- gl(2, 50)
 
 x<-merged_data[,c(3:11)] #covariates
 #y<-merged_data[,12] #response variable, duration

### 2018-01-24 move_sim1.R
Remove specific file pathways

@@ -8,9 +8,9 @@ library(doParallel)
 library(SDMTools)
 
 #load functions
-#source('C:/Users/law2y/OneDrive/R Code/IBM/May 2017/MSI Code/sim_parallel_functions.R')
-source('/home/forester/whit1951/sim_parallel_functions_2017_08_22.R')
+source('.../sim_parallel_functions_2017_08_22.R')
 
+#specify parameters to run
 maxtime<-10000
 nsim<-100
 k<-8 #dimensions of landscape= 2^k+1

### 2018-03-02 SimpleSIR.Rmd
Compare simulations to homogenous mixing model

---
title: "Simple SIR"
author: "Lauren White"
date: "February 24, 2018"
output: html_document
---

Deterministic and more simplistic stochastic SIR models for conspecific density vs. rec. rate combinations tested in spatially-explicit model

#Load libraries

```{r setup}
library(deSolve)
```

## Deterministic SIR Model
Code adapted from: <http://sbfnk.github.io/chennai-modelling/intro_to_r_gk.html>
```{r}
par(mfrow=c(1,1))
k<-8
dim<-2^k + 1
density<-0.25
n.initial <- round(density*dim^2) # inital population size

init <- c(S = n.initial-1, I = 1, R = 0)
times <- seq(0, 1000, by = 1) #1000 time steps

freq_sir <- function(time, state, parameters) {
    with(as.list(c(state, parameters)), {
        dS = -beta * S * I/16512  # The change in S 
        dI = beta * S * I/16512 - gamma * I
        dR = gamma * I
        return(list(c(dS, dI, dR))) 
    })
}

density_sir <- function(time, state, parameters) {
    with(as.list(c(state, parameters)), {
        dS = -beta * S * I/257  # The change in S 
        dI = beta * S * I/257 - gamma * I
        dR = gamma * I
        return(list(c(dS, dI, dR))) 
    })
}

parameters <- c(beta = 0.2, gamma = 0.4)

out_freq <- ode(y = init, func = freq_sir, times = times, parms = parameters)
out_density <- ode(y = init, func = density_sir, times = times, parms = parameters)

plot(out_freq[, "time"], out_freq[, "I"]/n.initial, type = "l", lwd = 10, col = "green", xlab = "Time", 
    ylab = "Prevalence")
lines(out_density[, "time"], out_density[, "I"]/n.initial, col="red")
# lines(out[, "time"], out[, "R"], col = "blue", lwd = 10)
#legend("bottomright", c("Susceptibles", "Infecteds", "Recovereds"), lwd = 10, lty = 1, 
#    col = 2:4)  # Add legend and specific position

```

## Stochastic SIR Model

```{r}
#' Function to randomly generate individuals and randomly assign 'nI' number of infected
#' individuals at t=0
#' @param n.initial- the number of desired individuals to start with
#' @param nI- the number of infected individuals to start with at t=0
#' @author Lauren White
make.inds <- function(n.initial, nI){
  id<-1:n.initial
  I<-sample(1:n.initial, nI)
  status<-rep("S", times=n.initial)
  status[I]<-"I"
  inds <- data.frame(id = id, status=status, stringsAsFactors=FALSE) 
  inds
}

#' Function that determines whether not a transmission event occurs
#' First checks to see if there are any individuals + infected infividuals present in the same cell
#' Then calculates final transmission probability based on # of infected individuals present
#' @param inds- dataframe with individual traits, including infection status
#' @param transProb- per interaction transmissioin probability
#' @author Lauren White
#' @date February 24, 2018
#' 
infection_simple<-function(inds, transProb){
    s_inds<-which(inds$status=="S" ) #which individuals are currently infected?
    if (length(s_inds>0)){
      i_count<-which(inds$status=="I" ) #which individuals are currently infected?
      finalProb <- 1 - (1 - transProb)^i_count
      transmit <- rbinom(length(s_inds), 1, finalProb)
      new_i<-s_inds[which(transmit == 1)]
      inds$status[new_i]<-"I"
  } 
  return(inds)
}

#############################################################################################
#############################################################################################

#' Function that allows infected individuals to recover at rate 'gamma'
#' @param inds: the dataframe describing the current status and location of individuals in the simulation
#' @param gamma: the recovery rate
#' @author Lauren White
recover.inds<-function(inds, gamma){
  infected<-which(inds$status=="I" ) #which individuals are currently infected?
  if(length(infected>0)){
    rec.prob<-runif(length(infected), min=0, max=1)
    for (i in 1:length(infected)){
      if(rec.prob[i]<= gamma){
        inds$status[infected[i]]<-"R"
      }
    }
  }
  return(inds)
}

SIR_simple_function<-function(maxtime, nsim, k, density, inf_prob, rec_rate){
  #Set up initial conditions for all simulations
  dim<-2^k + 1
  n.initial <- round(density*dim^2) # inital population size

  ##Initiate data structure across simulations
  mydata<-list(inds=NULL, N=NULL, infdat=NULL)
  filename<-paste("k", k, "dens", density, "inf", inf_prob, "rec", rec_rate, sep="")
  summary<-data.frame(k=rep(k, times=nsim), density=rep(density, times=nsim), inf_prob=rep(inf_prob, times=nsim), rec_rate=rep(rec_rate, times=nsim), duration=NaN, max_I=NaN, max_prevalence=NaN)
  infected<-matrix(NaN, nrow=maxtime, ncol=nsim)

  #Iterate for 'nsim' number of simulations per given parameter set
  for(count in 1:nsim){
    ##Initiate individuals
    inds <- make.inds(n.initial=n.initial, nI=1)
    mydata$inds[[count]]<-inds

    #Initiate longterm storage for infection data
    infdat<-inds$status

    # Object for storing results for single simulation (disease dynamics through time)
    N <-data.frame(S=NaN, I=NaN, R=NaN)
    N[1,] <- c(sum(inds$status=="S"), sum(inds$status=="I"), sum(inds$status=="R"))

    ##Run the simulation for a max of 'T' timesteps
    for(t in 2:maxtime){

      #Disease process(es)
      inds<-infection_simple(inds, transProb=inf_prob)
      inds<-recover.inds(inds, gamma=rec_rate)

      #Update disease status lists
      infdat<-cbind(infdat,inds$status)
      N[t,] <- c(sum(inds$status=="S"), sum(inds$status=="I"), sum(inds$status=="R"))
      if(sum(inds$status=="I")==0){ #If number of infected in individuals--> 0, stop running
        summary$duration[count]<-t-1
        for (i in t:maxtime){
          N[i,]<-N[t,] #automatically fill remaining time slots with current N values
        }
        break
      }
    }
    mydata$N[[count]]<-N
    mydata$infdat[[count]]<-infdat
    summary$max_I[count]<-max(N$I)
    summary$max_prevalence[count]<-max(N$I)/n.initial
    infected[,count]<-N$I
    print(count)
  }
  #Record output
  write.csv(summary,file=paste(filename,"summary.csv", sep="_"))
  write.csv(infected,file=paste(filename,"infected.csv", sep="_"))
}

# tic=Sys.time()
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")

#SIR_simple_function<-function(maxtime, nsim, k, density, inf_prob, rec_rate)
SIR_simple_function(1000, 100, 8, 0.25, 0.2, 0.1)
SIR_simple_function(1000, 100, 8, 0.25, 0.2, 0.2)
SIR_simple_function(1000, 100, 8, 0.25, 0.2, 0.4)
SIR_simple_function(1000, 100, 8, 0.5, 0.2, 0.1)
SIR_simple_function(1000, 100, 8, 0.5, 0.2, 0.2)
SIR_simple_function(1000, 100, 8, 0.5, 0.2, 0.4)

# print(difftime(Sys.time(),tic,units="mins"))

```
Plot deterministic and stochastic SIR results (assuming equal mixing)
```{r}
par(mfrow=c(2, 3))
k<-8
dim<-2^k + 1
density<-0.25
n.initial25 <- round(density*dim^2) # inital population size

density<-0.5
n.initial50 <- round(density*dim^2) # inital population size

#Density=0.25
init <- c(S = n.initial25-1, I = 1, R = 0)
times <- seq(0, 100, by = 1) #1000 time steps

stoch<-read.csv("k8dens0.25inf0.2rec0.1_infected.csv")
out <- ode(y = init, func = sir, times = times, parms = c(beta = 0.2, gamma = 0.1))
head(out)

plot(out[, "time"], out[, "I"]/n.initial25, type = "l", lwd = 10, col = "green", xlab = "Time", 
    ylab = "Prevalence")
for(i in 1:(dim(stoch)[2]-1)){
lines(stoch$X, stoch[,i+1]/n.initial25, col = "red", lwd = 1)
}
title("density=0.25;beta=0.2;gamma=0.1")

stoch<-read.csv("k8dens0.25inf0.2rec0.2_infected.csv")
out <- ode(y = init, func = sir, times = times, parms = c(beta = 0.2, gamma = 0.2))
head(out)

plot(out[, "time"], out[, "I"]/n.initial25, type = "l", lwd = 10, col = "green", xlab = "Time", 
    ylab = "Prevalence")
for(i in 1:(dim(stoch)[2]-1)){
lines(stoch$X, stoch[,i+1]/n.initial25, col = "red", lwd = 1)
}
title("density=0.25;beta=0.2;gamma=0.2")

stoch<-read.csv("k8dens0.25inf0.2rec0.4_infected.csv")
out <- ode(y = init, func = sir, times = times, parms = c(beta = 0.2, gamma = 0.4))
head(out)

plot(out[, "time"], out[, "I"]/n.initial25, type = "l", lwd = 10, col = "green", xlab = "Time", 
    ylab = "Prevalence")
for(i in 1:(dim(stoch)[2]-1)){
  lines(stoch$X, stoch[,i+1]/n.initial25, col = "red", lwd = 1)
}
title("density=0.25;beta=0.2;gamma=0.4")

#Density=0.50
init <- c(S = n.initial50-1, I = 1, R = 0)
times <- seq(0, 100, by = 1) #1000 time steps

stoch<-read.csv("k8dens0.5inf0.2rec0.1_infected.csv")
out <- ode(y = init, func = sir, times = times, parms = c(beta = 0.2, gamma = 0.1))
head(out)

plot(out[, "time"], out[, "I"]/n.initial50, type = "l", lwd = 10, col = "green", xlab = "Time", 
    ylab = "Prevalence")
for(i in 1:(dim(stoch)[2]-1)){
lines(stoch$X, stoch[,i+1]/n.initial50, col = "red", lwd = 1)
}
title("density=0.5;beta=0.2;gamma=0.1")

stoch<-read.csv("k8dens0.5inf0.2rec0.2_infected.csv")
out <- ode(y = init, func = sir, times = times, parms = c(beta = 0.2, gamma = 0.2))
head(out)

plot(out[, "time"], out[, "I"]/n.initial50, type = "l", lwd = 10, col = "green", xlab = "Time", 
    ylab = "Prevalence")
for(i in 1:(dim(stoch)[2]-1)){
lines(stoch$X, stoch[,i+1]/n.initial50, col = "red", lwd = 1)
}
title("density=0.5;beta=0.2;gamma=0.2")

stoch<-read.csv("k8dens0.5inf0.2rec0.4_infected.csv")
out <- ode(y = init, func = sir, times = times, parms = c(beta = 0.2, gamma = 0.4))
head(out)

plot(out[, "time"], out[, "I"]/n.initial50, type = "l", lwd = 10, col = "green", xlab = "Time", 
    ylab = "Prevalence")
for(i in 1:(dim(stoch)[2]-1)){
  lines(stoch$X, stoch[,i+1]/n.initial50, col = "red", lwd = 1)
}
title("density=0.5;beta=0.2;gamma=0.4")
```

##Combine simulation ouput
```{r}
library(doBy)
library(ggplot2)
library(viridis)
library(ggthemes)
library(scales)
library(lsr)

##Read in file names 
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")
filenames <- list.files(path = "C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")
summaries<-filenames[grep("summary", filenames)] #summary data
infecteds<-filenames[grep("infect", filenames)] #I data

##Make a merged dataset from all available .csv files
SIRdata_merged<- do.call("rbind", lapply(summaries, read.csv, header = TRUE))
#setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/")

```

##Box plots
Box plots comparing density and recovery rates
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
#sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks

#tiff("boxplot_prev.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
gg<- ggplot(data=SIRdata_merged, aes(y=max_prevalence, x=as.factor(rec_rate)))
#gg<- gg+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
gg<-gg+ geom_boxplot()+ facet_grid(. ~ density, scales= "free_x", labeller=label_both)
gg<- gg+ labs(x = expression(Recovery~rate~(gamma)), y = "Maximum prevalence",title="(A)")
gg<- gg+ theme(axis.title = element_text(size=16),title=element_text(face="bold", size=16))
gg<- gg + theme(axis.text.x = element_text(vjust=0.5, size=16))
gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
gg<- gg + theme(strip.text = element_text(vjust=0.5, size=14)) 
gg
#dev.off()

means <- aggregate(duration ~ density+ rec_rate, SIRdata_merged, mean)
#tiff("boxplot_dur.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
hh<- ggplot(data=SIRdata_merged, aes(x=as.factor(rec_rate), y=duration))
#hh<- hh+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
hh<-hh+ geom_boxplot()+ facet_grid(. ~ density, scales= "free_x", labeller=label_both)
hh<- hh+ labs(fill= "density", x = expression(Recovery~rate~(gamma)), y = "Duration", title="(B)")
hh<- hh+ theme(axis.title = element_text(face="bold", size=16), title=element_text(face="bold", size=16))
hh<- hh + theme(axis.text.x = element_text(vjust=0.5, size=16))
hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
hh<- hh + theme(strip.text = element_text(vjust=0.5, size=14))
hh<- hh + stat_summary(fun.y=mean, colour="darkred", geom="point", 
                           shape=18, size=3,show_guide = FALSE)
hh<-hh + geom_text(data = means , aes(label = duration, y = duration + 0.08))
hh
#dev.off()

tiff("DDtransmission.tif", height = 14, width = 8.7, units = "in", compression = "lzw", res = 300)
multiplot(gg,hh, cols=1)
dev.off()

```

##Box plot
Compare homogenous mixing and spatial models
```{r}
SIRdata_merged$percep<-"Homogenous"
SIRdata_merged$p<-NA
SIRdata_merged$H<-NA
SIRdata_merged$beta1<-NA
SIRdata_merged$beta2<-NA
SIRdata_merged$beta3<-NA
SIRdata_merged$betas<-NA
SIRdata_merged$pbyH<-NA
SIRdata_merged$Hurst<-NA
SIRdata_merged$proportion<-NA
SIRdata_merged$lstructure<-NA

h_vs_s <-rbind(sub_data, SIRdata_merged)
hh <- ggplot(h_vs_s, aes(x = as.factor(rec_rate), y = max_prevalence, fill = percep))
hh<-hh+ geom_boxplot()+ facet_grid(. ~ density, scales= "free_x", labeller=label_both)
hh<- hh+ labs(fill= "Perceptual \ndistance", x = expression(Recovery~rate~(gamma)), y = "Maximum prevalence", title="(A)")
hh<- hh+ theme(axis.title = element_text(face="bold", size=16), title=element_text(face="bold", size=16))
hh<- hh + theme(axis.text.x = element_text(vjust=0.5, size=16))
hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
hh<- hh + theme(strip.text = element_text(vjust=0.5, size=14))
#hh<- hh + stat_summary(fun.y=mean, colour="darkred", geom="point", 
                           #shape=18, size=3,show_guide = FALSE)
#hh<-hh + geom_text(data = means , aes(label = duration, y = duration + 0.08))
hh

ii <- ggplot(h_vs_s, aes(x = as.factor(rec_rate), y = duration, fill = percep))
ii<-ii+ geom_boxplot()+ facet_grid(. ~ density, scales= "free_x", labeller=label_both)
ii<- ii+ labs(fill= "Perceptual \ndistance", x = expression(Recovery~rate~(gamma)), y = "Duration", title="(B)")
ii<- ii+ theme(axis.title = element_text(face="bold", size=16), title=element_text(face="bold", size=16))
ii<- ii + theme(axis.text.x = element_text(vjust=0.5, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=14))
#ii<- ii + stat_summary(fun.y=mean, colour="darkred", geom="point", 
                           #shape=18, size=3,show_guide = FALSE)
#ii<-ii + geom_text(data = means , aes(label = duration, y = duration + 0.08))
ii

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
tiff("Compare_homog_spatial.tif", height = 8, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(hh,ii, cols=2)
dev.off()
```

### 2018-04-09 Manuscript_figures_2017_12_12.Rmd
Updated figure order and commented code

@@
 author: "Lauren White"
-date: "December 12, 2017"
+date: "April 3, 2018"
 output: html_document
@@
 library(SDMTools)
+library(cowplot)
 ```
@@
 ## Load and update summary dataset
-
-```{r}
-#Set working directory to where IBMsummary.csv is located
-#setwd()
+```{r}
+setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
 merged_data<-read.csv("IBMsummary.csv")
@@
 #Set working directory of where to produce Figures
-#setwd()
+setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
 ```
@@
 
-## Figure 1
-Representation of neutral landscapes
-```{r}
-#' Create neutral landscape maps
-library(raster)
-
-#' Use standard methods to generate fractal maps. Binary and continuous surfaces may be produced.
-#' 
-#' @param k integer. The extent of the map (2^k+1)^2 pixels
-#' @param h numeric. Level of aggregation in the map.
-#' @param p numeric (0,1). The proportion of map in habitat=1
-#' @param binary logical. If TRUE, a 0/1 categorical landscape is produced.
-#' @author Shannon Pittman, James Forester, modified by Lauren White
-#' @export
-#' @example examples/neutral.landscape_example.R
-fracland_mod <- function(k, h, p, binary = TRUE) {
-  ## Function for creating neutral landscapes Shannon Pittman University of Minnesota May, 2013 k = the extent of the map (2^k+1)^2 pixels h =
-  ## how clumped the map should be (ranging from ?? to ??) -- weird behavior at higher values p = proportion of map in habitat 1 binary =
-  ## plotflag == if TRUE will plot a filled contour version of the matrix
-
-  ## function call: testmap=land(6,1,.5,FALSE,TRUE)
-  A <- 2^k + 1  # Scalar-determines length of landscape matrix
-
-  #Right now, as written (1-p) represents the amount of habitat listed as "1"
-  B <- matrix(0, A, A)  # Creates landscape matrix
-
-  B[1, 1] <- 0
-  B[1, A] <- 0
-  B[A, 1] <- 0
-  B[A, A] <- 0
-
-  iter <- 1
-  for (iter in 1:k) {
-    scalef <- (0.5 + (1 - h)/2)^(iter)
-
-    d <- 2^(k - iter)
-
-    # ALL SQUARE STEPS#
-    for (i in seq(d + 1, A - d, 2 * d)) {
-      for (j in seq(d + 1, A - d, 2 * d)) {
-        B[i, j] <- mean(c(B[i - d, j - d], B[i - d, j + d], B[i + d, j - d], B[i + d, j + d])) + scalef * rnorm(n = 1)
-      }
-    }
-
-    # OUTSIDE DIAMOND STEP#
-    for (j in seq(d + 1, A - d, 2 * d)) {
-      B[1, j] <- mean(c(B[1, j - d], B[1, j + d], B[1 + d, j])) + scalef * rnorm(n = 1)
-      B[A, j] <- mean(c(B[A, j - d], B[A, j + d], B[A - d, j])) + scalef * rnorm(n = 1)
-    }
-
-    for (i in seq(d + 1, A - d, 2 * d)) {
-      B[i, 1] <- mean(c(B[i - d, 1], B[i + d, 1], B[i, 1 + d])) + scalef * rnorm(n = 1)
-      B[i, A] <- mean(c(B[i - d, A], B[i + d, A], B[i, A - d])) + scalef * rnorm(n = 1)
-    }
-
-    # INSIDE DIAMOND STEP#
-    if (2 * d + 1 <= A - 2 * d) {
-      for (i in seq(d + 1, A - d, 2 * d)) {
-        for (j in seq(2 * d + 1, A - 2 * d, 2 * d)) {
-          B[i, j] <- mean(c(B[i - d, j], B[i + d, j], B[i, j - d], B[i, j + d])) + scalef * rnorm(n = 1)
-        }
-      }
-
-      for (i in seq(2 * d + 1, A - 2 * d, 2 * d)) {
-        for (j in seq(d + 1, A - d, 2 * d)) {
-          B[i, j] <- mean(c(B[i - d, j], B[i + d, j], B[i, j - d], B[i, j + d])) + scalef * rnorm(n = 1)
-        }
-      }
-    }
-
-    iter <- iter + 1
-  }
-
-  if (binary == T) {
-    R <- sort(B)
-    PosR <- (1 - p) * length(R)  #larger values become habitat, designated as 1
-    pval <- R[PosR]
-    T1 <- which(B > pval)
-    T2 <- which(B <= pval)
-    B[T1] <- 1  #habitat is 1
-    B[T2] <- 0
-  } 
-  return(B)
-}
-
-landscape<-fracland_mod(k=7, h=0.1, p=0.25)
-map.1 <- raster(landscape)
-one<-spplot(map.1)
-landscape<-fracland_mod(k=7, h=0.1, p=0.5) 
-map.2 <- raster(landscape)
-two<-spplot(map.2)
-landscape<-fracland_mod(k=7, h=0.1, p=0.75)
-map.3 <- raster(landscape)
-three<-spplot(map.3)
-
-landscape<-fracland_mod(k=7, h=0.5, p=0.25) 
-map.4 <- raster(landscape)
-four<-spplot(map.4)
-landscape<-fracland_mod(k=7, h=0.5, p=0.5) 
-map.5 <- raster(landscape)
-five<-spplot(map.5)
-landscape<-fracland_mod(k=7, h=0.5, p=0.75)
-map.6 <- raster(landscape)
-six<-spplot(map.6)
-
-landscape<-fracland_mod(k=7, h=0.9, p=0.25)
-map.7 <- raster(landscape)
-seven<-spplot(map.7)
-landscape<-fracland_mod(k=7, h=0.9, p=0.5)
-map.8 <- raster(landscape)
-eight<-spplot(map.8)
-landscape<-fracland_mod(k=7, h=0.9, p=0.75)
-map.9 <- raster(landscape)
-# nine<-spplot(map.9)
-
-#convert the raster to points for plotting
-H<-rep(0.1, times=length(map.1))
-map.1 <- rasterToPoints(map.1)
-p<-rep(0.25, times=length(map.1))
-df <- data.frame(map.1, H, p)
-
-map.2 <- rasterToPoints(map.2)
-p<-rep(0.5, times=length(map.1))
-df2 <- data.frame(map.2, H, p)
-
-map.3 <- rasterToPoints(map.3)
-p<-rep(0.75, times=length(map.1))
-df3 <- data.frame(map.3, H, p)
-
-H<-rep(0.5, times=length(map.1))
-map.4 <- rasterToPoints(map.4)
-p<-rep(0.25, times=length(map.1))
-df4 <- data.frame(map.4, H, p)
-
-map.5 <- rasterToPoints(map.5)
-p<-rep(0.5, times=length(map.1))
-df5 <- data.frame(map.5, H, p)
-
-map.6 <- rasterToPoints(map.6)
-p<-rep(0.75, times=length(map.1))
-df6 <- data.frame(map.6, H, p)
-
-H<-rep(0.9, times=length(map.1))
-map.7 <- rasterToPoints(map.7)
-p<-rep(0.25, times=length(map.1))
-df7 <- data.frame(map.7, H, p)
-
-map.8 <- rasterToPoints(map.8)
-p<-rep(0.5, times=length(map.1))
-df8 <- data.frame(map.8, H, p)
-
-map.9 <- rasterToPoints(map.9)
-p<-rep(0.75, times=length(map.1))
-df9 <- data.frame(map.9, H, p)
-
-#Make the points a dataframe for ggplot
-
-df <- rbind(df, df2)
-df <- rbind(df, df3)
-df <- rbind(df, df4)
-df <- rbind(df, df5)
-df <- rbind(df, df6)
-df <- rbind(df, df7)
-df <- rbind(df, df8)
-df <- rbind(df, df9)
-
-my_x_title <- expression(paste("Hurst exponent- habitat patchiness (", italic("H"), ")"))
-my_y_title <- expression(paste("Proportion of available habitat (", italic("p"), ")"))
-
-#Now make the map
-tiff("Figure1_p_vs_H.tif", height = 8, width = 8, units = "in", compression = "lzw", res = 300)
-ggplot(data=df, aes(y=y, x=x)) +
-  geom_raster(aes(fill=layer)) +
-    theme_bw() +
-  coord_equal() +
-  facet_grid(p~ H) +
-  #scale_fill_viridis(name="Resource quality")+
-  #scale_fill_continuous(colours=c("#0000FFFF","#FFFFFFFF"))+
-  scale_fill_gradient(low="lightgrey", high="darkgreen", guide=FALSE) +
-  #scale_fill_continuous(guide = FALSE) +
-  labs(y=my_y_title, x=my_x_title)+
-  theme(axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
-  theme(axis.title = element_text(face="bold", size=28)) +
-  theme(strip.text = element_text(vjust=0.5, size=24))+ 
-  theme(legend.text = element_text(vjust=0.5, size=24), legend.title=element_text(vjust=0.5, size=28))
-dev.off()
-
-```
-
-## Figure 2
+##Figure 1
 Random forest variable importance results
@@
 library(randomForest)
-#setwd()
+setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")
 
@@
     "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
-    "percep" = "range")) +
+    "percep" = "r", "density"="d")) +
      #ylab("Mean Decrease in Accuracy (%IncMSE)") +
-    ylab(NULL)+
+    ylab("")+
+    theme_bw()+
     ggtitle("(A)") + #" Variable Importance for Epidemic \nSuccess") +
-    theme(axis.title = element_text(size=10),title=element_text(face="bold", size=10))+
-    coord_flip()+
-    theme_bw()
+    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8)) +
+    theme(plot.margin=unit(c(0.1,0.1,0,0), "cm"))+
+    coord_flip()
+    # theme_bw(axis.text=element_text(size=14),    axis.title=element_text(size=14,face="bold"), plot.title = element_text(size = 40))
 A
@@
     "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
-    "percep" = "range")) +
+    "percep" = "r", "density"="d")) +
      #ylab("Mean Decrease in Accuracy (%IncMSE)") +
-    ylab(NULL)+
-    theme(axis.title = element_text(size=10),title=element_text(face="bold", size=10))+
+    ylab("")+
+    theme_bw()+
     ggtitle("(B)") + #" Variable Importance for Maximum \nPrevalence|Success") +
-    coord_flip()+
-    theme_bw()
+    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8)) +
+    theme(plot.margin=unit(c(-0.25,0.1,0,0), "cm"))+
+    coord_flip()
 B
@@
     "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
-    "percep" = "range")) +
+    "percep" = "r", "density"="d")) +
     ylab("Mean Decrease in Accuracy (%IncMSE)") +
+    theme_bw()+
     ggtitle("(C)") + #" Variable Importance for Epidemic \nDuration|Success") +
-    theme(axis.title = element_text(size=10),title=element_text(face="bold", size=10))+
-    coord_flip()+
-    theme_bw()
+
+      theme(axis.text=element_text(size=6), plot.title = element_text(size = 8), axis.title.x=element_text(size=7)) +
+    theme(plot.margin=unit(c(-0.25,0.1,0,0), "cm"))+
+    coord_flip()
 C
 
-#setwd()
-tiff("Fig2_RF.tif", height =16 , width =8.7, units = "cm", compression = "lzw", res = 300)
+setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
+tiff("Figure1_RF.tiff", height =10 , width =8.7, units = "cm", compression = "lzw", res = 1200)
 multiplot(A, B, C, cols=1)
@@
 
-## Figure 3
+##Figure 1- vertical
+Random forest variable importance results
+```{r}
+library(randomForest)
+setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")
+
+#Load importance values (not scaled by SD)
+imp_logit<-read.csv("imp_logit.csv")
+imp_logitprev<-read.csv("logit_imp_maxprev.csv")
+imp_logitdur<-read.csv("logit_imp_dur.csv")
+
+logitSD<-read.csv("imp_logitSD.csv")
+logitprevSD<-read.csv("imp_logitprevSD.csv")
+logitdurSD<-read.csv("imp_logitdurSD.csv")
+
+imp_logit$SD<-logitSD$x
+imp_logitprev$SD<-logitprevSD$x
+imp_logitdur$SD<-logitdurSD$x
+
+#Order according to increasing node purity
+imp_logit<-imp_logit[order(imp_logit$IncNodePurity),]
+imp_logitdur<-imp_logitdur[order(imp_logitdur$IncNodePurity),] 
+imp_logitprev<-imp_logitprev[order(imp_logitprev$IncNodePurity),]
+
+#Remove infection probability (dummy variable--not varied in factorial design)
+imp_logit<- imp_logit[!(imp_logit$X=="inf_prob"),]
+imp_logitdur<- imp_logitdur[!(imp_logitdur$X=="inf_prob"),]
+imp_logitprev<- imp_logitprev[!(imp_logitprev$X=="inf_prob"),]
+
+#In ggplot
+imp_logit<-imp_logit[order(imp_logit$X.IncMSE),] #order according to %increase in MSE
+
+#imp_logit$SD<-rep(0.005, times=nrow(imp_logit))
+A<-ggplot(imp_logit, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
+    geom_bar(position=position_dodge(), stat="identity",
+             colour="black", # Use black outlines,
+             size=.3) +      # Thinner lines
+    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
+    #               size=.3,    # Thinner lines
+    #               width=.2,
+    #               position=position_dodge(.9)) +
+    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
+    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
+    "percep" = "r", "density"="d")) +
+     ylab("Mean Decrease in Accuracy (%IncMSE)") +
+    #ylab("")+
+    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
+    #ggtitle("(A)") + #" Variable Importance for Epidemic \nSuccess") +
+    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8), axis.title=element_text(size=6)) 
+    #theme(plot.margin=unit(c(0.1,0.1,0,0), "cm"))
+    # theme_bw(axis.text=element_text(size=14),    axis.title=element_text(size=14,face="bold"), plot.title = element_text(size = 40))
+A
+
+#imp_logitprev$SD<-rep(0.0000001, times=nrow(imp_logitprev))
+B<-ggplot(imp_logitprev, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
+    geom_bar(position=position_dodge(), stat="identity",
+             colour="black", # Use black outlines,
+             size=.3) +      # Thinner lines
+    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
+    #               size=.3,    # Thinner lines
+    #               width=.2,
+    #               position=position_dodge(.9)) +
+    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
+    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
+    "percep" = "r", "density"="d")) +
+     #ylab("Mean Decrease in Accuracy (%IncMSE)") +
+    ylab(NULL)+
+    theme_bw()+ theme(plot.margin = unit(c(0.25, 0, 0, 0), "cm"))+
+    #ggtitle("(B)") + #" Variable Importance for Maximum \nPrevalence|Success") +
+    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8))
+    #theme(plot.margin=unit(c(-0.25,0.1,0,0), "cm"))
+    #coord_flip()
+B
+
+#imp_logitdur$SD<-rep(100, times=nrow(imp_logitdur))
+C<-ggplot(imp_logitdur, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
+    geom_bar(position=position_dodge(), stat="identity",
+             colour="black", # Use black outlines,
+             size=.3) +      # Thinner lines
+    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
+    #               size=.3,    # Thinner lines
+    #               width=.2,
+    #               position=position_dodge(.9)) +
+    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
+    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
+    "percep" = "r", "density"="d")) +
+    #ylab("Mean Decrease in Accuracy (%IncMSE)") +
+    ylab(NULL)+
+    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
+    #ggtitle("(C)") + #" Variable Importance for Epidemic \nDuration|Success") +
+
+      theme(axis.text=element_text(size=6), plot.title = element_text(size = 8), axis.title.x=element_text(size=7)) 
+    #theme(plot.margin=unit(c(-0.25,0.1,0,0), "cm"))
+    #coord_flip()
+C
+
+prow <- plot_grid(A, B, C,
+           align = 'vh',
+           labels = c("(A)", "(B)", "(C)"),
+           hjust = -0.75,
+           ncol = 3, label_size=7
+           )
+#paxis <- axis_canvas(prow, axis = "y") 
+#ggdraw(insert_yaxis_grob(prow, paxis, grid::unit(.25, "null")))
+
+setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
+tiff("Figure1_RFvert.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
+#multiplot(A, B, C, cols=3)
+prow
+dev.off()
+
+```
+
+##Figure 2
 Box plots rec rate vs. density
 ```{r}
-#setwd()
+setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
 sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks
+colnames(sub_data)[3]<-"d" #rename density as "d"
+colnames(sub_data)[11]<-"r" #rename perceptual range as "r"
+#means <- aggregate(max_prevalence ~ density+ rec_rate +percep, sub_data, mean)
+#means_dur <- aggregate(duration ~ density+ rec_rate +percep, sub_data, mean)
 
@@
 #gg<- gg+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
-gg<-gg+ geom_boxplot()+ facet_grid(percep ~ density, scales= "free_x", labeller=label_both)
-gg<- gg+ labs(x = expression(Recovery~rate~(gamma)), y = "Maximum prevalence",title="(A)")
-gg<- gg+ theme(axis.title = element_text(size=16),title=element_text(face="bold", size=16))
-gg<- gg + theme(axis.text.x = element_text(vjust=0.5, size=16))
-gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-gg<- gg + theme(strip.text = element_text(vjust=0.5, size=14)) 
+gg<-gg+ geom_boxplot()+ facet_grid(r ~ d, scales= "free_x", labeller=label_value)
+gg<- gg+ labs(x = expression(Recovery~rate~(gamma)), y = "Maximum prevalence") #,title="(A)")
+#gg<- gg+ theme(axis.title.x = element_text(face="bold", size=10),title=element_text(face="bold", size=10))
+gg<- gg + theme(axis.text = element_text(size=6))
+gg<- gg + theme(axis.text.x =element_text(vjust= 0, angle=-90))
+gg<- gg + theme(axis.title = element_text(vjust=0.5, size=7))
+gg<- gg + theme(strip.text = element_text(vjust=0.5, size=6))
+gg<- gg + theme(plot.title = element_text(size = 7))
+gg<- gg + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
+#gg<-gg + geom_text(data = means , aes(label = duration, y = duration + 0.08))
+
 gg
@@
 #hh<- hh+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
-hh<-hh+ geom_boxplot()+ facet_grid(percep ~ density, scales= "free_x", labeller=label_both)
-hh<- hh+ labs(fill= "density", x = expression(Recovery~rate~(gamma)), y = "Duration", title="(B)")
-hh<- hh+ theme(axis.title = element_text(face="bold", size=16), title=element_text(face="bold", size=16))
-hh<- hh + theme(axis.text.x = element_text(vjust=0.5, size=16))
-hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-hh<- hh + theme(strip.text = element_text(vjust=0.5, size=14)) 
+hh<-hh+ geom_boxplot()+ facet_grid(r ~ d, scales= "free_x", labeller=label_value)
+hh<- hh+ labs(fill= "density", x = expression(Recovery~rate~(gamma)), y = "Duration") #, title="(B)")
+#hh<- hh+ theme(axis.title = element_text(size=10), title=element_text(face="bold", size=10))
+hh<- hh + theme(axis.text = element_text(vjust=0.5, size=6))
+hh<- hh + theme(axis.text.x =element_text(vjust= 0, angle=-90))
+hh<- hh + theme(axis.title = element_text(vjust=0.5, size=7))
+hh<- hh + theme(plot.title = element_text(size=7)) 
+hh<- hh + theme(strip.text = element_text(vjust=0.5, size=6)) 
+hh<- hh + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
 hh
@@
 
-tiff("Figure3.tif", height = 14, width = 8.7, units = "in", compression = "lzw", res = 300)
-multiplot(gg,hh, cols=1)
+prow <- plot_grid(gg + theme(legend.position="none"),
+            hh + theme(legend.position="none"),
+           align = 'vh',
+           labels = c("(A)", "(B)"),
+           hjust = -1,
+           ncol = 2, label_size=7
+           )
+
+tiff("Figure2.tiff", height = 7, width = 8.7, units = "cm", compression = "lzw", res = 1200)
+prow
+#multiplot(gg,hh, cols=2)
 dev.off()
@@
 
-## Figure 4
-```{r}
-#percep=3, rec_rate=0.2, density=0.5
-p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
-ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=max_prevalence, fill=as.factor(beta2)))
-ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
-ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
-ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
-ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
-ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
-ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
-ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
-ii
-
-jj<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=duration, fill=as.factor(beta2)))
-jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
-jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(B)", fill= expression(beta[2]))
-jj<- jj+ theme(axis.title = element_text(face="bold", size=20))
-jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
-jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-jj<- jj + theme(strip.text = element_text(vjust=0.5, size=16)) 
-jj<- jj + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
-jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
-jj
-
-tiff("Fig4.tif", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
-multiplot(ii,jj, cols=1)
-dev.off()
-```
-
-## Figure 4 (log version)
-```{r}
-#percep=3, rec_rate=0.2, density=0.5
-p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
-ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(max_prevalence), fill=as.factor(beta2)))
-ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
-ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Maximum prevalence)", title="(A)", fill= expression(beta[2]))
-ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
-ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
-ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
-ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
-ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
-ii
-
-jj<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(duration), fill=as.factor(beta2)))
-jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
-jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Duration)", title="(B)", fill= expression(beta[2]))
-jj<- jj+ theme(axis.title = element_text(face="bold", size=20))
-jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
-jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-jj<- jj + theme(strip.text = element_text(vjust=0.5, size=16)) 
-jj<- jj + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
-jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
-jj
-
-tiff("Fig4_log.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
-multiplot(ii,jj, cols=1)
-dev.off()
-```
-
-## Figure 5
+##Figure 3
 ```{r}
@@
 ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
-ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
-ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
-ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
-ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
-ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
+ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", fill= expression(beta[2]))
+ii<- ii+ theme(plot.title = element_text(size=7))
+ii<- ii+ theme(axis.title = element_text(size=6))
+ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=6))
 ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
+ii<- ii + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
 ii
@@
 jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
-jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(B)", fill= expression(beta[2]))
-jj<- jj+ theme(axis.title = element_text(face="bold", size=20))
-jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
-jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-jj<- jj + theme(strip.text = element_text(vjust=0.5, size=16)) 
-jj<- jj + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
+jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Duration", fill= expression(beta[2]))
+jj<- jj+ theme(plot.title = element_text(size=7))
+jj<- jj+ theme(axis.title = element_text(size=6))
+jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
+jj<- jj + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
 jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
+jj<- jj + theme(plot.margin=unit(c(-0.1,0.1,0,0.1), "cm"))
 jj
 
-tiff("Fig5.tif", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
-multiplot(ii,jj, cols=1)
+prow <- plot_grid( ii + theme(legend.position="none"),
+            jj + theme(legend.position="none"),
+           align = 'vh',
+           labels = c("(A)", "(B)"),
+           hjust = -1,
+           nrow = 2, label_size=7
+           )
+
+legend_b <- get_legend(ii + theme(legend.position="bottom"))
+
+p <- plot_grid( prow, legend_b, ncol = 1, rel_heights = c(1, .02))
+p
+
+tiff("Figure3test.tiff", height = 22.7, width = 17.8, units = "cm", compression = "lzw", res = 900)
+#multiplot(ii,jj, cols=1)
+p
 dev.off()
@@
 
-## Figure 5 (log version)
-```{r}
-#percep=3, rec_rate=0.1, density=0.5
-p3r0.1d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.1 & merged_data$density==0.5),]
-ii<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=log(max_prevalence),fill=as.factor(beta2)))
-ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
-ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Maximum prevalence)", title="(A)", fill= expression(beta[2]))
-ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
-ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
-ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
-ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
-ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
-ii
-
-jj<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=log(duration), fill=as.factor(beta2)))
-jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
-jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Duration)", title="(B)", fill= expression(beta[2]))
-jj<- jj+ theme(axis.title = element_text(face="bold", size=20))
-jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
-jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-jj<- jj + theme(strip.text = element_text(vjust=0.5, size=16)) 
-jj<- jj + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
-jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
-jj
-
-tiff("Fig5_log.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
-multiplot(ii,jj, cols=1)
-dev.off()
-```
-
-## Figure 6
-Comparing effects on landscape structure for a single RSF(\beta_1=6, \beta_2=2, \beta_3=-0.5) for different densities, perceptual distances, and recovery rates.
-```{r}
-sub_data<-merged_data[which(merged_data$max_I>1),]
-
-RSF620.5<-sub_data[which(sub_data$betas=="6 2 -0.5"),]
-RSF620.5_rec0.1<-RSF620.5[which(RSF620.5$rec_rate==0.1),]
-RSF620.5_rec0.2<-RSF620.5[which(RSF620.5$rec_rate==0.2),]
-RSF620.5_rec0.4<-RSF620.5[which(RSF620.5$rec_rate==0.4),]
+##Figure 4
+Comparing effects on landscape structure for select RSFs holding density, recovery rate and perceptual range constant.
+```{r}
+#sub_data<-merged_data[which(merged_data$max_I>1),]
+sub_data<-merged_data
+
+betas<-sub_data[which(sub_data$betas==c("3 0 0", "3 0 -1", "3 2 -0.5")),]
+betas<-betas[which(betas$rec_rate==0.1 & betas$percep==3 & betas$density==0.5),]
 
 #Individual plots of RSF box plot max prevalence and duration
-gg<- ggplot(data=RSF620.5_rec0.2, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
-gg<- gg+ geom_boxplot(stat="boxplot", position=position_dodge())
-gg<- gg + facet_grid(percep ~ density)
-# gg<-gg +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
-gg<- gg+ labs(title="(A)", x = "Landscape structure", y = "Mean maximum \n prevalence")
-#gg<-gg +theme_grey()
-#gg<-gg + theme(plot.title = element_text(hjust = 0.5))
-gg<- gg+ theme(axis.title = element_text(face="bold", size=19))
-gg<- gg + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=16))
-gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-gg<- gg + theme(strip.text = element_text(vjust=0.5, size=16)) 
-#gg <- gg+ theme(legend.position="none")
-#gg<-gg+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
-#gg<-gg+ theme(axis.ticks.x=element_blank())
-#gg<-gg +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
-gg
-
-hh<- ggplot(data=RSF620.5_rec0.2, aes(x=lstructure, y=duration)) #, fill=covariation)
-hh<- hh+ geom_boxplot(stat="boxplot", position=position_dodge())
-hh<- hh + facet_grid(percep ~ density)
-# hh<-hh +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
-hh<- hh+ labs(title="(B)", x = "Landscape structure", y = "Duration")
-#hh<-hh +theme_grey()
-#hh<-hh + theme(plot.title = element_text(hjust = 0.5))
-hh<- hh+ theme(axis.title = element_text(face="bold", size=19))
-hh<- hh + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=16))
-hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-hh<- hh + theme(strip.text = element_text(vjust=0.5, size=16)) 
-#hh <- hh+ theme(legend.position="none")
-#hh<-hh+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
-#hh<-hh+ theme(axis.ticks.x=element_blank())
-#hh<-hh +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
-hh
-
-#Individual plots of RSF box plot max prevalence and duration
-ii<- ggplot(data=RSF620.5_rec0.1, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
+ii<- ggplot(data=betas, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
 ii<- ii+ geom_boxplot(stat="boxplot", position=position_dodge())
-ii<- ii + facet_grid(percep ~ density)
+ii<- ii + facet_grid(betas ~.)
 # ii<-ii +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
-ii<- ii+ labs(title="(C)", x = "Landscape structure", y = "Mean maximum \n prevalence")
+ii<- ii+ labs(x = "Landscape structure", y = "Maximum \n prevalence")
 #ii<-ii +theme_grey()
 #ii<-ii + theme(plot.title = element_text(hjust = 0.5))
-ii<- ii+ theme(axis.title = element_text(face="bold", size=19))
-ii<- ii + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=16))
-ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
+ii<- ii+ theme(plot.title = element_text(size=7))
+ii<- ii+ theme(axis.title = element_text(size=6))
+ii<- ii + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
 #ii <- ii+ theme(legend.position="none")
@@
 
-jj<- ggplot(data=RSF620.5_rec0.1, aes(x=lstructure, y=duration)) #, fill=covariation)
+#Individual plots of RSF box plot max prevalence and duration
+jj<- ggplot(data=betas, aes(x=lstructure, y=duration)) #, fill=covariation)
 jj<- jj+ geom_boxplot(stat="boxplot", position=position_dodge())
-jj<- jj + facet_grid(percep ~ density)
+jj<- jj + facet_grid(betas ~.)
 # jj<-jj +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
-jj<- jj+ labs(title="(D)", x = "Landscape structure", y = "Duration")
+jj<- jj+ labs(x = "Landscape structure", y = "Duration")
 #jj<-jj +theme_grey()
 #jj<-jj + theme(plot.title = element_text(hjust = 0.5))
-jj<- jj+ theme(axis.title = element_text(face="bold", size=19))
-jj<- jj + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=16))
-jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-jj<- jj + theme(strip.text = element_text(vjust=0.5, size=16)) 
+jj<- jj+ theme(plot.title = element_text(size=7))
+jj<- jj+ theme(axis.title = element_text(size=6))
+jj<- jj + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
 #jj <- jj+ theme(legend.position="none")
@@
 
-tiff("Figure6.tif", height = 12, width = 12, units = "in", compression = "lzw", res = 300)
-multiplot(gg,hh,ii,jj, cols=2)
+prow <- plot_grid(ii, jj,
+           align = 'vh',
+           labels = c("(A)", "(B)"),
+           hjust = -1,
+           ncol = 1, label_size=7
+           )
+
+tiff("Figure4.tiff", height = 12, width = 8.7, units = "cm", compression = "lzw", res = 1200)
+#multiplot(ii,jj, cols=1)
+prow
 dev.off()
@@
 
-## Supplementary Figure 2
-Box plot of percep vs. rec rate vs. density
+##Supplementary Figure S1
+Box plot of percep vs. rec rate vs. density for every RSF combination
 ```{r}
 sub_data<-merged_data[which(merged_data$max_I>1),]
+sub_data25<-sub_data[which(sub_data$density==0.25),]
+sub_data50<-sub_data[which(sub_data$density==0.5),]
 
 #tiff("boxplot_prev.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
-gg<- ggplot(data=merged_data, aes(x=betas, y=max_prevalence, fill=as.factor(density)))
+gg<- ggplot(data=sub_data25, aes(x=betas, y=max_prevalence))#, fill=as.factor(density)))
 #gg<- gg+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
 gg<-gg+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
-gg<- gg+ labs(fill= "density", x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence",title="(A)")
+gg<- gg+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence",title="(A)")
 gg<- gg+ theme(axis.title = element_text(face="bold", size=20))
@@
 #tiff("boxplot_dur.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
-hh<- ggplot(data=merged_data, aes(x=betas, y=duration, fill=as.factor(density)))
+hh<- ggplot(data=sub_data25, aes(x=betas, y=duration))#, fill=as.factor(density)))
 #hh<- hh+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
 hh<-hh+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
-hh<- hh+ labs(fill= "density", x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(B)")
+hh<- hh+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(B)")
 hh<- hh+ theme(axis.title = element_text(face="bold", size=20))
@@
 
-tiff("FigureS2.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
-multiplot(gg,hh, cols=1)
+#tiff("boxplot_prev.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
+ii<- ggplot(data=sub_data50, aes(x=betas, y=max_prevalence))#, fill=as.factor(density)))
+#gg<- gg+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
+ii<-ii+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
+ii<- ii+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence",title="(C)")
+ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
+ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=14)) 
+ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
+ii
+#dev.off()
+
+#tiff("boxplot_dur.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
+jj<- ggplot(data=sub_data50, aes(x=betas, y=duration))#, fill=as.factor(density)))
+#jj<- jj+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
+jj<-jj+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
+jj<- jj+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(D)")
+jj<- jj+ theme(axis.title = element_text(face="bold", size=20))
+jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=14)) 
+jj<- jj + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
+jj
+
+tiff("FigureS2.tiff", height = 20, width = 14, units = "in", compression = "lzw", res = 300)
+multiplot(gg,hh,ii,jj, cols=1)
 dev.off()
@@
 
-## Supplementary Figure 3 (Heat map)
-Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing rec rates 0.1 and 0.2
-```{r}
-r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.5),]
+##Supplementary Figure S2 (Heat maps, density=0.25)
+Heatmap of max prevelance and mean duration for conspecific density=0.25 and comparing recovery rates of 0.1, 0.2, and 0.4
+```{r}
+r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.25),]
 
@@
 gg <- gg + facet_grid(percep ~ betas)
-gg<- gg+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title= "(B)")
+gg<- gg+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title= "(D)")
 gg<- gg+ theme(axis.title = element_text(face="bold", size=24))
@@
 hh <- hh + facet_grid(percep ~ betas)
-hh<- hh+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(A)")
+hh<- hh+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(C)")
 hh<- hh+ theme(axis.title = element_text(face="bold", size=24))
@@
 
+r1<-merged_data[which(merged_data$rec_rate==0.1 & merged_data$density==0.25),]
+sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r1, FUN=mean)
+ii <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
+ii <- ii + geom_tile(color="white", size=0.1)
+ii <- ii + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
+ii <- ii + coord_equal()
+ii <- ii + facet_grid(percep ~ betas)
+ii<- ii+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(A)")
+ii<- ii+ theme(axis.title = element_text(face="bold", size=24))
+ii<- ii + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=18)) 
+ii<- ii + theme(strip.text.x = element_text(angle = 90))
+ii<- ii + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+ii
+
+sdf <- summaryBy(duration~ H + betas +p+ percep, data=r1, FUN=mean)
+jj <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
+jj <- jj + geom_tile(color="white", size=0.1)
+jj <- jj + scale_fill_viridis(name="Duration")
+jj <- jj + coord_equal()
+jj <- jj + facet_grid(percep ~ betas)
+jj<- jj+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(B)")
+jj<- jj+ theme(axis.title = element_text(face="bold", size=24))
+jj<- jj + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=18)) 
+jj<- jj + theme(strip.text.x = element_text(angle = 90))
+jj<- jj + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+jj
+
+r4<-merged_data[which(merged_data$rec_rate==0.4 & merged_data$density==0.25),]
+sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r4, FUN=mean)
+kk <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
+kk <- kk + geom_tile(color="white", size=0.1)
+kk <- kk + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
+kk <- kk + coord_equal()
+kk <- kk + facet_grid(percep ~ betas)
+kk<- kk+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(E)")
+kk<- kk+ theme(axis.title = element_text(face="bold", size=24))
+kk<- kk + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+kk<- kk + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+kk<- kk + theme(strip.text = element_text(vjust=0.5, size=18)) 
+kk<- kk + theme(strip.text.x = element_text(angle = 90))
+kk<- kk + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+kk
+
+sdf <- summaryBy(duration~ H + betas +p+ percep, data=r4, FUN=mean)
+mm <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
+mm <- mm + geom_tile(color="white", size=0.1)
+mm <- mm + scale_fill_viridis(name="Duration")
+mm <- mm + coord_equal()
+mm <- mm + facet_grid(percep ~ betas)
+mm<- mm+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(F)")
+mm<- mm+ theme(axis.title = element_text(face="bold", size=24))
+mm<- mm + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+mm<- mm + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+mm<- mm + theme(strip.text = element_text(vjust=0.5, size=18)) 
+mm<- mm + theme(strip.text.x = element_text(angle = 90))
+mm<- mm + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+mm
+
+tiff("FigureS4_heatmap.tiff", height = 27, width = 14, units = "in", compression = "lzw", res = 300)
+multiplot(ii,jj,hh,gg, kk,mm, cols=1)
+dev.off()
+```
+
+##Supplementary Figure S3 (Heat maps, density=0.5)
+Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing recovery rates of 0.1, 0.2, and 0.4
+```{r}
+r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.5),]
+
+sdf <- summaryBy(duration~ H + betas +p+ percep, data=r2, FUN=mean)
+gg <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
+gg <- gg + geom_tile(color="white", size=0.1)
+gg <- gg + scale_fill_viridis(name="Duration")
+gg <- gg + coord_equal()
+gg <- gg + facet_grid(percep ~ betas)
+gg<- gg+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title= "(D)")
+gg<- gg+ theme(axis.title = element_text(face="bold", size=24))
+gg<- gg + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+gg<- gg + theme(strip.text = element_text(vjust=0.5, size=18)) 
+gg<- gg + theme(strip.text.x = element_text(angle = 90))
+gg<- gg + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+gg
+
+sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r2, FUN=mean)
+hh <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
+hh <- hh + geom_tile(color="white", size=0.1)
+hh <- hh + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
+hh <- hh + coord_equal()
+hh <- hh + facet_grid(percep ~ betas)
+hh<- hh+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(C)")
+hh<- hh+ theme(axis.title = element_text(face="bold", size=24))
+hh<- hh + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+hh<- hh + theme(strip.text = element_text(vjust=0.5, size=18)) 
+hh<- hh + theme(strip.text.x = element_text(angle = 90))
+hh<- hh + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+hh
+
 r1<-merged_data[which(merged_data$rec_rate==0.1 & merged_data$density==0.5),]
@@
 ii <- ii + facet_grid(percep ~ betas)
-ii<- ii+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(C)")
+ii<- ii+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(A)")
 ii<- ii+ theme(axis.title = element_text(face="bold", size=24))
@@
 jj <- jj + facet_grid(percep ~ betas)
-jj<- jj+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(D)")
+jj<- jj+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(B)")
 jj<- jj+ theme(axis.title = element_text(face="bold", size=24))
@@
 
-tiff("FigureS3_heatmap.tiff", height = 18, width = 14, units = "in", compression = "lzw", res = 300)
-multiplot(hh,gg, ii,jj, cols=1)
+r4<-merged_data[which(merged_data$rec_rate==0.4 & merged_data$density==0.5),]
+sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r4, FUN=mean)
+kk <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
+kk <- kk + geom_tile(color="white", size=0.1)
+kk <- kk + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
+kk <- kk + coord_equal()
+kk <- kk + facet_grid(percep ~ betas)
+kk<- kk+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(E)")
+kk<- kk+ theme(axis.title = element_text(face="bold", size=24))
+kk<- kk + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+kk<- kk + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+kk<- kk + theme(strip.text = element_text(vjust=0.5, size=18)) 
+kk<- kk + theme(strip.text.x = element_text(angle = 90))
+kk<- kk + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+kk
+
+sdf <- summaryBy(duration~ H + betas +p+ percep, data=r4, FUN=mean)
+mm <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
+mm <- mm + geom_tile(color="white", size=0.1)
+mm <- mm + scale_fill_viridis(name="Duration")
+mm <- mm + coord_equal()
+mm <- mm + facet_grid(percep ~ betas)
+mm<- mm+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(F)")
+mm<- mm+ theme(axis.title = element_text(face="bold", size=24))
+mm<- mm + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+mm<- mm + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+mm<- mm + theme(strip.text = element_text(vjust=0.5, size=18)) 
+mm<- mm + theme(strip.text.x = element_text(angle = 90))
+mm<- mm + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+mm
+
+tiff("FigureS3_heatmap.tiff", height = 27, width = 14, units = "in", compression = "lzw", res = 300)
+multiplot(ii,jj,hh,gg, kk,mm, cols=1)
 dev.off()
@@
 
-## Supplementary Figure 1 
-Calibrate beta1/beta2/beta3
+##Figure S4
+```{r}
+#percep=3, rec_rate=0.2, density=0.5
+p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
+ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=max_prevalence, fill=as.factor(beta2)))
+ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
+ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
+ii<- ii+ theme(plot.title = element_text(size=7))
+ii<- ii+ theme(axis.title = element_text(size=6))
+ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
+ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
+ii<- ii + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
+ii
+
+jj<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=duration, fill=as.factor(beta2)))
+jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
+jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(B)", fill= expression(beta[2]))
+jj<- jj+ theme(plot.title = element_text(size=7))
+jj<- jj+ theme(axis.title = element_text(size=6))
+jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
+jj<- jj + theme(legend.text = element_text(vjust=0.5, size=8), legend.title=element_text(vjust=0.5, size=7))
+jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
+jj<- jj + theme(plot.margin=unit(c(-0.1,0.1,0,0.1), "cm"))
+
+jj
+
+tiff("FigureS4.tiff", height = 22.5, width = 17.8, units = "cm", compression = "lzw", res = 900)
+multiplot(ii,jj, cols=1)
+dev.off()
+```
+
+##Figure S4 (log version)
+```{r}
+#percep=3, rec_rate=0.2, density=0.5
+p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
+ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(max_prevalence), fill=as.factor(beta2)))
+ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
+ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Maximum prevalence)", title="(A)", fill= expression(beta[2]))
+ii<- ii+ theme(plot.title = element_text(size=7))
+ii<- ii+ theme(axis.title = element_text(size=6))
+ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
+ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
+jj<- jj + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
+ii
+
+jj<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(duration), fill=as.factor(beta2)))
+jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
+jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Duration)", title="(B)", fill= expression(beta[2]))
+jj<- jj+ theme(plot.title = element_text(size=7))
+jj<- jj+ theme(axis.title = element_text(size=6))
+jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
+jj<- jj + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
+jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
+jj<- jj + theme(plot.margin=unit(c(-0.1,0.1,0,0.1), "cm"))
+jj
+
+tiff("FigS4_log.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
+multiplot(ii,jj, cols=1)
+dev.off()
+```
+
+##Fig. S5
+Comparing effects on landscape structure for a single RSF(\beta_1=6, \beta_2=2, \beta_3=-0.5) for different densities, perceptual distances, and recovery rates.
+```{r}
+#sub_data<-merged_data[which(merged_data$max_I>1),]
+sub_data<-merged_data
+
+RSF620.5<-sub_data[which(sub_data$betas=="6 2 -0.5"),]
+RSF620.5_rec0.1<-RSF620.5[which(RSF620.5$rec_rate==0.1),]
+RSF620.5_rec0.2<-RSF620.5[which(RSF620.5$rec_rate==0.2),]
+RSF620.5_rec0.4<-RSF620.5[which(RSF620.5$rec_rate==0.4),]
+
+#Individual plots of RSF box plot max prevalence and duration
+gg<- ggplot(data=RSF620.5_rec0.2, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
+gg<- gg+ geom_boxplot(stat="boxplot", position=position_dodge())
+gg<- gg + facet_grid(percep ~ density)
+# gg<-gg +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
+gg<- gg+ labs(title="(C)", x = "Landscape structure", y = "Mean maximum \n prevalence")
+#gg<-gg +theme_grey()
+#gg<-gg + theme(plot.title = element_text(hjust = 0.5))
+gg<- gg+ theme(plot.title = element_text(size=7))
+gg<- gg+ theme(axis.title = element_text(size=6))
+gg<- gg + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+gg<- gg + theme(strip.text = element_text(vjust=0.5, size=6)) 
+#gg <- gg+ theme(legend.position="none")
+#gg<-gg+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
+#gg<-gg+ theme(axis.ticks.x=element_blank())
+#gg<-gg +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
+gg
+
+hh<- ggplot(data=RSF620.5_rec0.2, aes(x=lstructure, y=duration)) #, fill=covariation)
+hh<- hh+ geom_boxplot(stat="boxplot", position=position_dodge())
+hh<- hh + facet_grid(percep ~ density)
+# hh<-hh +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
+hh<- hh+ labs(title="(D)", x = "Landscape structure", y = "Duration")
+#hh<-hh +theme_grey()
+#hh<-hh + theme(plot.title = element_text(hjust = 0.5))
+hh<- hh+ theme(plot.title = element_text(size=7))
+hh<- hh+ theme(axis.title = element_text(size=6))
+hh<- hh + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+hh<- hh + theme(strip.text = element_text(vjust=0.5, size=6)) 
+#hh <- hh+ theme(legend.position="none")
+#hh<-hh+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
+#hh<-hh+ theme(axis.ticks.x=element_blank())
+#hh<-hh +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
+hh
+
+#Individual plots of RSF box plot max prevalence and duration
+ii<- ggplot(data=RSF620.5_rec0.1, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
+ii<- ii+ geom_boxplot(stat="boxplot", position=position_dodge())
+ii<- ii + facet_grid(percep ~ density)
+# ii<-ii +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
+ii<- ii+ labs(x = "Landscape structure", y = "Mean maximum \n prevalence", title="(E)")
+#ii<-ii +theme_grey()
+#ii<-ii + theme(plot.title = element_text(hjust = 0.5))
+ii<- ii+ theme(plot.title = element_text(size=7))
+ii<- ii+ theme(axis.title = element_text(size=6))
+ii<- ii + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
+#ii <- ii+ theme(legend.position="none")
+#ii<-ii+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
+#ii<-ii+ theme(axis.ticks.x=element_blank())
+#ii<-ii +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
+ii
+
+jj<- ggplot(data=RSF620.5_rec0.1, aes(x=lstructure, y=duration)) #, fill=covariation)
+jj<- jj+ geom_boxplot(stat="boxplot", position=position_dodge())
+jj<- jj + facet_grid(percep ~ density)
+# jj<-jj +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
+jj<- jj+ labs(x = "Landscape structure", y = "Duration", title="(F)")
+#jj<-jj +theme_grey()
+#jj<-jj + theme(plot.title = element_text(hjust = 0.5))
+jj<- jj+ theme(plot.title = element_text(size=7))
+jj<- jj+ theme(axis.title = element_text(size=6))
+jj<- jj + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
+#jj <- jj+ theme(legend.position="none")
+#jj<-jj+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
+#jj<-jj+ theme(axis.ticks.x=element_blank())
+#jj<-jj +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
+jj
+
+#Individual plots of RSF box plot max prevalence and duration
+kk<- ggplot(data=RSF620.5_rec0.4, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
+kk<- kk+ geom_boxplot(stat="boxplot", position=position_dodge())
+kk<- kk + facet_grid(percep ~ density)
+# kk<-kk +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
+kk<- kk+ labs(title="(A)", x = "Landscape structure", y = "Mean maximum \n prevalence")
+#kk<-kk +theme_grey()
+#kk<-kk + theme(plot.title = element_text(hjust = 0.5))
+kk<- kk+ theme(plot.title = element_text(size=7))
+kk<- kk+ theme(axis.title = element_text(size=6))
+kk<- kk + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+kk<- kk + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+kk<- kk + theme(strip.text = element_text(vjust=0.5, size=6)) 
+#kk <- kk+ theme(legend.position="none")
+#kk<-kk+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
+#kk<-kk+ theme(axis.ticks.x=element_blank())
+#kk<-kk +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
+kk
+
+mm<- ggplot(data=RSF620.5_rec0.4, aes(x=lstructure, y=duration)) #, fill=covariation)
+mm<- mm+ geom_boxplot(stat="boxplot", position=position_dodge())
+mm<- mm + facet_grid(percep ~ density)
+# mm<-mm +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
+mm<- mm+ labs(title="(B)", x = "Landscape structure", y = "Duration")
+#mm<-mm +theme_grey()
+#mm<-mm + theme(plot.title = element_text(hjust = 0.5))
+mm<- mm+ theme(plot.title = element_text(size=7))
+mm<- mm+ theme(axis.title = element_text(size=6))
+mm<- mm + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+mm<- mm + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+mm<- mm + theme(strip.text = element_text(vjust=0.5, size=6)) 
+#mm <- mm+ theme(legend.position="none")
+#mm<-mm+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
+#mm<-mm+ theme(axis.ticks.x=element_blank())
+#mm<-mm +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
+mm
+
+tiff("FigureS5.tiff", height = 22, width = 17.8, units = "cm", compression = "lzw", res = 1200)
+multiplot(kk,mm,gg,hh,ii,jj, cols=2)
+dev.off()
+
+```
+
+##Supplementary Figure S6
+See SimpleSIR.Rmd
+
+##Supplementary Figure S7: Calibrating beta2/beta3 for RSF
 ```{r}
@@
 ```
+
+##Figure S8
+Representation of neutral landscapes used for simulation studies
+```{r}
+#' Create neutral landscape maps
+library(raster)
+
+#' Use standard methods to generate fractal maps. Binary and continuous surfaces may be produced.
+#' 
+#' @param k integer. The extent of the map (2^k+1)^2 pixels
+#' @param h numeric. Level of aggregation in the map.
+#' @param p numeric (0,1). The proportion of map in habitat=1
+#' @param binary logical. If TRUE, a 0/1 categorical landscape is produced.
+#' @author Shannon Pittman, James Forester, modified by Lauren White
+#' @export
+#' @example examples/neutral.landscape_example.R
+fracland_mod <- function(k, h, p, binary = TRUE) {
+  ## Function for creating neutral landscapes Shannon Pittman University of Minnesota May, 2013 k = the extent of the map (2^k+1)^2 pixels h =
+  ## how clumped the map should be (ranging from ?? to ??) -- weird behavior at higher values p = proportion of map in habitat 1 binary =
+  ## plotflag == if TRUE will plot a filled contour version of the matrix
+
+  ## function call: testmap=land(6,1,.5,FALSE,TRUE)
+  A <- 2^k + 1  # Scalar-determines length of landscape matrix
+
+  #Right now, as written (1-p) represents the amount of habitat listed as "1"
+  B <- matrix(0, A, A)  # Creates landscape matrix
+
+  B[1, 1] <- 0
+  B[1, A] <- 0
+  B[A, 1] <- 0
+  B[A, A] <- 0
+
+  iter <- 1
+  for (iter in 1:k) {
+    scalef <- (0.5 + (1 - h)/2)^(iter)
+
+    d <- 2^(k - iter)
+
+    # ALL SQUARE STEPS#
+    for (i in seq(d + 1, A - d, 2 * d)) {
+      for (j in seq(d + 1, A - d, 2 * d)) {
+        B[i, j] <- mean(c(B[i - d, j - d], B[i - d, j + d], B[i + d, j - d], B[i + d, j + d])) + scalef * rnorm(n = 1)
+      }
+    }
+
+    # OUTSIDE DIAMOND STEP#
+    for (j in seq(d + 1, A - d, 2 * d)) {
+      B[1, j] <- mean(c(B[1, j - d], B[1, j + d], B[1 + d, j])) + scalef * rnorm(n = 1)
+      B[A, j] <- mean(c(B[A, j - d], B[A, j + d], B[A - d, j])) + scalef * rnorm(n = 1)
+    }
+
+    for (i in seq(d + 1, A - d, 2 * d)) {
+      B[i, 1] <- mean(c(B[i - d, 1], B[i + d, 1], B[i, 1 + d])) + scalef * rnorm(n = 1)
+      B[i, A] <- mean(c(B[i - d, A], B[i + d, A], B[i, A - d])) + scalef * rnorm(n = 1)
+    }
+
+    # INSIDE DIAMOND STEP#
+    if (2 * d + 1 <= A - 2 * d) {
+      for (i in seq(d + 1, A - d, 2 * d)) {
+        for (j in seq(2 * d + 1, A - 2 * d, 2 * d)) {
+          B[i, j] <- mean(c(B[i - d, j], B[i + d, j], B[i, j - d], B[i, j + d])) + scalef * rnorm(n = 1)
+        }
+      }
+
+      for (i in seq(2 * d + 1, A - 2 * d, 2 * d)) {
+        for (j in seq(d + 1, A - d, 2 * d)) {
+          B[i, j] <- mean(c(B[i - d, j], B[i + d, j], B[i, j - d], B[i, j + d])) + scalef * rnorm(n = 1)
+        }
+      }
+    }
+
+    iter <- iter + 1
+  }
+
+  if (binary == T) {
+    R <- sort(B)
+    PosR <- (1 - p) * length(R)  #larger values become habitat, designated as 1
+    pval <- R[PosR]
+    T1 <- which(B > pval)
+    T2 <- which(B <= pval)
+    B[T1] <- 1  #habitat is 1
+    B[T2] <- 0
+  } 
+  return(B)
+}
+
+landscape<-fracland_mod(k=7, h=0.1, p=0.25)
+map.1 <- raster(landscape)
+one<-spplot(map.1)
+landscape<-fracland_mod(k=7, h=0.1, p=0.5) 
+map.2 <- raster(landscape)
+two<-spplot(map.2)
+landscape<-fracland_mod(k=7, h=0.1, p=0.75)
+map.3 <- raster(landscape)
+three<-spplot(map.3)
+
+landscape<-fracland_mod(k=7, h=0.5, p=0.25) 
+map.4 <- raster(landscape)
+four<-spplot(map.4)
+landscape<-fracland_mod(k=7, h=0.5, p=0.5) 
+map.5 <- raster(landscape)
+five<-spplot(map.5)
+landscape<-fracland_mod(k=7, h=0.5, p=0.75)
+map.6 <- raster(landscape)
+six<-spplot(map.6)
+
+landscape<-fracland_mod(k=7, h=0.9, p=0.25)
+map.7 <- raster(landscape)
+seven<-spplot(map.7)
+landscape<-fracland_mod(k=7, h=0.9, p=0.5)
+map.8 <- raster(landscape)
+eight<-spplot(map.8)
+landscape<-fracland_mod(k=7, h=0.9, p=0.75)
+map.9 <- raster(landscape)
+# nine<-spplot(map.9)
+
+#convert the raster to points for plotting
+H<-rep(0.1, times=length(map.1))
+map.1 <- rasterToPoints(map.1)
+p<-rep(0.25, times=length(map.1))
+df <- data.frame(map.1, H, p)
+
+map.2 <- rasterToPoints(map.2)
+p<-rep(0.5, times=length(map.1))
+df2 <- data.frame(map.2, H, p)
+
+map.3 <- rasterToPoints(map.3)
+p<-rep(0.75, times=length(map.1))
+df3 <- data.frame(map.3, H, p)
+
+H<-rep(0.5, times=length(map.1))
+map.4 <- rasterToPoints(map.4)
+p<-rep(0.25, times=length(map.1))
+df4 <- data.frame(map.4, H, p)
+
+map.5 <- rasterToPoints(map.5)
+p<-rep(0.5, times=length(map.1))
+df5 <- data.frame(map.5, H, p)
+
+map.6 <- rasterToPoints(map.6)
+p<-rep(0.75, times=length(map.1))
+df6 <- data.frame(map.6, H, p)
+
+H<-rep(0.9, times=length(map.1))
+map.7 <- rasterToPoints(map.7)
+p<-rep(0.25, times=length(map.1))
+df7 <- data.frame(map.7, H, p)
+
+map.8 <- rasterToPoints(map.8)
+p<-rep(0.5, times=length(map.1))
+df8 <- data.frame(map.8, H, p)
+
+map.9 <- rasterToPoints(map.9)
+p<-rep(0.75, times=length(map.1))
+df9 <- data.frame(map.9, H, p)
+
+#Make the points a dataframe for ggplot
+
+df <- rbind(df, df2)
+df <- rbind(df, df3)
+df <- rbind(df, df4)
+df <- rbind(df, df5)
+df <- rbind(df, df6)
+df <- rbind(df, df7)
+df <- rbind(df, df8)
+df <- rbind(df, df9)
+
+my_x_title <- expression(paste("Hurst exponent- habitat patchiness (", italic("H"), ")"))
+my_y_title <- expression(paste("Proportion of available habitat (", italic("p"), ")"))
+
+#Now make the map
+tiff("FigureS7_p_vs_H.tif", height = 8.7, width = 8.7, units = "cm", compression = "lzw", res = 900)
+ggplot(data=df, aes(y=y, x=x)) +
+  geom_raster(aes(fill=layer)) +
+    theme_bw() +
+  coord_equal() +
+  facet_grid(p~ H) +
+  #scale_fill_viridis(name="Resource quality")+
+  #scale_fill_continuous(colours=c("#0000FFFF","#FFFFFFFF"))+
+  scale_fill_gradient(low="lightgrey", high="darkgreen", guide=FALSE) +
+  #scale_fill_continuous(guide = FALSE) +
+  labs(y=my_y_title, x=my_x_title)+
+  theme(axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
+  theme(axis.title = element_text(size=10)) +
+  theme(strip.text = element_text(vjust=0.5, size=9))+ 
+  theme(legend.text = element_text(vjust=0.5, size=9), legend.title=element_text(vjust=0.5, size=10))
+dev.off()
+
+```

### 2018-04-09 SimpleSIR.Rmd
Updated figure order and commented code

@@
 
-Deterministic and more simplistic stochastic SIR models for conspecific density vs. rec. rate combinations tested in spatially-explicit model
+Deterministic and more simplistic stochastic SIR models for conspecific density vs. rec. rate combinations tested in spatially-explicit model. Assume homogenous mixing and no landscape structure.
 
 #Load libraries
-
+Load `deSolve` library for evaluating ordinary differntial equations (ODEs).
 ```{r setup}
 library(deSolve)
+library(ggplot2)
+library(cowplot)
 ```
@@
 
+#frequency dependent transmission
 freq_sir <- function(time, state, parameters) {
@@
 
+#density dependent transmission function
 density_sir <- function(time, state, parameters) {
@@
 ## Stochastic SIR Model 
-
+Develop functions to run equivalent stochastic SIR model that assumes density-dependent transmission, homogenous mixing, and operates using a Reed Frost model.
 ```{r}
@@
 
+```
+
+##Run stochastic simulations
+Run simplified SIR model for six combinations of conspecific density and recovery rate tested in spatially explicit model.
+
+```{r}
 # tic=Sys.time()
@@
 ```
-Plot deterministic and stochastic SIR results (assuming equal mixing)
+
+##Plot deterministic and stochastic SIR results (assuming equal mixing)
+Compare/verify output from deterministic ODE and stochastic SIR models
 ```{r}
+setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")
+#set wd to location of stochastic SIR simulation output files
+
 par(mfrow=c(2, 3))
@@
 stoch<-read.csv("k8dens0.25inf0.2rec0.1_infected.csv")
-out <- ode(y = init, func = sir, times = times, parms = c(beta = 0.2, gamma = 0.1))
+out <- ode(y = init, func = density_sir, times = times, parms = c(beta = 0.2, gamma = 0.1))
 head(out)
@@
 stoch<-read.csv("k8dens0.25inf0.2rec0.2_infected.csv")
-out <- ode(y = init, func = sir, times = times, parms = c(beta = 0.2, gamma = 0.2))
+out <- ode(y = init, func = density_sir, times = times, parms = c(beta = 0.2, gamma = 0.2))
 head(out)
@@
 stoch<-read.csv("k8dens0.25inf0.2rec0.4_infected.csv")
-out <- ode(y = init, func = sir, times = times, parms = c(beta = 0.2, gamma = 0.4))
+out <- ode(y = init, func = density_sir, times = times, parms = c(beta = 0.2, gamma = 0.4))
 head(out)
@@
 stoch<-read.csv("k8dens0.5inf0.2rec0.1_infected.csv")
-out <- ode(y = init, func = sir, times = times, parms = c(beta = 0.2, gamma = 0.1))
+out <- ode(y = init, func = density_sir, times = times, parms = c(beta = 0.2, gamma = 0.1))
 head(out)
@@
 stoch<-read.csv("k8dens0.5inf0.2rec0.2_infected.csv")
-out <- ode(y = init, func = sir, times = times, parms = c(beta = 0.2, gamma = 0.2))
+out <- ode(y = init, func = density_sir, times = times, parms = c(beta = 0.2, gamma = 0.2))
 head(out)
@@
 stoch<-read.csv("k8dens0.5inf0.2rec0.4_infected.csv")
-out <- ode(y = init, func = sir, times = times, parms = c(beta = 0.2, gamma = 0.4))
+out <- ode(y = init, func = density_sir, times = times, parms = c(beta = 0.2, gamma = 0.4))
 head(out)
@@
 SIRdata_merged<- do.call("rbind", lapply(summaries, read.csv, header = TRUE))
-#setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/")
+setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/")
+write.csv(SIRdata_merged, file="SIRdata_merged.csv")
 
@@
 ##Box plots
-Box plots comparing density and recovery rates
+Box plots comparing density and recovery rates for homogenous mixing SIR model
 ```{r}
@@
 hh<- hh + stat_summary(fun.y=mean, colour="darkred", geom="point", 
-                           shape=18, size=3,show_guide = FALSE)
+                           shape=18, size=3,show.legend = FALSE)
 hh<-hh + geom_text(data = means , aes(label = duration, y = duration + 0.08))
@@
 
-##Box plot
-Compare homogenous mixing and spatial models
+##Fig. S6
+Compare homogenous mixing and spatial models in box plot form.
 ```{r}
-SIRdata_merged$percep<-"Homogenous"
+setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/")
+SIRdata_merged<-read.csv("SIRdata_merged.csv")
+SIRdata_merged<-SIRdata_merged[,-1]
+
+SIRdata_merged$percep<-"H"
 SIRdata_merged$p<-NA
@@
 
-h_vs_s <-rbind(sub_data, SIRdata_merged)
+h_vs_s <-rbind(merged_data, SIRdata_merged)
 hh <- ggplot(h_vs_s, aes(x = as.factor(rec_rate), y = max_prevalence, fill = percep))
 hh<-hh+ geom_boxplot()+ facet_grid(. ~ density, scales= "free_x", labeller=label_both)
-hh<- hh+ labs(fill= "Perceptual \ndistance", x = expression(Recovery~rate~(gamma)), y = "Maximum prevalence", title="(A)")
-hh<- hh+ theme(axis.title = element_text(face="bold", size=16), title=element_text(face="bold", size=16))
-hh<- hh + theme(axis.text.x = element_text(vjust=0.5, size=16))
-hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-hh<- hh + theme(strip.text = element_text(vjust=0.5, size=14))
+hh<- hh+ labs(fill= "Perceptual \ndistance", x = expression(Recovery~rate~(gamma)), y = "Maximum prevalence")#, title="(A)")
+hh<- hh+ theme(axis.title = element_text(size=6), plot.title=element_text(size=7))
+hh<- hh + theme(axis.text.x = element_text(vjust=0.5, size=6))
+hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+hh<- hh + theme(strip.text = element_text(vjust=0.5, size=6))
+hh<- hh + theme(legend.position="none")
+hh<- hh + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
+hh<- hh +theme(plot.margin=unit(c(0.1,0.1,0,0.1),"cm"))
 #hh<- hh + stat_summary(fun.y=mean, colour="darkred", geom="point", 
@@
 ii<-ii+ geom_boxplot()+ facet_grid(. ~ density, scales= "free_x", labeller=label_both)
-ii<- ii+ labs(fill= "Perceptual \ndistance", x = expression(Recovery~rate~(gamma)), y = "Duration", title="(B)")
-ii<- ii+ theme(axis.title = element_text(face="bold", size=16), title=element_text(face="bold", size=16))
-ii<- ii + theme(axis.text.x = element_text(vjust=0.5, size=16))
-ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-ii<- ii + theme(strip.text = element_text(vjust=0.5, size=14))
+ii<- ii+ labs(fill= "Perceptual \ndistance", x = expression(Recovery~rate~(gamma)), y = "Duration") #, title="(B)")
+ii<- ii+ theme(axis.title = element_text(size=6), plot.title=element_text(size=7))
+ii<- ii + theme(axis.text.x = element_text(vjust=0.5, size=6))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6))
+ii<- ii + theme(legend.position="bottom")
+ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
+ii<- ii +theme(plot.margin=unit(c(-0.1,0.1,-0.5,0.1),"cm"))
 #ii<- ii + stat_summary(fun.y=mean, colour="darkred", geom="point", 
@@
 
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
-tiff("Compare_homog_spatial.tif", height = 8, width = 14, units = "in", compression = "lzw", res = 300)
-multiplot(hh,ii, cols=2)
+#install.packages("ggpubr")
+#library("ggpubr")
+#ggarrange(hh, ii, ncol=2, nrow=1, common.legend = TRUE, legend="bottom")
+
+library(cowplot)
+prow <- plot_grid( hh + theme(legend.position="none"),
+            ii + theme(legend.position="none"),
+           align = 'vh',
+           labels = c("(A)", "(B)"),
+           hjust = -1,
+           nrow = 2, label_size=7
+           )
+
+# extract the legend from one of the plots
+# (clearly the whole thing only makes sense if all plots
+# have the same legend, so we can arbitrarily pick one.)
+legend_b <- get_legend(ii + theme(legend.position="bottom"))
+
+# add the legend underneath the row we made earlier. Give it 10% of the height
+# of one plot (via rel_heights).
+p <- plot_grid( prow, legend_b, ncol = 1, rel_heights = c(1, .07))
+p
+
+setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
+tiff("FigureS6.tiff", height = 17, width = 17,8, units = "cm", compression = "lzw", res = 1200)
+p
+#multiplot(hh,ii, cols=1)
 dev.off()

### 2018-04-09 Manuscript_figures_2017_12_12.Rmd
Remove specific directory references

@@
 ```{r}
-setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
+#setwd()
 merged_data<-read.csv("IBMsummary.csv")
@@
 #Set working directory of where to produce Figures
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
+#setwd()
 ```
@@
 
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
+#setwd()
 tiff("Figure1_RF.tiff", height =10 , width =8.7, units = "cm", compression = "lzw", res = 1200)
@@
 
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
+#setwd()
 tiff("Figure1_RFvert.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
@@
 ```{r}
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
+setwd()
 sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks

### 2018-04-09 SimpleSIR.Rmd
Remove computer specific working directories

@@
 # tic=Sys.time()
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")
+#setwd()
 
@@
 ```{r}
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")
+setwd()
 #set wd to location of stochastic SIR simulation output files
@@
 ##Read in file names 
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")
-filenames <- list.files(path = "C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")
+#setwd()
+filenames <- list.files(path = "") #udpate with file path containing simulation data
 summaries<-filenames[grep("summary", filenames)] #summary data
@@
 SIRdata_merged<- do.call("rbind", lapply(summaries, read.csv, header = TRUE))
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/")
+#setwd("")
 write.csv(SIRdata_merged, file="SIRdata_merged.csv")
@@
 ```{r}
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
+#setwd("")
 #sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks
@@
 ```{r}
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/")
+#setwd() #set working directory to folder containing SIRdata_merged.csv
 SIRdata_merged<-read.csv("SIRdata_merged.csv")
@@
 
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
+#setwd()
 tiff("FigureS6.tiff", height = 17, width = 17,8, units = "cm", compression = "lzw", res = 1200)

### 2018-05-18 PartyRFLogit.R
Random forest analysis using party package
cforest function

@@ -1,0 +1,22 @@
+#Load libraries
+library(party)
+
+#Load data
+merged_data<-read.csv("IBMsummary.csv")
+merged_data<-merged_data[-which(merged_data$beta2==5),] #Take out saturating beta2
+
+#Is an outbreak successful or not?
+merged_data$outbreak<-ifelse(merged_data$max_I>1, 1,0)
+
+set.seed(213)
+
+tic=Sys.time()
+fit.cf1 <- cforest(outbreak ~ p + H+ beta1 +beta2 +beta3+ density + rec_rate + percep, data=merged_data, controls=cforest_unbiased(ntree=1000))
+v1 <- varimp(fit.cf1, conditional= FALSE)
+v1<-v1[order(v1)]
+write.csv(v1, "partyRF_logit1000.csv")
+
+print(difftime(Sys.time(),tic,units="mins"))
+
+
+rm(list=ls(all=T)) #clear workspace

### 2018-05-18 PartyRFLogitDur.R

@@ -1,0 +1,22 @@
+#Load libraries
+library(party)
+
+#Load data
+merged_data<-read.csv("IBMsummary.csv")
+merged_data<-merged_data[-which(merged_data$beta2==5),] #Take out saturating beta2
+
+#Is an outbreak successful or not?
+#merged_data$outbreak<-ifelse(merged_data$max_I>1, 1,0)
+
+set.seed(213)
+
+tic=Sys.time()
+fit.cf1 <- cforest(duration ~ p + H+ beta1 +beta2 + beta3+ density + rec_rate + percep, data=merged_data, controls=cforest_unbiased(ntree=1000))
+v1 <- varimp(fit.cf1, conditional= FALSE)
+v1<-v1[order(v1)]
+write.csv(v1, "partyRF_logitdur1000.csv")
+
+print(difftime(Sys.time(),tic,units="mins"))
+
+
+rm(list=ls(all=T)) #clear workspace

### 2018-05-18 PartyRFLogitPrev.R

@@ -1,0 +1,22 @@
+#Load libraries
+library(party)
+
+#Load data
+merged_data<-read.csv("IBMsummary.csv")
+merged_data<-merged_data[-which(merged_data$beta2==5),] #Take out saturating beta2
+
+#Is an outbreak successful or not?
+#merged_data$outbreak<-ifelse(merged_data$max_I>1, 1,0)
+
+set.seed(213)
+
+tic=Sys.time()
+fit.cf1 <- cforest(max_prevalence ~ p + H+ beta1 +beta2 + beta3+ density + rec_rate + percep, data=merged_data, controls=cforest_unbiased(ntree=1000))
+v1 <- varimp(fit.cf1, conditional= FALSE)
+v1<-v1[order(v1)]
+write.csv(v1, "partyRF_logitprev1000.csv")
+
+print(difftime(Sys.time(),tic,units="mins"))
+
+
+rm(list=ls(all=T)) #clear workspace

### 2018-05-18 Manuscript_figures_2017_12_12.Rmd
Added code for Fig. S9

--- 2018-04-09 Manuscript_figures_2017_12_12.Rmd
@@
 
-##Figure 1
+## Figure 1
 Random forest variable importance results
@@
 
-##Figure 1- vertical
+## Figure 1- vertical
 Random forest variable importance results
@@
              size=.3) +      # Thinner lines
-    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
-    #               size=.3,    # Thinner lines
-    #               width=.2,
-    #               position=position_dodge(.9)) +
+    geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
+                  size=.3,    # Thinner lines
+                  width=.2,
+                  position=position_dodge(.9)) +
     scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
@@
 
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
+setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures May 2018")
 tiff("Figure1_RFvert.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
@@
 
-##Figure 2
+## Figure 2
 Box plots rec rate vs. density
@@
 
-##Figure 3
+## Figure 3
 ```{r}
@@
 
-##Figure 4
+## Figure 4
 Comparing effects on landscape structure for select RSFs holding density, recovery rate and perceptual range constant.
@@
 
-##Supplementary Figure S1
+## Supplementary Figure S1
 Box plot of percep vs. rec rate vs. density for every RSF combination
@@
 
-##Supplementary Figure S2 (Heat maps, density=0.25)
+## Supplementary Figure S2 (Heat maps, density=0.25)
 Heatmap of max prevelance and mean duration for conspecific density=0.25 and comparing recovery rates of 0.1, 0.2, and 0.4
@@
 
-##Supplementary Figure S3 (Heat maps, density=0.5)
+## Supplementary Figure S3 (Heat maps, density=0.5)
 Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing recovery rates of 0.1, 0.2, and 0.4
@@
 
-##Figure S4
+## Figure S4
 ```{r}
@@
 
-##Fig. S5
+## Fig. S5
 Comparing effects on landscape structure for a single RSF(\beta_1=6, \beta_2=2, \beta_3=-0.5) for different densities, perceptual distances, and recovery rates.
@@
 
-##Supplementary Figure S6
+## Supplementary Figure S6
 See SimpleSIR.Rmd
@@
 
-##Figure S8
+## Figure S8
 Representation of neutral landscapes used for simulation studies
@@
 ```
+
+## Figure S9
+Random forest variable importance results from `party` package using cforest function
+```{r}
+setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Party Package May 2018")
+
+#Load importance values (not scaled by SD)
+imp_logit<-read.csv("partyRF_logit1000.csv")
+imp_logitprev<-read.csv("partyRF_logitprev1000.csv")
+imp_logitdur<-read.csv("partyRF_logitdur1000.csv")
+
+#imp_logit$SD<-rep(0.005, times=nrow(imp_logit))
+A<-ggplot(imp_logit, aes(x=reorder(X, x), y=x)) + 
+    geom_bar(position=position_dodge(), stat="identity",
+             colour="black", # Use black outlines,
+             size=.3) +      # Thinner lines
+    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
+    #               size=.3,    # Thinner lines
+    #               width=.2,
+    #               position=position_dodge(.9)) +
+    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
+    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
+    "percep" = "r", "density"="d")) +
+     ylab("Mean Decrease in Accuracy") +
+    #ylab("")+
+    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
+    #ggtitle("(A)") + #" Variable Importance for Epidemic \nSuccess") +
+    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8), axis.title=element_text(size=6)) 
+    #theme(plot.margin=unit(c(0.1,0.1,0,0), "cm"))
+    # theme_bw(axis.text=element_text(size=14),    axis.title=element_text(size=14,face="bold"), plot.title = element_text(size = 40))
+A
+
+#imp_logitprev$SD<-rep(0.0000001, times=nrow(imp_logitprev))
+B<-ggplot(imp_logitprev, aes(x=reorder(X, x), y=x)) + 
+    geom_bar(position=position_dodge(), stat="identity",
+             colour="black", # Use black outlines,
+             size=.3) +      # Thinner lines
+    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
+    #               size=.3,    # Thinner lines
+    #               width=.2,
+    #               position=position_dodge(.9)) +
+    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
+    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
+    "percep" = "r", "density"="d")) +
+     #ylab("Mean Decrease in Accuracy") +
+    ylab(NULL)+
+    theme_bw()+ theme(plot.margin = unit(c(0.25, 0, 0, 0), "cm"))+
+    #ggtitle("(B)") + #" Variable Importance for Maximum \nPrevalence|Success") +
+    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8))
+    #theme(plot.margin=unit(c(-0.25,0.1,0,0), "cm"))
+    #coord_flip()
+B
+
+#imp_logitdur$SD<-rep(100, times=nrow(imp_logitdur))
+C<-ggplot(imp_logitdur, aes(x=reorder(X, x), y=x)) + 
+    geom_bar(position=position_dodge(), stat="identity",
+             colour="black", # Use black outlines,
+             size=.3) +      # Thinner lines
+    # geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
+    #               size=.3,    # Thinner lines
+    #               width=.2,
+    #               position=position_dodge(.9)) +
+    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
+    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
+    "percep" = "r", "density"="d")) +
+    #ylab("Mean Decrease in Accuracy") +
+    ylab(NULL)+
+    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
+    #ggtitle("(C)") + #" Variable Importance for Epidemic \nDuration|Success") +
+
+      theme(axis.text=element_text(size=6), plot.title = element_text(size = 8), axis.title.x=element_text(size=7)) 
+    #theme(plot.margin=unit(c(-0.25,0.1,0,0), "cm"))
+    #coord_flip()
+C
+
+prow <- plot_grid(A, B, C,
+           align = 'vh',
+           labels = c("(A)", "(B)", "(C)"),
+           hjust = -0.75,
+           ncol = 3, label_size=7
+           )
+#paxis <- axis_canvas(prow, axis = "y") 
+#ggdraw(insert_yaxis_grob(prow, paxis, grid::unit(.25, "null")))
+
+setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures May 2018")
+tiff("FigureS9_party.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
+#multiplot(A, B, C, cols=3)
+prow
+dev.off()
+
+```

### 2018-05-18 Manuscript_figures_2017_12_12.Rmd
Remove directory specific references

@@
 
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures May 2018")
+#setwd()
 tiff("Figure1_RFvert.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
@@
 ```{r}
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
+#setwd()
 sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks
@@
 ```{r}
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Party Package May 2018")
+#setwd()
 
@@
 
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures May 2018")
+#setwd()
 tiff("FigureS9_party.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)

### 2018-05-22 Manuscript_figures_2017_12_12.Rmd
Updated figure numbering

--- 2018-05-18 Manuscript_figures_2017_12_12.Rmd
@@
     "percep" = "r", "density"="d")) +
-     ylab("Mean Decrease in Accuracy (%IncMSE)") +
+     ylab("Mean Decrease in Accuracy") +
     #ylab("")+
@@
 
-## Supplementary Figure S1
-Box plot of percep vs. rec rate vs. density for every RSF combination
-```{r}
-sub_data<-merged_data[which(merged_data$max_I>1),]
-sub_data25<-sub_data[which(sub_data$density==0.25),]
-sub_data50<-sub_data[which(sub_data$density==0.5),]
-
-#tiff("boxplot_prev.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
-gg<- ggplot(data=sub_data25, aes(x=betas, y=max_prevalence))#, fill=as.factor(density)))
-#gg<- gg+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
-gg<-gg+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
-gg<- gg+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence",title="(A)")
-gg<- gg+ theme(axis.title = element_text(face="bold", size=20))
-gg<- gg + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
-gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-gg<- gg + theme(strip.text = element_text(vjust=0.5, size=14)) 
-gg<- gg + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
-gg
-#dev.off()
-
-#tiff("boxplot_dur.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
-hh<- ggplot(data=sub_data25, aes(x=betas, y=duration))#, fill=as.factor(density)))
-#hh<- hh+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
-hh<-hh+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
-hh<- hh+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(B)")
-hh<- hh+ theme(axis.title = element_text(face="bold", size=20))
-hh<- hh + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
-hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-hh<- hh + theme(strip.text = element_text(vjust=0.5, size=14)) 
-hh<- hh + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
-hh
-#dev.off()
-
-#tiff("boxplot_prev.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
-ii<- ggplot(data=sub_data50, aes(x=betas, y=max_prevalence))#, fill=as.factor(density)))
-#gg<- gg+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
-ii<-ii+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
-ii<- ii+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence",title="(C)")
-ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
-ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
-ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-ii<- ii + theme(strip.text = element_text(vjust=0.5, size=14)) 
-ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
-ii
-#dev.off()
-
-#tiff("boxplot_dur.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
-jj<- ggplot(data=sub_data50, aes(x=betas, y=duration))#, fill=as.factor(density)))
-#jj<- jj+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
-jj<-jj+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
-jj<- jj+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(D)")
-jj<- jj+ theme(axis.title = element_text(face="bold", size=20))
-jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
-jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-jj<- jj + theme(strip.text = element_text(vjust=0.5, size=14)) 
-jj<- jj + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
-jj
-
-tiff("FigureS2.tiff", height = 20, width = 14, units = "in", compression = "lzw", res = 300)
-multiplot(gg,hh,ii,jj, cols=1)
-dev.off()
-
-```
-
-## Supplementary Figure S2 (Heat maps, density=0.25)
-Heatmap of max prevelance and mean duration for conspecific density=0.25 and comparing recovery rates of 0.1, 0.2, and 0.4
-```{r}
-r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.25),]
-
-sdf <- summaryBy(duration~ H + betas +p+ percep, data=r2, FUN=mean)
-gg <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
-gg <- gg + geom_tile(color="white", size=0.1)
-gg <- gg + scale_fill_viridis(name="Duration")
-gg <- gg + coord_equal()
-gg <- gg + facet_grid(percep ~ betas)
-gg<- gg+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title= "(D)")
-gg<- gg+ theme(axis.title = element_text(face="bold", size=24))
-gg<- gg + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
-gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-gg<- gg + theme(strip.text = element_text(vjust=0.5, size=18)) 
-gg<- gg + theme(strip.text.x = element_text(angle = 90))
-gg<- gg + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
-gg
-
-sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r2, FUN=mean)
-hh <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
-hh <- hh + geom_tile(color="white", size=0.1)
-hh <- hh + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
-hh <- hh + coord_equal()
-hh <- hh + facet_grid(percep ~ betas)
-hh<- hh+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(C)")
-hh<- hh+ theme(axis.title = element_text(face="bold", size=24))
-hh<- hh + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
-hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-hh<- hh + theme(strip.text = element_text(vjust=0.5, size=18)) 
-hh<- hh + theme(strip.text.x = element_text(angle = 90))
-hh<- hh + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
-hh
-
-r1<-merged_data[which(merged_data$rec_rate==0.1 & merged_data$density==0.25),]
-sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r1, FUN=mean)
-ii <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
-ii <- ii + geom_tile(color="white", size=0.1)
-ii <- ii + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
-ii <- ii + coord_equal()
-ii <- ii + facet_grid(percep ~ betas)
-ii<- ii+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(A)")
-ii<- ii+ theme(axis.title = element_text(face="bold", size=24))
-ii<- ii + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
-ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-ii<- ii + theme(strip.text = element_text(vjust=0.5, size=18)) 
-ii<- ii + theme(strip.text.x = element_text(angle = 90))
-ii<- ii + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
-ii
-
-sdf <- summaryBy(duration~ H + betas +p+ percep, data=r1, FUN=mean)
-jj <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
-jj <- jj + geom_tile(color="white", size=0.1)
-jj <- jj + scale_fill_viridis(name="Duration")
-jj <- jj + coord_equal()
-jj <- jj + facet_grid(percep ~ betas)
-jj<- jj+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(B)")
-jj<- jj+ theme(axis.title = element_text(face="bold", size=24))
-jj<- jj + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
-jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-jj<- jj + theme(strip.text = element_text(vjust=0.5, size=18)) 
-jj<- jj + theme(strip.text.x = element_text(angle = 90))
-jj<- jj + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
-jj
-
-r4<-merged_data[which(merged_data$rec_rate==0.4 & merged_data$density==0.25),]
-sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r4, FUN=mean)
-kk <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
-kk <- kk + geom_tile(color="white", size=0.1)
-kk <- kk + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
-kk <- kk + coord_equal()
-kk <- kk + facet_grid(percep ~ betas)
-kk<- kk+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(E)")
-kk<- kk+ theme(axis.title = element_text(face="bold", size=24))
-kk<- kk + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
-kk<- kk + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-kk<- kk + theme(strip.text = element_text(vjust=0.5, size=18)) 
-kk<- kk + theme(strip.text.x = element_text(angle = 90))
-kk<- kk + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
-kk
-
-sdf <- summaryBy(duration~ H + betas +p+ percep, data=r4, FUN=mean)
-mm <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
-mm <- mm + geom_tile(color="white", size=0.1)
-mm <- mm + scale_fill_viridis(name="Duration")
-mm <- mm + coord_equal()
-mm <- mm + facet_grid(percep ~ betas)
-mm<- mm+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(F)")
-mm<- mm+ theme(axis.title = element_text(face="bold", size=24))
-mm<- mm + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
-mm<- mm + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-mm<- mm + theme(strip.text = element_text(vjust=0.5, size=18)) 
-mm<- mm + theme(strip.text.x = element_text(angle = 90))
-mm<- mm + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
-mm
-
-tiff("FigureS4_heatmap.tiff", height = 27, width = 14, units = "in", compression = "lzw", res = 300)
-multiplot(ii,jj,hh,gg, kk,mm, cols=1)
-dev.off()
-```
-
-## Supplementary Figure S3 (Heat maps, density=0.5)
-Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing recovery rates of 0.1, 0.2, and 0.4
-```{r}
-r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.5),]
-
-sdf <- summaryBy(duration~ H + betas +p+ percep, data=r2, FUN=mean)
-gg <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
-gg <- gg + geom_tile(color="white", size=0.1)
-gg <- gg + scale_fill_viridis(name="Duration")
-gg <- gg + coord_equal()
-gg <- gg + facet_grid(percep ~ betas)
-gg<- gg+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title= "(D)")
-gg<- gg+ theme(axis.title = element_text(face="bold", size=24))
-gg<- gg + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
-gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-gg<- gg + theme(strip.text = element_text(vjust=0.5, size=18)) 
-gg<- gg + theme(strip.text.x = element_text(angle = 90))
-gg<- gg + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
-gg
-
-sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r2, FUN=mean)
-hh <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
-hh <- hh + geom_tile(color="white", size=0.1)
-hh <- hh + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
-hh <- hh + coord_equal()
-hh <- hh + facet_grid(percep ~ betas)
-hh<- hh+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(C)")
-hh<- hh+ theme(axis.title = element_text(face="bold", size=24))
-hh<- hh + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
-hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-hh<- hh + theme(strip.text = element_text(vjust=0.5, size=18)) 
-hh<- hh + theme(strip.text.x = element_text(angle = 90))
-hh<- hh + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
-hh
-
-r1<-merged_data[which(merged_data$rec_rate==0.1 & merged_data$density==0.5),]
-sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r1, FUN=mean)
-ii <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
-ii <- ii + geom_tile(color="white", size=0.1)
-ii <- ii + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
-ii <- ii + coord_equal()
-ii <- ii + facet_grid(percep ~ betas)
-ii<- ii+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(A)")
-ii<- ii+ theme(axis.title = element_text(face="bold", size=24))
-ii<- ii + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
-ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-ii<- ii + theme(strip.text = element_text(vjust=0.5, size=18)) 
-ii<- ii + theme(strip.text.x = element_text(angle = 90))
-ii<- ii + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
-ii
-
-sdf <- summaryBy(duration~ H + betas +p+ percep, data=r1, FUN=mean)
-jj <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
-jj <- jj + geom_tile(color="white", size=0.1)
-jj <- jj + scale_fill_viridis(name="Duration")
-jj <- jj + coord_equal()
-jj <- jj + facet_grid(percep ~ betas)
-jj<- jj+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(B)")
-jj<- jj+ theme(axis.title = element_text(face="bold", size=24))
-jj<- jj + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
-jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-jj<- jj + theme(strip.text = element_text(vjust=0.5, size=18)) 
-jj<- jj + theme(strip.text.x = element_text(angle = 90))
-jj<- jj + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
-jj
-
-r4<-merged_data[which(merged_data$rec_rate==0.4 & merged_data$density==0.5),]
-sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r4, FUN=mean)
-kk <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
-kk <- kk + geom_tile(color="white", size=0.1)
-kk <- kk + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
-kk <- kk + coord_equal()
-kk <- kk + facet_grid(percep ~ betas)
-kk<- kk+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(E)")
-kk<- kk+ theme(axis.title = element_text(face="bold", size=24))
-kk<- kk + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
-kk<- kk + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-kk<- kk + theme(strip.text = element_text(vjust=0.5, size=18)) 
-kk<- kk + theme(strip.text.x = element_text(angle = 90))
-kk<- kk + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
-kk
-
-sdf <- summaryBy(duration~ H + betas +p+ percep, data=r4, FUN=mean)
-mm <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
-mm <- mm + geom_tile(color="white", size=0.1)
-mm <- mm + scale_fill_viridis(name="Duration")
-mm <- mm + coord_equal()
-mm <- mm + facet_grid(percep ~ betas)
-mm<- mm+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(F)")
-mm<- mm+ theme(axis.title = element_text(face="bold", size=24))
-mm<- mm + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
-mm<- mm + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
-mm<- mm + theme(strip.text = element_text(vjust=0.5, size=18)) 
-mm<- mm + theme(strip.text.x = element_text(angle = 90))
-mm<- mm + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
-mm
-
-tiff("FigureS3_heatmap.tiff", height = 27, width = 14, units = "in", compression = "lzw", res = 300)
-multiplot(ii,jj,hh,gg, kk,mm, cols=1)
-dev.off()
-```
-
-## Figure S4
-```{r}
-#percep=3, rec_rate=0.2, density=0.5
-p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
-ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=max_prevalence, fill=as.factor(beta2)))
-ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
-ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
-ii<- ii+ theme(plot.title = element_text(size=7))
-ii<- ii+ theme(axis.title = element_text(size=6))
-ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
-ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
-ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
-ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
-ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
-ii<- ii + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
-ii
-
-jj<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=duration, fill=as.factor(beta2)))
-jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
-jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(B)", fill= expression(beta[2]))
-jj<- jj+ theme(plot.title = element_text(size=7))
-jj<- jj+ theme(axis.title = element_text(size=6))
-jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
-jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
-jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
-jj<- jj + theme(legend.text = element_text(vjust=0.5, size=8), legend.title=element_text(vjust=0.5, size=7))
-jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
-jj<- jj + theme(plot.margin=unit(c(-0.1,0.1,0,0.1), "cm"))
-
-jj
-
-tiff("FigureS4.tiff", height = 22.5, width = 17.8, units = "cm", compression = "lzw", res = 900)
-multiplot(ii,jj, cols=1)
-dev.off()
-```
-
-##Figure S4 (log version)
-```{r}
-#percep=3, rec_rate=0.2, density=0.5
-p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
-ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(max_prevalence), fill=as.factor(beta2)))
-ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
-ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Maximum prevalence)", title="(A)", fill= expression(beta[2]))
-ii<- ii+ theme(plot.title = element_text(size=7))
-ii<- ii+ theme(axis.title = element_text(size=6))
-ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
-ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
-ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
-ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
-ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
-jj<- jj + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
-ii
-
-jj<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(duration), fill=as.factor(beta2)))
-jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
-jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Duration)", title="(B)", fill= expression(beta[2]))
-jj<- jj+ theme(plot.title = element_text(size=7))
-jj<- jj+ theme(axis.title = element_text(size=6))
-jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
-jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
-jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
-jj<- jj + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
-jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
-jj<- jj + theme(plot.margin=unit(c(-0.1,0.1,0,0.1), "cm"))
-jj
-
-tiff("FigS4_log.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
-multiplot(ii,jj, cols=1)
-dev.off()
-```
-
-## Fig. S5
-Comparing effects on landscape structure for a single RSF(\beta_1=6, \beta_2=2, \beta_3=-0.5) for different densities, perceptual distances, and recovery rates.
-```{r}
-#sub_data<-merged_data[which(merged_data$max_I>1),]
-sub_data<-merged_data
-
-RSF620.5<-sub_data[which(sub_data$betas=="6 2 -0.5"),]
-RSF620.5_rec0.1<-RSF620.5[which(RSF620.5$rec_rate==0.1),]
-RSF620.5_rec0.2<-RSF620.5[which(RSF620.5$rec_rate==0.2),]
-RSF620.5_rec0.4<-RSF620.5[which(RSF620.5$rec_rate==0.4),]
-
-#Individual plots of RSF box plot max prevalence and duration
-gg<- ggplot(data=RSF620.5_rec0.2, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
-gg<- gg+ geom_boxplot(stat="boxplot", position=position_dodge())
-gg<- gg + facet_grid(percep ~ density)
-# gg<-gg +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
-gg<- gg+ labs(title="(C)", x = "Landscape structure", y = "Mean maximum \n prevalence")
-#gg<-gg +theme_grey()
-#gg<-gg + theme(plot.title = element_text(hjust = 0.5))
-gg<- gg+ theme(plot.title = element_text(size=7))
-gg<- gg+ theme(axis.title = element_text(size=6))
-gg<- gg + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
-gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
-gg<- gg + theme(strip.text = element_text(vjust=0.5, size=6)) 
-#gg <- gg+ theme(legend.position="none")
-#gg<-gg+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
-#gg<-gg+ theme(axis.ticks.x=element_blank())
-#gg<-gg +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
-gg
-
-hh<- ggplot(data=RSF620.5_rec0.2, aes(x=lstructure, y=duration)) #, fill=covariation)
-hh<- hh+ geom_boxplot(stat="boxplot", position=position_dodge())
-hh<- hh + facet_grid(percep ~ density)
-# hh<-hh +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
-hh<- hh+ labs(title="(D)", x = "Landscape structure", y = "Duration")
-#hh<-hh +theme_grey()
-#hh<-hh + theme(plot.title = element_text(hjust = 0.5))
-hh<- hh+ theme(plot.title = element_text(size=7))
-hh<- hh+ theme(axis.title = element_text(size=6))
-hh<- hh + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
-hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
-hh<- hh + theme(strip.text = element_text(vjust=0.5, size=6)) 
-#hh <- hh+ theme(legend.position="none")
-#hh<-hh+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
-#hh<-hh+ theme(axis.ticks.x=element_blank())
-#hh<-hh +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
-hh
-
-#Individual plots of RSF box plot max prevalence and duration
-ii<- ggplot(data=RSF620.5_rec0.1, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
-ii<- ii+ geom_boxplot(stat="boxplot", position=position_dodge())
-ii<- ii + facet_grid(percep ~ density)
-# ii<-ii +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
-ii<- ii+ labs(x = "Landscape structure", y = "Mean maximum \n prevalence", title="(E)")
-#ii<-ii +theme_grey()
-#ii<-ii + theme(plot.title = element_text(hjust = 0.5))
-ii<- ii+ theme(plot.title = element_text(size=7))
-ii<- ii+ theme(axis.title = element_text(size=6))
-ii<- ii + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
-ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
-ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
-#ii <- ii+ theme(legend.position="none")
-#ii<-ii+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
-#ii<-ii+ theme(axis.ticks.x=element_blank())
-#ii<-ii +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
-ii
-
-jj<- ggplot(data=RSF620.5_rec0.1, aes(x=lstructure, y=duration)) #, fill=covariation)
-jj<- jj+ geom_boxplot(stat="boxplot", position=position_dodge())
-jj<- jj + facet_grid(percep ~ density)
-# jj<-jj +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
-jj<- jj+ labs(x = "Landscape structure", y = "Duration", title="(F)")
-#jj<-jj +theme_grey()
-#jj<-jj + theme(plot.title = element_text(hjust = 0.5))
-jj<- jj+ theme(plot.title = element_text(size=7))
-jj<- jj+ theme(axis.title = element_text(size=6))
-jj<- jj + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
-jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
-jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
-#jj <- jj+ theme(legend.position="none")
-#jj<-jj+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
-#jj<-jj+ theme(axis.ticks.x=element_blank())
-#jj<-jj +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
-jj
-
-#Individual plots of RSF box plot max prevalence and duration
-kk<- ggplot(data=RSF620.5_rec0.4, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
-kk<- kk+ geom_boxplot(stat="boxplot", position=position_dodge())
-kk<- kk + facet_grid(percep ~ density)
-# kk<-kk +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
-kk<- kk+ labs(title="(A)", x = "Landscape structure", y = "Mean maximum \n prevalence")
-#kk<-kk +theme_grey()
-#kk<-kk + theme(plot.title = element_text(hjust = 0.5))
-kk<- kk+ theme(plot.title = element_text(size=7))
-kk<- kk+ theme(axis.title = element_text(size=6))
-kk<- kk + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
-kk<- kk + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
-kk<- kk + theme(strip.text = element_text(vjust=0.5, size=6)) 
-#kk <- kk+ theme(legend.position="none")
-#kk<-kk+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
-#kk<-kk+ theme(axis.ticks.x=element_blank())
-#kk<-kk +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
-kk
-
-mm<- ggplot(data=RSF620.5_rec0.4, aes(x=lstructure, y=duration)) #, fill=covariation)
-mm<- mm+ geom_boxplot(stat="boxplot", position=position_dodge())
-mm<- mm + facet_grid(percep ~ density)
-# mm<-mm +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
-mm<- mm+ labs(title="(B)", x = "Landscape structure", y = "Duration")
-#mm<-mm +theme_grey()
-#mm<-mm + theme(plot.title = element_text(hjust = 0.5))
-mm<- mm+ theme(plot.title = element_text(size=7))
-mm<- mm+ theme(axis.title = element_text(size=6))
-mm<- mm + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
-mm<- mm + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
-mm<- mm + theme(strip.text = element_text(vjust=0.5, size=6)) 
-#mm <- mm+ theme(legend.position="none")
-#mm<-mm+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
-#mm<-mm+ theme(axis.ticks.x=element_blank())
-#mm<-mm +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
-mm
-
-tiff("FigureS5.tiff", height = 22, width = 17.8, units = "cm", compression = "lzw", res = 1200)
-multiplot(kk,mm,gg,hh,ii,jj, cols=2)
-dev.off()
-
-```
-
-## Supplementary Figure S6
-See SimpleSIR.Rmd
-
-##Supplementary Figure S7: Calibrating beta2/beta3 for RSF
-```{r}
-#Function to calculate rsf
-myrsf=function(x,b1,b2) exp(x*b1+x^2*b2)   #caclulate rsf
-
-#Function to calculate probability of selecting a given cell relative to other cells
-#' @param x= \delta N
-#' @param x.1= baseline population size of individuals
-#' @param b2= \beta2 
-#' @param b3= \beta3 (quadratic coefficient for RSF)
-#' @param ncells= number of cells in neighborhood (e.g., 9, 25, 49)
-myprsf=function(x,x.1,b2,b3,ncells)  #calculates rsf value for each cell; ncells= number of cells
-{ lowlocs=myrsf(x.1,b2,b3)*(ncells-1)  #x = delta n
-hiloc=myrsf(x+x.1,b2,b3)    
-phi=hiloc/(hiloc+lowlocs)}
-
-##beta2= 0, beta3=0
-A <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
-  stat_function(fun = myprsf, args = list(0, 0, 0, 9),
-                aes(linetype = "N=0")) +
-  stat_function(fun =  myprsf, args = list(2, 0, 0, 9),
-                aes(linetype = "N=2")) +
-  stat_function(fun =  myprsf, args = list(4, 0, 0, 9),
-                aes(linetype = "N=4")) +
-  scale_x_continuous(name = expression(paste(Delta, "N")),
-                     breaks = seq(0, 6, 1),
-                     limits=c(0, 6)) +
-  geom_hline(yintercept = 1/9, colour="red") + 
-  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
-  ggtitle(expression(paste("(A) ", beta[2], "= 0 & ", beta[3], "= 0 (Random)"))) +
-  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
-A
-
-##beta2= 0, beta3=-1
-B <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
-  stat_function(fun = myprsf, args = list(0, 0, -1, 9),
-                aes(linetype = "N=0")) +
-  stat_function(fun =  myprsf, args = list(2, 0, -1, 9),
-                aes(linetype = "N=2")) +
-  stat_function(fun =  myprsf, args = list(4, 0, -1, 9),
-                aes(linetype = "N=4")) +
-  scale_x_continuous(name = expression(paste(Delta, "N")),
-                     breaks = seq(0, 6, 1),
-                     limits=c(0, 6)) +
-  geom_hline(yintercept = 1/9, colour="red") + 
-  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
-  ggtitle(expression(paste("(B) ", beta[2], "= 0 & ", beta[3], "= -1 (Negative)"))) +
-  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
-B
-
-##beta2= 1, beta3=-1
-C <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
-  stat_function(fun = myprsf, args = list(0, 1, -1, 9),
-                aes(linetype = "N=0")) +
-  stat_function(fun =  myprsf, args = list(2, 1, -1, 9),
-                aes(linetype = "N=2")) +
-  stat_function(fun =  myprsf, args = list(4, 1, -1, 9),
-                aes(linetype = "N=4")) +
-  scale_x_continuous(name = expression(paste(Delta, "N")),
-                     breaks = seq(0, 6, 1),
-                     limits=c(0, 6)) +
-  geom_hline(yintercept = 1/9, colour="red") + 
-  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
-  ggtitle(expression(paste("(C) ", beta[2], "= 1 & ", beta[3], "=-1 (Positive)"))) +
-  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
-C
-
-##beta2= 0, beta3=0
-D <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
-  stat_function(fun = myprsf, args = list(0, 1, -0.5, 9),
-                aes(linetype = "N=0")) +
-  stat_function(fun =  myprsf, args = list(2, 1, -0.5, 9),
-                aes(linetype = "N=2")) +
-  stat_function(fun =  myprsf, args = list(4, 1, -0.5, 9),
-                aes(linetype = "N=4")) +
-  scale_x_continuous(name = expression(paste(Delta, "N")),
-                     breaks = seq(0, 6, 1),
-                     limits=c(0, 6)) +
-  geom_hline(yintercept = 1/9, colour="red") + 
-  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
-  ggtitle(expression(paste("(D) ", beta[2], "= 1 & ", beta[3], "= -0.5 (Positive)"))) +
-  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
-D
-
-##beta2= 2, beta3=-1
-E <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
-  stat_function(fun = myprsf, args = list(0, 2, -1, 9),
-                aes(linetype = "N=0")) +
-  stat_function(fun =  myprsf, args = list(2, 2, -1, 9),
-                aes(linetype = "N=2")) +
-  stat_function(fun =  myprsf, args = list(4, 2, -1, 9),
-                aes(linetype = "N=4")) +
-  scale_x_continuous(name = expression(paste(Delta, "N")),
-                     breaks = seq(0, 6, 1),
-                     limits=c(0, 6)) +
-  geom_hline(yintercept = 1/9, colour="red") + 
-  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
-  ggtitle(expression(paste("(E) ", beta[2], "= 2 & ", beta[3], "=-1 (Positive)"))) +
-  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
-E
-
-##beta2= 2, beta3=-0.5
-F <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
-  stat_function(fun = myprsf, args = list(0, 2, -0.5, 9),
-                aes(linetype = "N=0")) +
-  stat_function(fun =  myprsf, args = list(2, 2, -0.5, 9),
-                aes(linetype = "N=2")) +
-  stat_function(fun =  myprsf, args = list(4, 2, -0.5, 9),
-                aes(linetype = "N=4")) +
-  scale_x_continuous(name = expression(paste(Delta, "N")),
-                     breaks = seq(0, 6, 1),
-                     limits=c(0, 6)) +
-  geom_hline(yintercept = 1/9, colour="red") + 
-  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
-  ggtitle(expression(paste("(F) ", beta[2], "= 2 & ", beta[3], "=-0.5 (Positive)"))) +
-  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
-F
-
-tiff("RSF_conspecifics.tiff", height = 18, width = 14, units = "in", compression = "lzw", res = 300)
-multiplot(A,B,C,D,E,F, cols=2)
-dev.off()
-```
-
-## Figure S8
-Representation of neutral landscapes used for simulation studies
-```{r}
-#' Create neutral landscape maps
-library(raster)
-
-#' Use standard methods to generate fractal maps. Binary and continuous surfaces may be produced.
-#' 
-#' @param k integer. The extent of the map (2^k+1)^2 pixels
-#' @param h numeric. Level of aggregation in the map.
-#' @param p numeric (0,1). The proportion of map in habitat=1
-#' @param binary logical. If TRUE, a 0/1 categorical landscape is produced.
-#' @author Shannon Pittman, James Forester, modified by Lauren White
-#' @export
-#' @example examples/neutral.landscape_example.R
-fracland_mod <- function(k, h, p, binary = TRUE) {
-  ## Function for creating neutral landscapes Shannon Pittman University of Minnesota May, 2013 k = the extent of the map (2^k+1)^2 pixels h =
-  ## how clumped the map should be (ranging from ?? to ??) -- weird behavior at higher values p = proportion of map in habitat 1 binary =
-  ## plotflag == if TRUE will plot a filled contour version of the matrix
-
-  ## function call: testmap=land(6,1,.5,FALSE,TRUE)
-  A <- 2^k + 1  # Scalar-determines length of landscape matrix
-
-  #Right now, as written (1-p) represents the amount of habitat listed as "1"
-  B <- matrix(0, A, A)  # Creates landscape matrix
-
-  B[1, 1] <- 0
-  B[1, A] <- 0
-  B[A, 1] <- 0
-  B[A, A] <- 0
-
-  iter <- 1
-  for (iter in 1:k) {
-    scalef <- (0.5 + (1 - h)/2)^(iter)
-
-    d <- 2^(k - iter)
-
-    # ALL SQUARE STEPS#
-    for (i in seq(d + 1, A - d, 2 * d)) {
-      for (j in seq(d + 1, A - d, 2 * d)) {
-        B[i, j] <- mean(c(B[i - d, j - d], B[i - d, j + d], B[i + d, j - d], B[i + d, j + d])) + scalef * rnorm(n = 1)
-      }
-    }
-
-    # OUTSIDE DIAMOND STEP#
-    for (j in seq(d + 1, A - d, 2 * d)) {
-      B[1, j] <- mean(c(B[1, j - d], B[1, j + d], B[1 + d, j])) + scalef * rnorm(n = 1)
-      B[A, j] <- mean(c(B[A, j - d], B[A, j + d], B[A - d, j])) + scalef * rnorm(n = 1)
-    }
-
-    for (i in seq(d + 1, A - d, 2 * d)) {
-      B[i, 1] <- mean(c(B[i - d, 1], B[i + d, 1], B[i, 1 + d])) + scalef * rnorm(n = 1)
-      B[i, A] <- mean(c(B[i - d, A], B[i + d, A], B[i, A - d])) + scalef * rnorm(n = 1)
-    }
-
-    # INSIDE DIAMOND STEP#
-    if (2 * d + 1 <= A - 2 * d) {
-      for (i in seq(d + 1, A - d, 2 * d)) {
-        for (j in seq(2 * d + 1, A - 2 * d, 2 * d)) {
-          B[i, j] <- mean(c(B[i - d, j], B[i + d, j], B[i, j - d], B[i, j + d])) + scalef * rnorm(n = 1)
-        }
-      }
-
-      for (i in seq(2 * d + 1, A - 2 * d, 2 * d)) {
-        for (j in seq(d + 1, A - d, 2 * d)) {
-          B[i, j] <- mean(c(B[i - d, j], B[i + d, j], B[i, j - d], B[i, j + d])) + scalef * rnorm(n = 1)
-        }
-      }
-    }
-
-    iter <- iter + 1
-  }
-
-  if (binary == T) {
-    R <- sort(B)
-    PosR <- (1 - p) * length(R)  #larger values become habitat, designated as 1
-    pval <- R[PosR]
-    T1 <- which(B > pval)
-    T2 <- which(B <= pval)
-    B[T1] <- 1  #habitat is 1
-    B[T2] <- 0
-  } 
-  return(B)
-}
-
-landscape<-fracland_mod(k=7, h=0.1, p=0.25)
-map.1 <- raster(landscape)
-one<-spplot(map.1)
-landscape<-fracland_mod(k=7, h=0.1, p=0.5) 
-map.2 <- raster(landscape)
-two<-spplot(map.2)
-landscape<-fracland_mod(k=7, h=0.1, p=0.75)
-map.3 <- raster(landscape)
-three<-spplot(map.3)
-
-landscape<-fracland_mod(k=7, h=0.5, p=0.25) 
-map.4 <- raster(landscape)
-four<-spplot(map.4)
-landscape<-fracland_mod(k=7, h=0.5, p=0.5) 
-map.5 <- raster(landscape)
-five<-spplot(map.5)
-landscape<-fracland_mod(k=7, h=0.5, p=0.75)
-map.6 <- raster(landscape)
-six<-spplot(map.6)
-
-landscape<-fracland_mod(k=7, h=0.9, p=0.25)
-map.7 <- raster(landscape)
-seven<-spplot(map.7)
-landscape<-fracland_mod(k=7, h=0.9, p=0.5)
-map.8 <- raster(landscape)
-eight<-spplot(map.8)
-landscape<-fracland_mod(k=7, h=0.9, p=0.75)
-map.9 <- raster(landscape)
-# nine<-spplot(map.9)
-
-#convert the raster to points for plotting
-H<-rep(0.1, times=length(map.1))
-map.1 <- rasterToPoints(map.1)
-p<-rep(0.25, times=length(map.1))
-df <- data.frame(map.1, H, p)
-
-map.2 <- rasterToPoints(map.2)
-p<-rep(0.5, times=length(map.1))
-df2 <- data.frame(map.2, H, p)
-
-map.3 <- rasterToPoints(map.3)
-p<-rep(0.75, times=length(map.1))
-df3 <- data.frame(map.3, H, p)
-
-H<-rep(0.5, times=length(map.1))
-map.4 <- rasterToPoints(map.4)
-p<-rep(0.25, times=length(map.1))
-df4 <- data.frame(map.4, H, p)
-
-map.5 <- rasterToPoints(map.5)
-p<-rep(0.5, times=length(map.1))
-df5 <- data.frame(map.5, H, p)
-
-map.6 <- rasterToPoints(map.6)
-p<-rep(0.75, times=length(map.1))
-df6 <- data.frame(map.6, H, p)
-
-H<-rep(0.9, times=length(map.1))
-map.7 <- rasterToPoints(map.7)
-p<-rep(0.25, times=length(map.1))
-df7 <- data.frame(map.7, H, p)
-
-map.8 <- rasterToPoints(map.8)
-p<-rep(0.5, times=length(map.1))
-df8 <- data.frame(map.8, H, p)
-
-map.9 <- rasterToPoints(map.9)
-p<-rep(0.75, times=length(map.1))
-df9 <- data.frame(map.9, H, p)
-
-#Make the points a dataframe for ggplot
-
-df <- rbind(df, df2)
-df <- rbind(df, df3)
-df <- rbind(df, df4)
-df <- rbind(df, df5)
-df <- rbind(df, df6)
-df <- rbind(df, df7)
-df <- rbind(df, df8)
-df <- rbind(df, df9)
-
-my_x_title <- expression(paste("Hurst exponent- habitat patchiness (", italic("H"), ")"))
-my_y_title <- expression(paste("Proportion of available habitat (", italic("p"), ")"))
-
-#Now make the map
-tiff("FigureS7_p_vs_H.tif", height = 8.7, width = 8.7, units = "cm", compression = "lzw", res = 900)
-ggplot(data=df, aes(y=y, x=x)) +
-  geom_raster(aes(fill=layer)) +
-    theme_bw() +
-  coord_equal() +
-  facet_grid(p~ H) +
-  #scale_fill_viridis(name="Resource quality")+
-  #scale_fill_continuous(colours=c("#0000FFFF","#FFFFFFFF"))+
-  scale_fill_gradient(low="lightgrey", high="darkgreen", guide=FALSE) +
-  #scale_fill_continuous(guide = FALSE) +
-  labs(y=my_y_title, x=my_x_title)+
-  theme(axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
-  theme(axis.title = element_text(size=10)) +
-  theme(strip.text = element_text(vjust=0.5, size=9))+ 
-  theme(legend.text = element_text(vjust=0.5, size=9), legend.title=element_text(vjust=0.5, size=10))
-dev.off()
-
-```
-
-## Figure S9
+## Figure S1
 Random forest variable importance results from `party` package using cforest function
@@
 setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures May 2018")
-tiff("FigureS9_party.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
+tiff("FigureS1_party.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
 #multiplot(A, B, C, cols=3)
@@
 ```
+
+## Supplementary Figure S2
+Box plot of percep vs. rec rate vs. density for every RSF combination
+```{r}
+sub_data<-merged_data[which(merged_data$max_I>1),]
+sub_data25<-sub_data[which(sub_data$density==0.25),]
+sub_data50<-sub_data[which(sub_data$density==0.5),]
+
+#tiff("boxplot_prev.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
+gg<- ggplot(data=sub_data25, aes(x=betas, y=max_prevalence))#, fill=as.factor(density)))
+#gg<- gg+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
+gg<-gg+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
+gg<- gg+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence",title="(A)")
+gg<- gg+ theme(axis.title = element_text(face="bold", size=20))
+gg<- gg + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
+gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+gg<- gg + theme(strip.text = element_text(vjust=0.5, size=14)) 
+gg<- gg + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
+gg
+#dev.off()
+
+#tiff("boxplot_dur.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
+hh<- ggplot(data=sub_data25, aes(x=betas, y=duration))#, fill=as.factor(density)))
+#hh<- hh+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
+hh<-hh+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
+hh<- hh+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(B)")
+hh<- hh+ theme(axis.title = element_text(face="bold", size=20))
+hh<- hh + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
+hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+hh<- hh + theme(strip.text = element_text(vjust=0.5, size=14)) 
+hh<- hh + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
+hh
+#dev.off()
+
+#tiff("boxplot_prev.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
+ii<- ggplot(data=sub_data50, aes(x=betas, y=max_prevalence))#, fill=as.factor(density)))
+#gg<- gg+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
+ii<-ii+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
+ii<- ii+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence",title="(C)")
+ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
+ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=14)) 
+ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
+ii
+#dev.off()
+
+#tiff("boxplot_dur.tiff", height = 8, width = 12, units = "in", compression = "lzw", res = 300)
+jj<- ggplot(data=sub_data50, aes(x=betas, y=duration))#, fill=as.factor(density)))
+#jj<- jj+ geom_bar(stat="identity", position=position_dodge(), colour="black")+ facet_grid(Rec.prob. ~ percep, scales= "free_x", labeller=label_both)
+jj<-jj+ geom_boxplot()+ facet_grid(rec_rate ~ percep, scales= "free_x", labeller=label_both)
+jj<- jj+ labs(x = expression(Resource~Selection~Function~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(D)")
+jj<- jj+ theme(axis.title = element_text(face="bold", size=20))
+jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, size=16))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=14)) 
+jj<- jj + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=20))
+jj
+
+tiff("FigureS2.tiff", height = 20, width = 14, units = "in", compression = "lzw", res = 300)
+multiplot(gg,hh,ii,jj, cols=1)
+dev.off()
+
+```
+
+## Supplementary Figure S3 (Heat maps, density=0.25)
+Heatmap of max prevelance and mean duration for conspecific density=0.25 and comparing recovery rates of 0.1, 0.2, and 0.4
+```{r}
+r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.25),]
+
+sdf <- summaryBy(duration~ H + betas +p+ percep, data=r2, FUN=mean)
+gg <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
+gg <- gg + geom_tile(color="white", size=0.1)
+gg <- gg + scale_fill_viridis(name="Duration")
+gg <- gg + coord_equal()
+gg <- gg + facet_grid(percep ~ betas)
+gg<- gg+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title= "(D)")
+gg<- gg+ theme(axis.title = element_text(face="bold", size=24))
+gg<- gg + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+gg<- gg + theme(strip.text = element_text(vjust=0.5, size=18)) 
+gg<- gg + theme(strip.text.x = element_text(angle = 90))
+gg<- gg + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+gg
+
+sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r2, FUN=mean)
+hh <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
+hh <- hh + geom_tile(color="white", size=0.1)
+hh <- hh + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
+hh <- hh + coord_equal()
+hh <- hh + facet_grid(percep ~ betas)
+hh<- hh+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(C)")
+hh<- hh+ theme(axis.title = element_text(face="bold", size=24))
+hh<- hh + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+hh<- hh + theme(strip.text = element_text(vjust=0.5, size=18)) 
+hh<- hh + theme(strip.text.x = element_text(angle = 90))
+hh<- hh + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+hh
+
+r1<-merged_data[which(merged_data$rec_rate==0.1 & merged_data$density==0.25),]
+sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r1, FUN=mean)
+ii <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
+ii <- ii + geom_tile(color="white", size=0.1)
+ii <- ii + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
+ii <- ii + coord_equal()
+ii <- ii + facet_grid(percep ~ betas)
+ii<- ii+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(A)")
+ii<- ii+ theme(axis.title = element_text(face="bold", size=24))
+ii<- ii + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=18)) 
+ii<- ii + theme(strip.text.x = element_text(angle = 90))
+ii<- ii + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+ii
+
+sdf <- summaryBy(duration~ H + betas +p+ percep, data=r1, FUN=mean)
+jj <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
+jj <- jj + geom_tile(color="white", size=0.1)
+jj <- jj + scale_fill_viridis(name="Duration")
+jj <- jj + coord_equal()
+jj <- jj + facet_grid(percep ~ betas)
+jj<- jj+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(B)")
+jj<- jj+ theme(axis.title = element_text(face="bold", size=24))
+jj<- jj + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=18)) 
+jj<- jj + theme(strip.text.x = element_text(angle = 90))
+jj<- jj + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+jj
+
+r4<-merged_data[which(merged_data$rec_rate==0.4 & merged_data$density==0.25),]
+sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r4, FUN=mean)
+kk <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
+kk <- kk + geom_tile(color="white", size=0.1)
+kk <- kk + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
+kk <- kk + coord_equal()
+kk <- kk + facet_grid(percep ~ betas)
+kk<- kk+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(E)")
+kk<- kk+ theme(axis.title = element_text(face="bold", size=24))
+kk<- kk + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+kk<- kk + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+kk<- kk + theme(strip.text = element_text(vjust=0.5, size=18)) 
+kk<- kk + theme(strip.text.x = element_text(angle = 90))
+kk<- kk + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+kk
+
+sdf <- summaryBy(duration~ H + betas +p+ percep, data=r4, FUN=mean)
+mm <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
+mm <- mm + geom_tile(color="white", size=0.1)
+mm <- mm + scale_fill_viridis(name="Duration")
+mm <- mm + coord_equal()
+mm <- mm + facet_grid(percep ~ betas)
+mm<- mm+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(F)")
+mm<- mm+ theme(axis.title = element_text(face="bold", size=24))
+mm<- mm + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+mm<- mm + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+mm<- mm + theme(strip.text = element_text(vjust=0.5, size=18)) 
+mm<- mm + theme(strip.text.x = element_text(angle = 90))
+mm<- mm + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+mm
+
+tiff("FigureS3_heatmap.tiff", height = 27, width = 14, units = "in", compression = "lzw", res = 300)
+multiplot(ii,jj,hh,gg, kk,mm, cols=1)
+dev.off()
+```
+
+## Supplementary Figure S4 (Heat maps, density=0.5)
+Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing recovery rates of 0.1, 0.2, and 0.4
+```{r}
+r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.5),]
+
+sdf <- summaryBy(duration~ H + betas +p+ percep, data=r2, FUN=mean)
+gg <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
+gg <- gg + geom_tile(color="white", size=0.1)
+gg <- gg + scale_fill_viridis(name="Duration")
+gg <- gg + coord_equal()
+gg <- gg + facet_grid(percep ~ betas)
+gg<- gg+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title= "(D)")
+gg<- gg+ theme(axis.title = element_text(face="bold", size=24))
+gg<- gg + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+gg<- gg + theme(strip.text = element_text(vjust=0.5, size=18)) 
+gg<- gg + theme(strip.text.x = element_text(angle = 90))
+gg<- gg + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+gg
+
+sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r2, FUN=mean)
+hh <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
+hh <- hh + geom_tile(color="white", size=0.1)
+hh <- hh + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
+hh <- hh + coord_equal()
+hh <- hh + facet_grid(percep ~ betas)
+hh<- hh+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(C)")
+hh<- hh+ theme(axis.title = element_text(face="bold", size=24))
+hh<- hh + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+hh<- hh + theme(strip.text = element_text(vjust=0.5, size=18)) 
+hh<- hh + theme(strip.text.x = element_text(angle = 90))
+hh<- hh + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+hh
+
+r1<-merged_data[which(merged_data$rec_rate==0.1 & merged_data$density==0.5),]
+sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r1, FUN=mean)
+ii <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
+ii <- ii + geom_tile(color="white", size=0.1)
+ii <- ii + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
+ii <- ii + coord_equal()
+ii <- ii + facet_grid(percep ~ betas)
+ii<- ii+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(A)")
+ii<- ii+ theme(axis.title = element_text(face="bold", size=24))
+ii<- ii + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=18)) 
+ii<- ii + theme(strip.text.x = element_text(angle = 90))
+ii<- ii + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+ii
+
+sdf <- summaryBy(duration~ H + betas +p+ percep, data=r1, FUN=mean)
+jj <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
+jj <- jj + geom_tile(color="white", size=0.1)
+jj <- jj + scale_fill_viridis(name="Duration")
+jj <- jj + coord_equal()
+jj <- jj + facet_grid(percep ~ betas)
+jj<- jj+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(B)")
+jj<- jj+ theme(axis.title = element_text(face="bold", size=24))
+jj<- jj + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=18)) 
+jj<- jj + theme(strip.text.x = element_text(angle = 90))
+jj<- jj + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+jj
+
+r4<-merged_data[which(merged_data$rec_rate==0.4 & merged_data$density==0.5),]
+sdf <- summaryBy(max_prevalence~ H + betas +p+ percep, data=r4, FUN=mean)
+kk <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=max_prevalence.mean))
+kk <- kk + geom_tile(color="white", size=0.1)
+kk <- kk + scale_fill_viridis(name="Mean \nmaximum \nprevalence")
+kk <- kk + coord_equal()
+kk <- kk + facet_grid(percep ~ betas)
+kk<- kk+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(E)")
+kk<- kk+ theme(axis.title = element_text(face="bold", size=24))
+kk<- kk + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+kk<- kk + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+kk<- kk + theme(strip.text = element_text(vjust=0.5, size=18)) 
+kk<- kk + theme(strip.text.x = element_text(angle = 90))
+kk<- kk + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+kk
+
+sdf <- summaryBy(duration~ H + betas +p+ percep, data=r4, FUN=mean)
+mm <- ggplot(sdf, aes(x=as.factor(p), y=as.factor(H), fill=duration.mean))
+mm <- mm + geom_tile(color="white", size=0.1)
+mm <- mm + scale_fill_viridis(name="Duration")
+mm <- mm + coord_equal()
+mm <- mm + facet_grid(percep ~ betas)
+mm<- mm+ labs(x="Proportion of available habitat (p)", y="Hurst exponent (H)", title="(F)")
+mm<- mm+ theme(axis.title = element_text(face="bold", size=24))
+mm<- mm + theme(axis.text.x = element_text(angle=90, hjust=0, vjust=0.5, size=16))
+mm<- mm + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
+mm<- mm + theme(strip.text = element_text(vjust=0.5, size=18)) 
+mm<- mm + theme(strip.text.x = element_text(angle = 90))
+mm<- mm + theme(legend.text = element_text(vjust=0.5, size=14), legend.title=element_text(vjust=0.5, size=20))
+mm
+
+tiff("FigureS4_heatmap.tiff", height = 27, width = 14, units = "in", compression = "lzw", res = 300)
+multiplot(ii,jj,hh,gg, kk,mm, cols=1)
+dev.off()
+```
+
+## Figure S5
+```{r}
+#percep=3, rec_rate=0.2, density=0.5
+p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
+ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=max_prevalence, fill=as.factor(beta2)))
+ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
+ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
+ii<- ii+ theme(plot.title = element_text(size=7))
+ii<- ii+ theme(axis.title = element_text(size=6))
+ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
+ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
+ii<- ii + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
+ii
+
+jj<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=duration, fill=as.factor(beta2)))
+jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
+jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Duration", title="(B)", fill= expression(beta[2]))
+jj<- jj+ theme(plot.title = element_text(size=7))
+jj<- jj+ theme(axis.title = element_text(size=6))
+jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
+jj<- jj + theme(legend.text = element_text(vjust=0.5, size=8), legend.title=element_text(vjust=0.5, size=7))
+jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
+jj<- jj + theme(plot.margin=unit(c(-0.1,0.1,0,0.1), "cm"))
+
+jj
+
+tiff("FigureS5.tiff", height = 22.5, width = 17.8, units = "cm", compression = "lzw", res = 900)
+multiplot(ii,jj, cols=1)
+dev.off()
+```
+
+##Figure S5 (log version)
+```{r}
+#percep=3, rec_rate=0.2, density=0.5
+p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
+ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(max_prevalence), fill=as.factor(beta2)))
+ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
+ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Maximum prevalence)", title="(A)", fill= expression(beta[2]))
+ii<- ii+ theme(plot.title = element_text(size=7))
+ii<- ii+ theme(axis.title = element_text(size=6))
+ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
+ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
+jj<- jj + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
+ii
+
+jj<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(duration), fill=as.factor(beta2)))
+jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
+jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Duration)", title="(B)", fill= expression(beta[2]))
+jj<- jj+ theme(plot.title = element_text(size=7))
+jj<- jj+ theme(axis.title = element_text(size=6))
+jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
+jj<- jj + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
+jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
+jj<- jj + theme(plot.margin=unit(c(-0.1,0.1,0,0.1), "cm"))
+jj
+
+tiff("FigS5_log.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
+multiplot(ii,jj, cols=1)
+dev.off()
+```
+
+## Fig. S6
+Comparing effects on landscape structure for a single RSF(\beta_1=6, \beta_2=2, \beta_3=-0.5) for different densities, perceptual distances, and recovery rates.
+```{r}
+#sub_data<-merged_data[which(merged_data$max_I>1),]
+sub_data<-merged_data
+
+RSF620.5<-sub_data[which(sub_data$betas=="6 2 -0.5"),]
+RSF620.5_rec0.1<-RSF620.5[which(RSF620.5$rec_rate==0.1),]
+RSF620.5_rec0.2<-RSF620.5[which(RSF620.5$rec_rate==0.2),]
+RSF620.5_rec0.4<-RSF620.5[which(RSF620.5$rec_rate==0.4),]
+
+#Individual plots of RSF box plot max prevalence and duration
+gg<- ggplot(data=RSF620.5_rec0.2, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
+gg<- gg+ geom_boxplot(stat="boxplot", position=position_dodge())
+gg<- gg + facet_grid(percep ~ density)
+# gg<-gg +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
+gg<- gg+ labs(title="(C)", x = "Landscape structure", y = "Mean maximum \n prevalence")
+#gg<-gg +theme_grey()
+#gg<-gg + theme(plot.title = element_text(hjust = 0.5))
+gg<- gg+ theme(plot.title = element_text(size=7))
+gg<- gg+ theme(axis.title = element_text(size=6))
+gg<- gg + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+gg<- gg + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+gg<- gg + theme(strip.text = element_text(vjust=0.5, size=6)) 
+#gg <- gg+ theme(legend.position="none")
+#gg<-gg+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
+#gg<-gg+ theme(axis.ticks.x=element_blank())
+#gg<-gg +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
+gg
+
+hh<- ggplot(data=RSF620.5_rec0.2, aes(x=lstructure, y=duration)) #, fill=covariation)
+hh<- hh+ geom_boxplot(stat="boxplot", position=position_dodge())
+hh<- hh + facet_grid(percep ~ density)
+# hh<-hh +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
+hh<- hh+ labs(title="(D)", x = "Landscape structure", y = "Duration")
+#hh<-hh +theme_grey()
+#hh<-hh + theme(plot.title = element_text(hjust = 0.5))
+hh<- hh+ theme(plot.title = element_text(size=7))
+hh<- hh+ theme(axis.title = element_text(size=6))
+hh<- hh + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+hh<- hh + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+hh<- hh + theme(strip.text = element_text(vjust=0.5, size=6)) 
+#hh <- hh+ theme(legend.position="none")
+#hh<-hh+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
+#hh<-hh+ theme(axis.ticks.x=element_blank())
+#hh<-hh +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
+hh
+
+#Individual plots of RSF box plot max prevalence and duration
+ii<- ggplot(data=RSF620.5_rec0.1, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
+ii<- ii+ geom_boxplot(stat="boxplot", position=position_dodge())
+ii<- ii + facet_grid(percep ~ density)
+# ii<-ii +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
+ii<- ii+ labs(x = "Landscape structure", y = "Mean maximum \n prevalence", title="(E)")
+#ii<-ii +theme_grey()
+#ii<-ii + theme(plot.title = element_text(hjust = 0.5))
+ii<- ii+ theme(plot.title = element_text(size=7))
+ii<- ii+ theme(axis.title = element_text(size=6))
+ii<- ii + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
+#ii <- ii+ theme(legend.position="none")
+#ii<-ii+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
+#ii<-ii+ theme(axis.ticks.x=element_blank())
+#ii<-ii +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
+ii
+
+jj<- ggplot(data=RSF620.5_rec0.1, aes(x=lstructure, y=duration)) #, fill=covariation)
+jj<- jj+ geom_boxplot(stat="boxplot", position=position_dodge())
+jj<- jj + facet_grid(percep ~ density)
+# jj<-jj +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
+jj<- jj+ labs(x = "Landscape structure", y = "Duration", title="(F)")
+#jj<-jj +theme_grey()
+#jj<-jj + theme(plot.title = element_text(hjust = 0.5))
+jj<- jj+ theme(plot.title = element_text(size=7))
+jj<- jj+ theme(axis.title = element_text(size=6))
+jj<- jj + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
+#jj <- jj+ theme(legend.position="none")
+#jj<-jj+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
+#jj<-jj+ theme(axis.ticks.x=element_blank())
+#jj<-jj +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
+jj
+
+#Individual plots of RSF box plot max prevalence and duration
+kk<- ggplot(data=RSF620.5_rec0.4, aes(x=lstructure, y=max_prevalence)) #, fill=covariation)
+kk<- kk+ geom_boxplot(stat="boxplot", position=position_dodge())
+kk<- kk + facet_grid(percep ~ density)
+# kk<-kk +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
+kk<- kk+ labs(title="(A)", x = "Landscape structure", y = "Mean maximum \n prevalence")
+#kk<-kk +theme_grey()
+#kk<-kk + theme(plot.title = element_text(hjust = 0.5))
+kk<- kk+ theme(plot.title = element_text(size=7))
+kk<- kk+ theme(axis.title = element_text(size=6))
+kk<- kk + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+kk<- kk + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+kk<- kk + theme(strip.text = element_text(vjust=0.5, size=6)) 
+#kk <- kk+ theme(legend.position="none")
+#kk<-kk+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
+#kk<-kk+ theme(axis.ticks.x=element_blank())
+#kk<-kk +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
+kk
+
+mm<- ggplot(data=RSF620.5_rec0.4, aes(x=lstructure, y=duration)) #, fill=covariation)
+mm<- mm+ geom_boxplot(stat="boxplot", position=position_dodge())
+mm<- mm + facet_grid(percep ~ density)
+# mm<-mm +  scale_x_discrete(limits= c("L/HP", "L/MP", "L/LP", "M/HP", "M/MP", "M/LP", "H/HP", "H/MP", "H/LP"))
+mm<- mm+ labs(title="(B)", x = "Landscape structure", y = "Duration")
+#mm<-mm +theme_grey()
+#mm<-mm + theme(plot.title = element_text(hjust = 0.5))
+mm<- mm+ theme(plot.title = element_text(size=7))
+mm<- mm+ theme(axis.title = element_text(size=6))
+mm<- mm + theme(axis.text.x = element_text(angle=90, hjust= 0, vjust=0.5, size=6))
+mm<- mm + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
+mm<- mm + theme(strip.text = element_text(vjust=0.5, size=6)) 
+#mm <- mm+ theme(legend.position="none")
+#mm<-mm+  theme( axis.ticks.length=unit(-0.1, "cm")) #, axis.ticks.margin=unit(0.5, "cm"))
+#mm<-mm+ theme(axis.ticks.x=element_blank())
+#mm<-mm +theme (axis.text.x = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")), axis.text.y = element_text(margin=unit(c(0.15,0.15,0.15,0.15), "cm")))
+mm
+
+tiff("FigureS6.tiff", height = 22, width = 17.8, units = "cm", compression = "lzw", res = 1200)
+multiplot(kk,mm,gg,hh,ii,jj, cols=2)
+dev.off()
+
+```
+
+## Supplementary Figure S7
+See SimpleSIR.Rmd
+
+##Supplementary Figure S8: Calibrating beta2/beta3 for RSF
+```{r}
+#Function to calculate rsf
+myrsf=function(x,b1,b2) exp(x*b1+x^2*b2)   #caclulate rsf
+
+#Function to calculate probability of selecting a given cell relative to other cells
+#' @param x= \delta N
+#' @param x.1= baseline population size of individuals
+#' @param b2= \beta2 
+#' @param b3= \beta3 (quadratic coefficient for RSF)
+#' @param ncells= number of cells in neighborhood (e.g., 9, 25, 49)
+myprsf=function(x,x.1,b2,b3,ncells)  #calculates rsf value for each cell; ncells= number of cells
+{ lowlocs=myrsf(x.1,b2,b3)*(ncells-1)  #x = delta n
+hiloc=myrsf(x+x.1,b2,b3)    
+phi=hiloc/(hiloc+lowlocs)}
+
+##beta2= 0, beta3=0
+A <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
+  stat_function(fun = myprsf, args = list(0, 0, 0, 9),
+                aes(linetype = "N=0")) +
+  stat_function(fun =  myprsf, args = list(2, 0, 0, 9),
+                aes(linetype = "N=2")) +
+  stat_function(fun =  myprsf, args = list(4, 0, 0, 9),
+                aes(linetype = "N=4")) +
+  scale_x_continuous(name = expression(paste(Delta, "N")),
+                     breaks = seq(0, 6, 1),
+                     limits=c(0, 6)) +
+  geom_hline(yintercept = 1/9, colour="red") + 
+  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
+  ggtitle(expression(paste("(A) ", beta[2], "= 0 & ", beta[3], "= 0 (Random)"))) +
+  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
+A
+
+##beta2= 0, beta3=-1
+B <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
+  stat_function(fun = myprsf, args = list(0, 0, -1, 9),
+                aes(linetype = "N=0")) +
+  stat_function(fun =  myprsf, args = list(2, 0, -1, 9),
+                aes(linetype = "N=2")) +
+  stat_function(fun =  myprsf, args = list(4, 0, -1, 9),
+                aes(linetype = "N=4")) +
+  scale_x_continuous(name = expression(paste(Delta, "N")),
+                     breaks = seq(0, 6, 1),
+                     limits=c(0, 6)) +
+  geom_hline(yintercept = 1/9, colour="red") + 
+  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
+  ggtitle(expression(paste("(B) ", beta[2], "= 0 & ", beta[3], "= -1 (Negative)"))) +
+  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
+B
+
+##beta2= 1, beta3=-1
+C <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
+  stat_function(fun = myprsf, args = list(0, 1, -1, 9),
+                aes(linetype = "N=0")) +
+  stat_function(fun =  myprsf, args = list(2, 1, -1, 9),
+                aes(linetype = "N=2")) +
+  stat_function(fun =  myprsf, args = list(4, 1, -1, 9),
+                aes(linetype = "N=4")) +
+  scale_x_continuous(name = expression(paste(Delta, "N")),
+                     breaks = seq(0, 6, 1),
+                     limits=c(0, 6)) +
+  geom_hline(yintercept = 1/9, colour="red") + 
+  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
+  ggtitle(expression(paste("(C) ", beta[2], "= 1 & ", beta[3], "=-1 (Positive)"))) +
+  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
+C
+
+##beta2= 0, beta3=0
+D <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
+  stat_function(fun = myprsf, args = list(0, 1, -0.5, 9),
+                aes(linetype = "N=0")) +
+  stat_function(fun =  myprsf, args = list(2, 1, -0.5, 9),
+                aes(linetype = "N=2")) +
+  stat_function(fun =  myprsf, args = list(4, 1, -0.5, 9),
+                aes(linetype = "N=4")) +
+  scale_x_continuous(name = expression(paste(Delta, "N")),
+                     breaks = seq(0, 6, 1),
+                     limits=c(0, 6)) +
+  geom_hline(yintercept = 1/9, colour="red") + 
+  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
+  ggtitle(expression(paste("(D) ", beta[2], "= 1 & ", beta[3], "= -0.5 (Positive)"))) +
+  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
+D
+
+##beta2= 2, beta3=-1
+E <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
+  stat_function(fun = myprsf, args = list(0, 2, -1, 9),
+                aes(linetype = "N=0")) +
+  stat_function(fun =  myprsf, args = list(2, 2, -1, 9),
+                aes(linetype = "N=2")) +
+  stat_function(fun =  myprsf, args = list(4, 2, -1, 9),
+                aes(linetype = "N=4")) +
+  scale_x_continuous(name = expression(paste(Delta, "N")),
+                     breaks = seq(0, 6, 1),
+                     limits=c(0, 6)) +
+  geom_hline(yintercept = 1/9, colour="red") + 
+  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
+  ggtitle(expression(paste("(E) ", beta[2], "= 2 & ", beta[3], "=-1 (Positive)"))) +
+  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
+E
+
+##beta2= 2, beta3=-0.5
+F <- ggplot(data.frame(x = c(0, 6)), aes(x = x)) +
+  stat_function(fun = myprsf, args = list(0, 2, -0.5, 9),
+                aes(linetype = "N=0")) +
+  stat_function(fun =  myprsf, args = list(2, 2, -0.5, 9),
+                aes(linetype = "N=2")) +
+  stat_function(fun =  myprsf, args = list(4, 2, -0.5, 9),
+                aes(linetype = "N=4")) +
+  scale_x_continuous(name = expression(paste(Delta, "N")),
+                     breaks = seq(0, 6, 1),
+                     limits=c(0, 6)) +
+  geom_hline(yintercept = 1/9, colour="red") + 
+  scale_y_continuous(name = expression(paste("Probability of selecting cell with ", Delta, "N individuals")), limits=c(0,0.5)) +
+  ggtitle(expression(paste("(F) ", beta[2], "= 2 & ", beta[3], "=-0.5 (Positive)"))) +
+  scale_linetype_manual("Initial \npopulation \nsize", values = c("solid", "dashed", "dotted"))
+F
+
+tiff("RSF_conspecifics.tiff", height = 18, width = 14, units = "in", compression = "lzw", res = 300)
+multiplot(A,B,C,D,E,F, cols=2)
+dev.off()
+```
+
+## Figure S9
+Representation of neutral landscapes used for simulation studies
+```{r}
+#' Create neutral landscape maps
+library(raster)
+
+#' Use standard methods to generate fractal maps. Binary and continuous surfaces may be produced.
+#' 
+#' @param k integer. The extent of the map (2^k+1)^2 pixels
+#' @param h numeric. Level of aggregation in the map.
+#' @param p numeric (0,1). The proportion of map in habitat=1
+#' @param binary logical. If TRUE, a 0/1 categorical landscape is produced.
+#' @author Shannon Pittman, James Forester, modified by Lauren White
+#' @export
+#' @example examples/neutral.landscape_example.R
+fracland_mod <- function(k, h, p, binary = TRUE) {
+  ## Function for creating neutral landscapes Shannon Pittman University of Minnesota May, 2013 k = the extent of the map (2^k+1)^2 pixels h =
+  ## how clumped the map should be (ranging from ?? to ??) -- weird behavior at higher values p = proportion of map in habitat 1 binary =
+  ## plotflag == if TRUE will plot a filled contour version of the matrix
+
+  ## function call: testmap=land(6,1,.5,FALSE,TRUE)
+  A <- 2^k + 1  # Scalar-determines length of landscape matrix
+
+  #Right now, as written (1-p) represents the amount of habitat listed as "1"
+  B <- matrix(0, A, A)  # Creates landscape matrix
+
+  B[1, 1] <- 0
+  B[1, A] <- 0
+  B[A, 1] <- 0
+  B[A, A] <- 0
+
+  iter <- 1
+  for (iter in 1:k) {
+    scalef <- (0.5 + (1 - h)/2)^(iter)
+
+    d <- 2^(k - iter)
+
+    # ALL SQUARE STEPS#
+    for (i in seq(d + 1, A - d, 2 * d)) {
+      for (j in seq(d + 1, A - d, 2 * d)) {
+        B[i, j] <- mean(c(B[i - d, j - d], B[i - d, j + d], B[i + d, j - d], B[i + d, j + d])) + scalef * rnorm(n = 1)
+      }
+    }
+
+    # OUTSIDE DIAMOND STEP#
+    for (j in seq(d + 1, A - d, 2 * d)) {
+      B[1, j] <- mean(c(B[1, j - d], B[1, j + d], B[1 + d, j])) + scalef * rnorm(n = 1)
+      B[A, j] <- mean(c(B[A, j - d], B[A, j + d], B[A - d, j])) + scalef * rnorm(n = 1)
+    }
+
+    for (i in seq(d + 1, A - d, 2 * d)) {
+      B[i, 1] <- mean(c(B[i - d, 1], B[i + d, 1], B[i, 1 + d])) + scalef * rnorm(n = 1)
+      B[i, A] <- mean(c(B[i - d, A], B[i + d, A], B[i, A - d])) + scalef * rnorm(n = 1)
+    }
+
+    # INSIDE DIAMOND STEP#
+    if (2 * d + 1 <= A - 2 * d) {
+      for (i in seq(d + 1, A - d, 2 * d)) {
+        for (j in seq(2 * d + 1, A - 2 * d, 2 * d)) {
+          B[i, j] <- mean(c(B[i - d, j], B[i + d, j], B[i, j - d], B[i, j + d])) + scalef * rnorm(n = 1)
+        }
+      }
+
+      for (i in seq(2 * d + 1, A - 2 * d, 2 * d)) {
+        for (j in seq(d + 1, A - d, 2 * d)) {
+          B[i, j] <- mean(c(B[i - d, j], B[i + d, j], B[i, j - d], B[i, j + d])) + scalef * rnorm(n = 1)
+        }
+      }
+    }
+
+    iter <- iter + 1
+  }
+
+  if (binary == T) {
+    R <- sort(B)
+    PosR <- (1 - p) * length(R)  #larger values become habitat, designated as 1
+    pval <- R[PosR]
+    T1 <- which(B > pval)
+    T2 <- which(B <= pval)
+    B[T1] <- 1  #habitat is 1
+    B[T2] <- 0
+  } 
+  return(B)
+}
+
+landscape<-fracland_mod(k=7, h=0.1, p=0.25)
+map.1 <- raster(landscape)
+one<-spplot(map.1)
+landscape<-fracland_mod(k=7, h=0.1, p=0.5) 
+map.2 <- raster(landscape)
+two<-spplot(map.2)
+landscape<-fracland_mod(k=7, h=0.1, p=0.75)
+map.3 <- raster(landscape)
+three<-spplot(map.3)
+
+landscape<-fracland_mod(k=7, h=0.5, p=0.25) 
+map.4 <- raster(landscape)
+four<-spplot(map.4)
+landscape<-fracland_mod(k=7, h=0.5, p=0.5) 
+map.5 <- raster(landscape)
+five<-spplot(map.5)
+landscape<-fracland_mod(k=7, h=0.5, p=0.75)
+map.6 <- raster(landscape)
+six<-spplot(map.6)
+
+landscape<-fracland_mod(k=7, h=0.9, p=0.25)
+map.7 <- raster(landscape)
+seven<-spplot(map.7)
+landscape<-fracland_mod(k=7, h=0.9, p=0.5)
+map.8 <- raster(landscape)
+eight<-spplot(map.8)
+landscape<-fracland_mod(k=7, h=0.9, p=0.75)
+map.9 <- raster(landscape)
+# nine<-spplot(map.9)
+
+#convert the raster to points for plotting
+H<-rep(0.1, times=length(map.1))
+map.1 <- rasterToPoints(map.1)
+p<-rep(0.25, times=length(map.1))
+df <- data.frame(map.1, H, p)
+
+map.2 <- rasterToPoints(map.2)
+p<-rep(0.5, times=length(map.1))
+df2 <- data.frame(map.2, H, p)
+
+map.3 <- rasterToPoints(map.3)
+p<-rep(0.75, times=length(map.1))
+df3 <- data.frame(map.3, H, p)
+
+H<-rep(0.5, times=length(map.1))
+map.4 <- rasterToPoints(map.4)
+p<-rep(0.25, times=length(map.1))
+df4 <- data.frame(map.4, H, p)
+
+map.5 <- rasterToPoints(map.5)
+p<-rep(0.5, times=length(map.1))
+df5 <- data.frame(map.5, H, p)
+
+map.6 <- rasterToPoints(map.6)
+p<-rep(0.75, times=length(map.1))
+df6 <- data.frame(map.6, H, p)
+
+H<-rep(0.9, times=length(map.1))
+map.7 <- rasterToPoints(map.7)
+p<-rep(0.25, times=length(map.1))
+df7 <- data.frame(map.7, H, p)
+
+map.8 <- rasterToPoints(map.8)
+p<-rep(0.5, times=length(map.1))
+df8 <- data.frame(map.8, H, p)
+
+map.9 <- rasterToPoints(map.9)
+p<-rep(0.75, times=length(map.1))
+df9 <- data.frame(map.9, H, p)
+
+#Make the points a dataframe for ggplot
+
+df <- rbind(df, df2)
+df <- rbind(df, df3)
+df <- rbind(df, df4)
+df <- rbind(df, df5)
+df <- rbind(df, df6)
+df <- rbind(df, df7)
+df <- rbind(df, df8)
+df <- rbind(df, df9)
+
+my_x_title <- expression(paste("Hurst exponent- habitat patchiness (", italic("H"), ")"))
+my_y_title <- expression(paste("Proportion of available habitat (", italic("p"), ")"))
+
+#Now make the map
+tiff("FigureS9_p_vs_H.tif", height = 8.7, width = 8.7, units = "cm", compression = "lzw", res = 900)
+ggplot(data=df, aes(y=y, x=x)) +
+  geom_raster(aes(fill=layer)) +
+    theme_bw() +
+  coord_equal() +
+  facet_grid(p~ H) +
+  #scale_fill_viridis(name="Resource quality")+
+  #scale_fill_continuous(colours=c("#0000FFFF","#FFFFFFFF"))+
+  scale_fill_gradient(low="lightgrey", high="darkgreen", guide=FALSE) +
+  #scale_fill_continuous(guide = FALSE) +
+  labs(y=my_y_title, x=my_x_title)+
+  theme(axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
+  theme(axis.title = element_text(size=10)) +
+  theme(strip.text = element_text(vjust=0.5, size=9))+ 
+  theme(legend.text = element_text(vjust=0.5, size=9), legend.title=element_text(vjust=0.5, size=10))
+dev.off()
+
+```

### 2018-05-22 SimpleSIR.Rmd
Updated figure numbering

--- 2018-04-09 SimpleSIR.Rmd
@@
 setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
-tiff("FigureS6.tiff", height = 17, width = 17,8, units = "cm", compression = "lzw", res = 1200)
+tiff("FigureS7.tiff", height = 17, width = 17,8, units = "cm", compression = "lzw", res = 1200)
 p

### 2018-05-22 Manuscript_figures_2017_12_12.Rmd
Remove directory specific references

@@
 #Set working directory of where to produce Figures
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
+setwd()
 ```
@@
 
-setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures May 2018")
+#setwd()
 tiff("FigureS1_party.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)

### 2018-05-22 SimpleSIR.Rmd
Update .Rmd formatting

@@
 
-#Load libraries
+## Load libraries
 Load `deSolve` library for evaluating ordinary differntial equations (ODEs).
@@
 
-##Run stochastic simulations
+## Run stochastic simulations
 Run simplified SIR model for six combinations of conspecific density and recovery rate tested in spatially explicit model.
@@
 
-##Plot deterministic and stochastic SIR results (assuming equal mixing)
+## Plot deterministic and stochastic SIR results (assuming equal mixing)
 Compare/verify output from deterministic ODE and stochastic SIR models
@@
 
-##Combine simulation ouput
+## Combine simulation ouput
 ```{r}
@@
 
-##Box plots
+## Box plots
 Box plots comparing density and recovery rates for homogenous mixing SIR model
@@
 
-##Fig. S6
+## Fig. S7
 Compare homogenous mixing and spatial models in box plot form.

### 2018-05-25 Manuscript_figures_2017_12_12.Rmd
Updated Fig 3 label sizing

--- 2018-05-22 Manuscript_figures_2017_12_12.Rmd
@@
 ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", fill= expression(beta[2]))
-ii<- ii+ theme(plot.title = element_text(size=7))
-ii<- ii+ theme(axis.title = element_text(size=6))
-ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
-ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
-ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
-ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=6))
+ii<- ii+ theme(plot.title = element_text(size=12))
+ii<- ii+ theme(axis.title = element_text(size=11))
+ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=10))
+ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=10)) 
+ii<- ii + theme(strip.text = element_text(vjust=0.5, size=11)) 
+ii<- ii + theme(legend.text = element_text(vjust=0.5, size=11), legend.title=element_text(vjust=0.5, size=11))
 ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
@@
 jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Duration", fill= expression(beta[2]))
-jj<- jj+ theme(plot.title = element_text(size=7))
-jj<- jj+ theme(axis.title = element_text(size=6))
-jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
-jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
-jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
-jj<- jj + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
+jj<- jj+ theme(plot.title = element_text(size=12))
+jj<- jj+ theme(axis.title = element_text(size=11))
+jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=10))
+jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=10)) 
+jj<- jj + theme(strip.text = element_text(vjust=0.5, size=11)) 
+jj<- jj + theme(legend.text = element_text(vjust=0.5, size=11), legend.title=element_text(vjust=0.5, size=11))
 jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
@@
            hjust = -1,
-           nrow = 2, label_size=7
+           nrow = 2, label_size=11
            )
@@
 
-tiff("Figure3test.tiff", height = 22.7, width = 17.8, units = "cm", compression = "lzw", res = 900)
+tiff("Figure3new.tiff", height = 22.7, width = 17.8, units = "cm", compression = "lzw", res = 900)
 #multiplot(ii,jj, cols=1)
